\documentclass[10pt]{article}
 \textwidth 15cm
 \oddsidemargin 0.0in 
 \evensidemargin 0.0in 
 \topmargin 0in
 \headheight -0in
 \headsep 0in
 \topskip 0in
 \textheight 23.0cm
 \marginparwidth 0in

\usepackage{fancyhdr}

%%%%%%%%%%%%% REMOVE TO GET PAGE NUMBERS BACK %%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{empty}
\thispagestyle{empty}

\begin{document}

\linespread{1.0}


\renewcommand{\thesection}{\Roman{section}.}


\begin{samepage}

\cfoot{\thepage\vspace{0.1in} of 8}
\rfoot{{\small{\bf{as of December 2015}}}}

{\center
{\Large\bf Demetrios Zeinalipour-Yazti \\ (Curriculum Vitae) \\  \centerline{\small Last Update: \today}} \vspace{0.1in} }

\begin{center} 
\begin{tabular*}{1.0\textwidth}%
   {@{\extracolsep{\fill}}lr}
	Department of Computer Science 		& 	Tel:   +357-22-892755 \\
	University of Cyprus                & 	Fax:   +357-22-892701  \\
	1 University Ave., P.O. Box 20537, 	&	{\tt dzeina@cs.ucy.ac.cy}	\\
	1678 Nicosia, Cyprus                & 	{\tt http://www.cs.ucy.ac.cy/\~{}dzeina/}	\\
    {\bf Data Management Systems Laboratory (DMSL)}  &  	{\tt http://dmsl.cs.ucy.ac.cy/}	\\
\end{tabular*}
\end{center}


\addtolength{\itemsep}{-1ex} \addtolength{\topsep}{-1.5ex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%			RESEARCH INTERESTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5

\section{\bf RESEARCH INTERESTS}
{\bf Data Management in Computer Systems and Networks:}
{\em Mobile and Sensor Data Management; Big Data Management in Parallel and Distributed Architectures; Spatio-Temporal Data Management; Network and Telco Data Management; Crowd, Web 2.0 and Indoor Data Management; Data Privacy Management.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%			EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5

\section{\bf EDUCATION}
\begin{center}  % put inside center environment
\begin{tabular*}{1.0\textwidth}%
   {@{\extracolsep{\fill}}llr}
{\bf Ph.D.}	& 	Computer Science \& Engineering, University of California - Riverside 		&       06/2003 - 08/2005 \\
		& 	{\em Dissertation: Search and Retrieval Algorithms for Distributed Data}		&			\\
        &  {\em Management Systems}  & \\
{\bf M.Sc.}	& 	Computer Science \& Engineering, University of California - Riverside 		& 	 09/2001 - 06/2003	\\
		& 	{\em Thesis: Information Retrieval in Peer-to-Peer Networks}	 		&			\\
{\bf B.Sc.}	& 	Computer Science, University of Cyprus			 		& 	 09/1996 - 07/2000		\\
		& 	{\em Thesis: An eXtensible Retrieval Annotation Caching Engine}	 		&			\\
\end{tabular*}
\end{center}



\section{\bf EXPERIENCE}

\begin{center} 
\begin{tabular*}{1.0\textwidth}%
   {@{\extracolsep{\fill}}lr}

{\bf Associate Professor}, Dept. of Computer Science, Univ. of Cyprus, Cyprus	&       04/2018 - current\\ \\

{\bf Assistant Professor}, Dept. of Computer Science, Univ. of Cyprus, Cyprus	&       01/2013 - 03/2018\\ \\

{\bf Humboldt Fellow},  Max Planck Institute for Informatics, Saarbr{\"u}cken, Germany 	&  	09/2016-08/2017  \\\\

{\bf Visiting Researcher},  Dept. of Computer Science, Univ. of Pittsburgh, PA, USA 	&  	Summer 2015  \\\\

{\bf Lecturer}, Dept. of Computer Science, Univ. of Cyprus, Cyprus	&       01/2009 - 12/2012 \\\\

{\bf Lecturer}, School of Pure and Applied Sc., Open Univ. of Cyprus, Cyprus	&       07/2007 - 01/2009 \\\\

{\bf Marie-Curie Fellow}, Dept. of Informatics \& Telec., University of Athens, Greece 	&  	Summer 2007  \\\\

{\bf Visiting Lecturer}, Dept. of Computer Science, Univ. of Cyprus, Cyprus 	&  	 08/2005 - 07/2007 \\\\

{\bf Visiting Researcher},  Network Intelligence Lab, Akamai, Cambridge MA, USA 	&  	Summer 2004  \\\\

{\bf Research Assistant}, DB Lab, Univ. of California - Riverside, CA, USA 	&  	 06/2003 - 08/2005	\\\\

{\bf Teaching Assistant}, University of California - Riverside, CA, USA 	&  	 09/2001 - 06/2003	\\\\
        		
{\bf Academic Collaborator},  University of Cyprus, Nicosia, Cyprus 	&  	 06/2000 - 09/2001 \\\\

\end{tabular*} 
\end{center}

\end{samepage}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%		        AWARDS \& HONORS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\renewcommand{\labelitemi}{$\bullet$}

\section{\bf AWARDS \& HONORS}
\setlength{\itemsep}{0.10ex}
\begin{itemize}
\item {\bf  Best Demo Award}. {\em ``FMS: Managing Crowdsourced Indoor Signals with the Fingerprint Management Studio''}, 19th IEEE International Conference on Mobile Data Management (MDM'18), Aalborg, Denmark, June 26 - June 28, 2018.
\item {\bf Honorable Mention Award}. {\em ``Indoor Localization Accuracy Estimation from Fingerprint Data''}, A. Nikitin, C. Laoudias, G. Chatzimilioudis, P. Karras, D. Zeinalipour-Yazti, {\em 18th IEEE Intl. Conf. on Mobile Data Management (MDM'17)}, Daejeon, S. Korea, May 29-Jun 1, 2017.
\item {\bf ACM Distinguished Speaker}.  {\em ``a highly visible way that ACM, through the appointment of leading researchers, engages with emerging professionals, students and, in some cases, the public on a range of topics in computing.''}, Association for Computing Machinery, New York, NY, USA, as of February 17, 2017 until February 17, 2020.
\item {\bf ACM Senior Member}  for {\em ``having demonstrated performance that sets them apart from their peers''}, Association for Computing Machinery, New York, NY, USA, as of January 3, 2017.
\item {\bf IEEE Senior Member}  for {\em ``significant contributions to the profession''}, Institute of Electrical and Electronics Engineers, 	New York, NY, USA, as of December 8, 2016.
\item {\bf Humboldt Fellow}, for {\em ``exceptionally highly-qualified scientists and scholars''}, Host Institute: Max Planck Institute for Informatics, Saarbr{\"u}cken, Germany,  Alexander von Humboldt Foundation, Bonn, Germany, 09/2016-08/2017.
\item {\bf Best Demo Award}, ``Indoor Geolocation for Android Smartphones with Airplace'', T. Costambeys, C. Laoudias, {\bf D. Zeinalipour-Yazti}, C. G. Panayiotou, EVARILOS Open Challenge, FP7 Project (\#317989), European Union, Berlin, Germany, 2014.
\item  {\bf 2nd Best Demo Award}, ``Accurate Multi-Sensor Localization on Android Devices'', C. Laoudias, G. Larkou, M. Chin-Lung Li, Yu-Kuen Tsai, {\bf D. Zeinalipour-Yazti}, C. G. Panayiotou, Microsoft Indoor Localization Competition, {\em 13th ACM/IEEE Intl. Conf. on Information Processing in Sensor Networks} (IPSN'14), April 15-17, Berlin, Germany, 2014.
\item  {\bf Appcampus Award}, ``Rayzit: Crowd Messaging'' by Microsoft, Nokia and Aalto University (Finland) innovative mobile application rayzit.com, 2013.

\item  {\bf Best Demo Award}, ``The Airplace Indoor Positioning Platform for Android Smartphones'', C. Laoudias, G. Constantinou, M. Constantinides, S. Nicolaou, {\bf D. Zeinalipour-Yazti}, C. G. Panayiotou, {\em 13th IEEE Intl. Conference on Mobile Data Management}  (MDM 2012), Bangalore, India, July 23-26, 2012.
\item   {\bf Best Demo Award}, ``ICGrid: Intensive Care Grid'',
CoreGRID Industrial Conference, Sophia Antipolis, France,  November 2006
\item  {\bf Outstanding Teaching Assistant Honorable Mention}, University of California, Riverside, CA, USA,		2002-2003.
\item  {\bf Head Teaching Assistant}, Computer Science \& Engr. Dept, Univ. of California, Riverside, CA, USA,    2002-2003.
\item  {\bf Outstanding Teaching Assistant Award}, U. of California, Riverside, CA, USA, 			2001-2002.
\item  {\bf Full Scholarship} by the Computer Science \& Engr. Dept, Univ. of California, Riverside, CA, USA,	2001-2006.
\item  {\bf Dean's Graduate Fellowship Award}, U. of California, Riverside, CA, USA,				2001-2003.
\item  {\bf Young Researcher Fellowship Award}, Cyprus Research Promotion Foundat.,	2000-2001.
\item  {\bf Awards at School}: Praise in Paneuropean writing
contest (1990-91), 1st in CyBC's national History \& Archeology contest (1991-92) and
2nd in national Geography (1992-93) contest.
\end{itemize}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%			PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\section{PUBLICATIONS}
{\bf Google Scholar Citations: 2,655;
h-index\footnote{h-index is the largest number h such that h publications have at least h citations.}: 24;
i10-index\footnote{i10-index is the number of publications with at least 10 citations.}: 52}

\subsection*{JOURNAL AND MAGAZINE ARTICLES}
\begin{enumerate}

\item[{\bf J23.}]
\label{J23} % TOIT'18
{\bf ``IoT Data Prefetching in Indoor Navigation SOAs''}, \\
Andreas Konstantinidis, Panagiotis Irakleous, Zacharias Georgiou,
{\bf Demetrios Zeinalipour-Yazti}, Panos K. Chrysanthis,
{\bf ACM Transactions on Internet Technology (TOIT'18)}, 20 pages, {\bf 2018}.

\item[{\bf J22.}]
\label{J22} % Internet Computing '17
{\bf ``Internet-based Indoor Navigation Services''}, \\
{\bf Demetrios Zeinalipour-Yazti}, Christos Laoudias, Kyriakos Georgiou and Georgios Chatzimilioudis
{\bf IEEE Internet Computing (IC)}, IEEE Computer Society, Vol. 21, Iss. 4, pp. 54-63, 10.1109/MIC.2017.265101954, Los Alamitos, CA, USA, {\bf 2017}.

\item[{\bf J21.}]
\label{J21} % Infosys'15
{\bf ``Crowdsourcing Emergency Data in Non-Operational Cellular Networks''}, \\
Georgios Chatzimilioudis, Constantinos Costa,  {\bf Demetrios Zeinalipour-Yazti}, Wang-Chien Lee,
{\bf Information Systems (InfoSys)}, Special Issue on Large-Scale Data Management for Mobile Applications,
Vol. 64, pp. 292 - 302, Oxford, UK, {\bf 2017}.

\item[{\bf J20.}]
\label{J20} % TKDE'16
{\bf ``Distributed In-Memory Processing of All k Nearest Neighbor Queries''}, \\
Georgios Chatzimilioudis, Constantinos Costa, {\bf Demetrios Zeinalipour-Yazti} and
Wang-Chien Lee and Evaggelia Pitoura,
{\bf Transactions on Knowledge and Data Engineering (TKDE)},
IEEE Computer Society, Volume 28, Issue 4, Pages: 925-938, Los Alamitos, CA, USA, {\bf 2016}.

\item[{\bf J19.}]
\label{J19} % DAPD'14
{\bf ``Managing Big-Data Experiments on Smartphones''}, \\
Georgios Larkou, Marios Mintzis, Andreas Konstantinidis, Panayiotis Andreou and {\bf Demetrios Zeinalipour-Yazti},
{\bf Distributed and Parallel Databases (DAPD)}, Special Issue on Large-Scale Data Management for Mobile Applications, Springer US, Vol. 34, Iss. 1, pp. 33-64, {\bf 2016}.

\item[{\bf J18.}]
\label{J18} % TKDE'15
{\bf ``Privacy-Preserving Indoor Localization on Smartphones''}, \\
Andreas Konstantinidis, Georgios Chatzimilioudis, {\bf Demetrios Zeinalipour-Yazti}, Paschalis Mpeis, Nikos Pelekis,  and Yannis Theodoridis,
{\bf Transactions on Knowledge and Data Engineering (TKDE)},
IEEE Computer Society, Volume 27, Issue 11, Pages: 3042-3055, Los Alamitos, CA, USA, {\bf 2015}.

\item[{\bf J17.}] 
\label{J17} %JNCA
{\bf ``A Network-aware Framework for Energy-efficient Data Acquisition in Wireless Sensor Networks''}, \\
Panayiotis G. Andreou, {\bf Demetrios Zeinalipour-Yazti}, George S. Samaras, Panos K. Chrysanthis,
{\bf Journal of Network and Computer Applications (JNCA)},  Elsevier Press,  
Volume 30, Issue 1, Pages: 209-243, January {\bf 2014}.  
 
\item[{\bf J16.}] 
\label{J16}
{\bf ``Crowdsourced Trace Similarity with Smartphones''}, \\
{\bf Demetrios Zeinalipour-Yazti}, Christos Laoudias, Costandinos Costa, Maria I. Andreou, Michalis Vlachos, Dimitrios Gunopulos, {\bf IEEE Transactions on Knowledge and Data Engineering (TKDE)},
IEEE Computer Society, Volume 25, Pages: 1240-1253, Los Alamitos, CA, USA, {\bf 2013}.  

\item[{\bf J15.}] 
\label{J15}
{\bf ``Intelligent Search in Social Communities of Smartphone Users''}, \\
Andreas Konstantinidis, {\bf Demetrios Zeinalipour-Yazti}, Panayiotis G. Andreou, 
Panos K. Chrysanthis, George Samaras, 
{\bf Distributed and Parallel Databases (DAPD)}, Special Issue on Mobile Data Management, 
Springer US, Volume 31, Pages: 115-149, {\bf 2013}.

\item[{\bf J14.}] 
\label{J14}
{\bf ``Crowdsourcing with Smartphones''}, \\
Georgios Chatzimiloudis, Andreas Konstantinides, Christos Laoudias and {\bf Demetrios Zeinalipour-Yazti}, 
{\bf IEEE Internet Computing (IC)}, Special Issue: Sep/Oct 2012 - Crowdsourcing May 2012. IEEE Press, Volume 16, Pages: 36-44, {\bf 2012}.

\item[{\bf J13.}] 
\label{J13}
{\bf ``Power Efficiency through Tuple Ranking in Wireless Sensor Network Monitoring''},\\
Panayiotis Andreou, {\bf Demetrios Zeinalipour-Yazti}, Panos K. Chrysanthis and George Samaras,
{\bf Distributed and Parallel Databases (DAPD)}, Special Issue on Query Processing in Sensor Networks, Springer Press, Volume 29, Issue 1-2, Pages: 113-150, DOI: 10.1007/s10619-010-7072-5, January {\bf 2011}.

\item[{\bf J12.}] 
\label{J12}
{\bf ``In-Network Data Acquisition and Replication in Mobile Sensor Networks''},\\
Panayiotis Andreou, {\bf Demetrios Zeinalipour-Yazti}, Panos K. Chrysanthis and George Samaras,
{\bf Distributed and Parallel Databases (DAPD)}, Special Issue on Query Processing in Sensor Networks, 
Springer Press,  Volume 29, Issue 1-2, Pages: 87-112, DOI: 10.1007/s10619-010-7073-4, January {\bf 2011}.

\item[{\bf J11.}] 
\label{J11}
{\bf ``Optimized Query Routing Trees for Wireless Sensor Networks''},\\
Panayiotis Andreou, {\bf Demetrios Zeinalipour-Yazti}, Andreas Pamboris, Panos K. Chrysanthis and George Samaras,
{\bf Information Systems (InfoSys)}, Volume 36, Issue 2, Pages: 267-291, Elsevier Press, April {\bf 2011}.

\item[{\bf J10.}] 
\label{J10}
{\bf ``A Multi-Objective Evolutionary Algorithm for the Deployment and Power Assignment Problem in Wireless Sensor Networks''}, \\
Andreas Konstantinidis, Kun Yang, Qingfu Zhang, {\bf Demetrios Zeinalipour-Yazti}
{\bf Computer Networks (ComNet)}, Volume 54, Issue 6, Pages: 960-976, Elsevier Press, April {\bf 2010}.

\item[{\bf J9.}] 
\label{J9}
{\bf ``Finding the K Highest-Ranked Answers in a Distributed Network''},\\
{\bf Demetrios Zeinalipour-Yazti}, Zografoula Vagena, Dimitrios Gunopulos, Vana Kalogeraki, Vassilis Tsotras, Michail Vlachos, Nick Koudas and Divesh Srivastava,
{\bf Computer Networks (ComNet)},  Volume 53, Issue 9, Pages: 1431-1449, Elsevier Press, {\bf 2009}.

\item[{\bf J8.}] 
\label{J8}
{\bf ``Metadata Ranking and Pruning for Failure Detection in Grids''},\\
{\bf Demetrios Zeinalipour-Yazti}, Haris Papadakis, Chryssis Georgiou and Marios D. Dikaiakos,
{\bf Parallel Processing Letters Journal (PPL)}, 
Special Issue on Grid Architectural Issues: Scalability, Dependability, Adaptability,
Volume:  18, Issue: 3, Page 371 - 390, September {\bf 2008}.

\item[{\bf J7.}] 
\label{J7}
{\bf ``pFusion: An Architecture for Internet-Scale Content-Based Search and Retrieval''},\\
{\bf Demetrios Zeinalipour-Yazti}, Vana Kalogeraki and Dimitrios Gunopulos,
{\bf IEEE Transactions on Parallel and Distributed Systems (TPDS)}, Volume 18, No. 6, Pages: 804-817, June {\bf 2007}.

\item[{\bf J6.}] 
\label{J6}
{\bf ``Distributed Middleware Architectures for Scalable Media Services''},  
Vana Kalogeraki, {\bf Demetrios Zeinalipour-Yazti}, Dimitrios Gunopulos and Alex Delis,
{\bf Journal of Network and Computer Applications (JNCA)},  Elsevier Press,  
Volume 30, Issue 1, Pages: 209-243, January {\bf 2007}.  

\item [{\bf J5.}] 
\label{J5}
{\bf ``Efficient Indexing Data Structures for Flash-Based Sensor Devices''},\\
Song Lin, {\bf Demetrios Zeinalipour-Yazti}, Vana Kalogeraki, Dimitrios Gunopulos, Walid Najjar, 
{\bf ACM Transactions on Storage (TOS)}, Volume 2, No. 4, Pages: 468 - 503, November {\bf 2006}.

\item[{\bf J4.}] 
\label{J4} 
{\bf ``Structuring Topologically-Aware Overlay Networks using Domain Names''},\\
{\bf Demetrios Zeinalipour-Yazti} and Vana Kalogeraki,
{\bf Computer Networks (ComNet)},  Elsevier Press, Volume 50, Issue 16, Pages: 3064-3082, November {\bf 2006}.  

\item[{\bf J3.}] 
\label{J3}
{\bf ``Exploiting Locality for Scalable Information Retrieval in Peer-to-Peer Systems''},\\
{\bf Demetrios Zeinalipour-Yazti}, Vana Kalogeraki and Dimitrios Gunopulos, 
{\bf Information Systems (InfoSys)},  Elsevier Press,  Volume 30, Issue 4, Pages: 277-298, {\bf 2005}.
(ranks 1st in the TOP25 list of the Information Systems journal in April-May-June 2005).

\item[{\bf J2.}] 
\label{J2}
{\bf ``A Distributed Middleware Infrastructure for Personalized Services''},\\
Marios D. Dikaiakos, {\bf Demetrios Zeinalipour-Yazti}, 
{\bf Computer Communications (ComCom)}, Elsevier Press, Volume 27, Issue 15, Pages: 1464-1480, {\bf 2004}.

\item[{\bf J1.}] 
\label{J1}  
{\bf ``Information Retrieval Techniques for Peer-to-Peer Systems''}, \\
{\bf Demetrios Zeinalipour-Yazti}, Vana Kalogeraki and Dimitrios Gunopulos, 
{\bf Computing in Science and Engineering (CiSE)}, Special Issue on Web Engineering, IEEE Publications, Pages: 20 - 26, ISSN: 1521-9615, July/August {\bf 2004}.

\end{enumerate}


\subsection*{CONFERENCE AND WORKSHOP PROCEEDINGS}
\begin{enumerate}


\item[{\bf C78.}]
\label{C78} % ICC19-FINGER
{\bf ``A Qualitative and Quantitative Evaluation of Differential Signal Strength Fingerprinting Methods''}, \\
Christos Laoudias, Sunwoo Kim, Christos Panayiotou and {\bf Demetrios Zeinalipour-Yazti},
{\em Proceedings of the 53rd IEEE International Conference on Communications (ICC) / WC Symposium {\bf (ICC 2019 / WC Symposium)}}, 7 pages, IEEE Communications Society, Shanghai, China, 20-24 May {\bf 2019}.

\item[{\bf C77.}]
\label{C77} % ICDE19-BRIQ
{\bf ``Bridging Quantities in Tables and Text''}, \\
Yusra Ibrahim, Mirek Riedewald, Gerhard Weikum and {\bf Demetrios Zeinalipour-Yazti},
{\em Proceedings of the 35th IEEE International Conference on Data Engineering {\bf (ICDE 2019)}}, 10 pages, IEEE Computer Society, 8-12 April 2019, Macau SAR, China, {\bf 2019}.

\item[{\bf C76.}]
\label{C76} % ICDE19-TBD-PAPER
{\bf ``Telco Big Data Research and Open Problems''}, \\
Constantinos Costa and {\bf Demetrios Zeinalipour-Yazti},
{\em Proceedings of the 35th IEEE International Conference on Data Engineering {\bf (ICDE 2019)}}, 10 pages, IEEE Computer Society, 8-12 April 2019, Macau SAR, China, {\bf 2019}.

\item[{\bf C75.}]
\label{C75} % MDM18-DP
{\bf ``Decaying Telco Big Data with Data Postdiction''}, \\
Constantinos Costa, Andreas Charalampous, Andreas Konstantinidis, {\bf Demetrios Zeinalipour-Yazti}, and Mohamed F. Mokbel,
{\em Proceedings of the 19th IEEE International Conference on Mobile Data Management, {\bf (MDM 2018)}}, 10 pages, June 25 - June 28, 2018, AAU, Aalborg, Denmark, {\bf 2018}.

\item[{\bf C74.}]
\label{C74} % MDM18-PANEL
{\bf ``Future Directions for Indoor Information Systems: A Panel Discussion''}, \\
{\bf Demetrios Zeinalipour-Yazti},
{\em Proceedings of the 19th IEEE International Conference on Mobile Data Management, {\bf (MDM 2018)}}, 2 pages, June 25 - June 28, 2018, AAU, Aalborg, Denmark, {\bf 2018}.

\item[{\bf C73.}]
\label{C73} % MDM18-SEMINAR
{\bf ``Telco Big Data: Current State \& Future Directions''}, \\
Constantinos Costa and {\bf Demetrios Zeinalipour-Yazti},
{\em Proceedings of the 19th IEEE International Conference on Mobile Data Management, {\bf (MDM 2018)}}, 4 pages, June 25 - June 28, 2018, AAU, Aalborg, Denmark, {\bf 2018}.

\item[{\bf C72.}]
\label{C72} % MDM'18-FMS-DEMO
{\bf ``FMS: Managing Crowdsourced Indoor Signals with the Fingerprint Management Studio''}, \\
Marileni Angelidou, Constantinos Costa, Artyom Nikitin and {\bf Demetrios Zeinalipour-Yazti},
{\em Proceedings of the 19th IEEE International Conference on Mobile Data Management, {\bf (MDM 2018)}}, 2 pages, June 25 - June 28, 2018, AAU, Aalborg, Denmark, {\bf 2018}.

\item[{\bf C71.}]
\label{C71} % MDM'18-DP-DEMO
{\bf ``TBD-DP: Telco Big Data Visual Analytics with Data Postdiction''}, \\
Constantinos Costa, Andreas Charalampous, Andreas Konstantinidis, {\bf Demetrios Zeinalipour-Yazti}, and Mohamed F. Mokbel
{\em Proceedings of the 19th IEEE International Conference on Mobile Data Management, {\bf (MDM 2018)}}, 2 pages, June 25 - June 28, 2018, AAU, Aalborg, Denmark, {\bf 2018}.

\item[{\bf C70.}]
\label{C70} % SIGMOD18-EPUI
{\bf ``EPUI: Experimental Platform for Urban Informatics''}, \\
Xiaoyi Ge, Panos K. Chrysanthis, Konstantinos Pelechrinis, and {\bf Demetrios Zeinalipour-Yazti}
{\em Proceedings of the 2018 ACM International Conference on Management of Data, {\bf (SIGMOD 2018)}}, 4 pages, June 10-15, Houston, Texas, USA, {\bf 2018}.

\item[{\bf C69.}]
\label{C69} % JCDL19-ASPECT
{\bf ``Generating Semantic Aspects for Queries''}, \\
Dhruv Gupta, Klaus Berberich, Jannik Strötgen, and {\bf Demetrios Zeinalipour-Yazti}
{\em Proceedings of the 18th ACM/IEEE Joint Conference on Digital Libraries, {\bf (JCDL '18)}}, 2 pages, June 3-6, 2018, Fort Worth, Texas, USA, {\bf 2018}.

\item[{\bf C68.}]
\label{C68} % ICDE'17
{\bf ``Towards Real-Time Road Traffic Analytics using Telco Big Data''}, \\
Constantinos Costa, Georgios Chatzimilioudis, {\bf Demetrios Zeinalipour-Yazti} and Mohamed F. Mokbel,
{\em Proceedings of the 11th Intl. Workshop on Real-Time Business Intelligence and Analytics {\bf (BIRTE 2017)}}, collocated with VLDB 2017, pp. 5:1--5:5, ISBN: 978-1-4503-5425-7/17/08, Munich, Germany, August 28, {\bf 2017}.

\item[{\bf C67.}]
\label{C67} % ICDCS17-SERENDIPITY
{\bf ``Data-driven Serendipity Navigation in Urban Places''}, \\
Xiaoyi Ge, Ameya Daphalapurkar, Manali Shmipi, Kohli Darpun, Konstantinos Pelechrinis, Panos K. Chrysanthis, and {\bf Demetrios Zeinalipour-Yazti}
{\em Proceedings of the 37th IEEE International Conference on Distributed Computing Systems {\bf (ICDCS 2017)}}, 4 pages,
June 5-8, Atlanta, GA, USA, {\bf 2017}.

\item[{\bf C66.}]
\label{C66} % MDM'17
{\bf ``Indoor Localization Accuracy Estimation from Fingerprint Data''}, \\
Artyom Nikitin, Christos Laoudias,  Georgios Chatzimilioudis, Panagiotis Karras and {\bf Demetrios Zeinalipour-Yazti},
{\em Proceedings of the 18th IEEE International Conference on Mobile Data Management {\bf (MDM 2017)}}, IEEE Computer Society, pp. 196-205, May 29 - June 1, 2017, Daejeon, South Korea, {\bf 2017}. {\bf (Honorable Mention Award)}

\item[{\bf C65.}]
\label{C65} % MDM'17
{\bf ``ACCES: Offline Accuracy Estimation for Fingerprint-based Localization''}, \\
Artyom Nikitin, Christos Laoudias,  Georgios Chatzimilioudis, Panagiotis Karras and {\bf Demetrios Zeinalipour-Yazti},
{\em Proceedings of the 18th IEEE International Conference on Mobile Data Management {\bf (MDM 2017)}}, IEEE Computer Society, pp. 358-359, May 29 - June 1, 2017, Daejeon, South Korea, ISBN-13: 978-1-5386-3932-0, {\bf 2017}.

\item[{\bf C64.}]
\label{C64} % ICDE'17
{\bf ``Efficient Exploration of Telco Big Data with Compression and Decaying''}, \\
Constantinos Costa, Georgios Chatzimilioudis, {\bf Demetrios Zeinalipour-Yazti} and Mohamed F. Mokbel,
{\em Proceedings of the 33rd International Conference on Data Engineering {\bf (ICDE 2017)}}, IEEE Computer Society, pp. 1332-1343, April 19-22, 2017, San Diego, CA, USA, ISBN: 978-1-5090-6543-1, {\bf 2017}.

\item[{\bf C63.}]
\label{C63} % ICDE'17
{\bf ``SPATE: Compacting and Exploring Telco Big Data''}, \\
Constantinos Costa, Georgios Chatzimilioudis, {\bf Demetrios Zeinalipour-Yazti}, and Mohamed F. Mokbel,
{\em Demo Proceedings of the 33rd International Conference on Data Engineering {\bf (ICDE 2017)}}, IEEE Computer Society, pp. 1419-1420, April 19-22, 2017, San Diego, CA, USA, ISBN: 978-1-5090-6543-1, {\bf 2017}.

\item[{\bf C62.}]
\label{C62} % ICDE'16
{\bf ``Distributed In-Memory Processing of All k Nearest Neighbor Queries (Extended Abstract)''}, \\
Georgios Chatzimilioudis, Constantinos Costa, {\bf Demetrios Zeinalipour-Yazti} and
Wang-Chien Lee and Evaggelia Pitoura,
{\em Proceedings of the 32nd International Conference on Data Engineering {\bf (ICDE 2016)}},
Helsinki, Finland, May 16-20, Pages: 1490--1491, DOI: 10.1109/ICDE.2016.7498389, {\bf 2016}.

\item[{\bf C61.}]
\label{C61} % ICDE'16
{\bf ``Privacy-Preserving Indoor Localization on Smartphones (Extended Abstract)''}, \\
Andreas Konstantinidis, Georgios Chatzimilioudis, {\bf Demetrios Zeinalipour-Yazti}, Paschalis Mpeis, 
Nikos Pelekis, and Yannis Theodoridis,
{\em Proceedings of the 32nd International Conference on Data Engineering {\bf (ICDE 2016)}},
Helsinki, Finland, May 16-20, Pages: 1470--1471, DOI: 10.1109/ICDE.2016.7498379, {\bf 2016}.

\item[{\bf C60.}]
\label{C60}
{\bf ``A Realistic Evaluation and Comparison of Indoor Location Technologies: Experiences and Lessons Learned''}, \\
Dimitrios Lymberopoulos, Jie Liu, Xue Yang, Romit Roy Choudhury, ..., Christos Laoudias, {\bf Demetrios Zeinalipour-Yazti}, Yu-Kuen Tsai, et. al.
{\em Proceedings of the 14th International Conference on Information Processing in Sensor Networks {\bf (IPSN 2015)}},
Seattle, WA, USA, April 14-16, Pages: 178--189, {\bf 2015}.

\item[{\bf C59.}]
\label{C59}
{\bf ``RadioMap Prefetching for Indoor Navigation in Intermittently Connected Wi-Fi Networks''}, \\
Andreas Konstantinidis, George Nikolaides, Georgios Chatzimilioudis, Giannis Evagorou,  {\bf Demetrios Zeinalipour-Yazti} and Panos K. Chrysanthis,
{\em Proceedings of the 16th IEEE International Conference on Mobile Data Management {\bf (MDM 2015)}},
Pittsburgh, PA, USA, July 15-18, Volume 1, Pages: 34-43, {\bf 2015}.

\item[{\bf C58.}]
\label{C58}
{\bf ``Rayzit: An Anonymous and Dynamic Crowd Messaging Architecture''}, \\
Constantinos Costa, Chrysovalantis Anastasiou, Georgios Chatzimilioudis and {\bf Demetrios Zeinalipour-Yazti}
{\em Proceedings of the 3rd IEEE International Workshop on Mobile Data Management Mining and Computing on Social Networks collocated with IEEE MDM '15 {\bf (Mobisocial 2015)}},
Pittsburgh, PA, USA, July 15-18, 978-1-4799-9972-9/15, IEEE Press, Volume 2, Pages: 98-103, {\bf 2015}.

\item[{\bf C57.}]
\label{C57}
{\bf ``Scalable Mockup Experiments on Smartphones using SmartLab''}, \\
Georgios Larkou, Marios Mintzis, Panayiotis G. Andreou, Andreas Konstantinidis and {\bf Demetrios Zeinalipour-Yazti}
{\em Proceedings of the 16th IEEE International Conference on Mobile Data Management {\bf (MDM 2015)}},
Pittsburgh, PA, USA, July 15-18, 978-1-4799-9972-9/15, IEEE Press, Volume 2, Pages: 287-290, {\bf 2015}.

\item[{\bf C56.}]
\label{C56}
{\bf ``Anyplace: A Crowdsourced Indoor Information Service''}, \\
Kyriakos Georgiou, Timotheos Constambeys, Christos Laoudias, Lambros Petrou, Georgios Chatzimilioudis and  {\bf Demetrios Zeinalipour-Yazti}
{\em Proceedings of the 16th IEEE International Conference on Mobile Data Management {\bf (MDM 2015)}},
Pittsburgh, PA, USA, July 15-18, 978-1-4799-9972-9/15, IEEE Press, Volume 2, Pages: 291-294, {\bf 2015}.

\item[{\bf C55.}]
\label{C55}
{\bf ``Mobile Data Management in Indoor Spaces''}, \\
Christos Laoudias and {\bf Demetrios Zeinalipour-Yazti},
{\em Proceedings of the 16th IEEE International Conference on Mobile Data Management}
{\bf (MDM 2015)}, Pittsburgh, PA, USA, June 15-18, Volume 1, Pages: 11-14, {\bf 2015}.

\item[{\bf C54.}]
\label{C54}
{\bf ``Mobile Big Data Analytics: Research, Practice and Opportunities''}, \\
{\bf Demetrios Zeinalipour-Yazti} and Shonali Krishnaswamy,
{\em Proceedings of the 15th IEEE International Conference on Mobile Data Management}
{\bf (MDM 2014)}, Brisbane, Australia, July 15-18, Volume 1, Pages: 1-2, {\bf 2014}.

\item[{\bf C53.}]
\label{C53}
{\bf ``Sensor Mockup Experiments with SmartLab''}, \\
George Larkou, Marios Mintzis, Stefano Taranto, Andreas Konstantinidis, Panayiotis G. Andreou and {\bf Demetrios Zeinalipour-Yazti},
{\em Proceedings of the 13th international conference on Information processing in sensor networks}
{\bf (IPSN 2014)}, Pages: 339--340, ISBN: 978-1-4799-3146-0, Berlin, Germany, April 15-17, {\bf 2014}.

\item[{\bf C52.}]
\label{C52}
{\bf ``Crowdsourced Indoor Localization and Navigation with Anyplace''}, \\
Lambros Petrou, George Larkou, Christos Laoudias, {\bf Demetrios Zeinalipour-Yazti}, Christos G. Panayiotou,
{\em Proceedings of the 13th international conference on Information processing in sensor networks}
{\bf (IPSN 2014)}, Pages: 331--332, ISBN: 978-1-4799-3146-0, Berlin, Germany, April 15-17, {\bf 2014}.

\item[{\bf C51.}]
\label{C51}
{\bf ``Managing Smartphone Testbeds with SmartLab''}, \\
George Larkou, Panayiotis K. Andreou, Andreas Konstantinides and {\bf Demetrios Zeinalipour-Yazti}
{\em Proceedings of the 27th USENIX Large Installation System Administration Conference}
{\bf (LISA 2013)}, Pages: 115-132, ISBN: 978-1-931971-05-8, Washington D.C., USA, {\bf 2013}.

\item[{\bf C50.}]
\label{C50}
{\bf ``Indoor Positioning and Navigation in the Big-Data Era''}, \\
Lambros Petrou, George Larkou, Christos Laoudias, {\bf Demetrios Zeinalipour-Yazti} and Christos G. Panayiotou,
{\em Proceedings of the 4th Intl. Conference on Indoor Positioning and Indoor Navigation}
{\bf (IPIN 2013)},  Montbéliard, France, {\bf 2013}.
 
\item[{\bf C49.}]
\label{C49}
{\bf ``Crowdsourced Indoor Localization for Diverse Devices through Radiomap Fusion''}, \\
Christos Laoudias, {\bf Demetrios Zeinalipour-Yazti} and Christos G. Panayiotou,
{\em Proceedings of the 4th Intl. Conference on Indoor Positioning and Indoor Navigation}
{\bf (IPIN 2013)},  Montbéliard, France, {\bf 2013}.

\item[{\bf C48.}]
\label{C48}
{\bf ``Demo: Indoor Geolocation on Multi-Sensor Smartphones''}, \\
Chin-Lung Li, Christos Laoudias, George Larkou, Yu-Kuen Tsai, {\bf Demetrios Zeinalipour-Yazti} and Christos G. Panayiotou
{\em Proceedings of the 11th International Conference on Mobile Systems, Applications and Services}
{\bf (MobiSys 2013)}, Tapei, Taiwan, Pages: 503-504, Taipei, Taiwan, June 25 - 28, ISBN: 978-1-4503-1672-9, {\bf 2013}.

\item[{\bf C47.}]
\label{C47}
{\bf ``Crowdsourcing for Mobile Data Management''}, \\
Georgios Chatzimilioudis and {\bf Demetrios Zeinalipour-Yazti}
{\em 14th IEEE International Conference on Mobile Data Management} {\bf (MDM 2013)}, Milan, Italy, June 3-6, {\bf 2013}.

\item[{\bf C46.}]
\label{C46}
{\bf ``CLODA: A Crowdsourced Linked Open Data Architecture''}, \\
George Larkou, Julia Metochi, Georgios Chatzimilioudis and {\bf Demetrios Zeinalipour-Yazti}
{\em 1st IEEE International Workshop on Mobile Data Management, Mining, and Computing on Social Networks (MobiSocial)}, at {\em 14th IEEE International Conference on Mobile Data Management} {\bf (MDM 2013)}, June 3-6 2013, Milan, Italy, {\bf 2013}.
 
\item[{\bf C45.}]
\label{C45}
{\bf ``Hybrid Indoor Positioning on Multi-Sensor Android Smartphones''}, \\
Chin-Lung Li, Christos Laoudias, George Larkou, Georgios Chatzimilioudis, {\bf Demetrios Zeinalipour-Yazti} and Christos G. Panayiotou
{\em The 3rd International Conference on Indoor Positioning and Indoor Navigation} {\bf (IPIN 2012)},
November 13-15, 2012, Sydney, Australia, {\bf 2012}.
  
\item[{\bf C44.}]
\label{C44}
{\bf ``FireWatch: G.I.S.-assisted Wireless Sensor Networks for Forest Fires''}, \\
Panayiotis G. Andreou, George Constantinou, {\bf Demetrios Zeinalipour-Yazti}, George Samaras,
{\em The 24th International Conference on Scientific and Statistical Database Management} {\bf (SSDBM 2012)},
Springer LNCS Series, Volume 7338, Pages: 618-621, Chania, Greece, ISBN: 978-3-642-31234-2, {\bf 2012}.

\item[{\bf C43.}]
\label{C43}
{\bf ``Continuous All k-Nearest Neighbor Querying in Smartphone Networks''}, \\
Georgios Chatzimilioudis, {\bf Demetrios Zeinalipour-Yazti}, Wang-Chien Lee, Marios D. Dikaiakos,
{\em Proceedings of the 13th IEEE International Conference on Mobile Data Management} {\bf (MDM 2012)}, IEEE Computer Society, Pages: 79--88, Bangalore, India, ISBN: 978-0-7695-4713-8, {\bf 2012}. 

\item[{\bf C42.}]
\label{C42}
{\bf ``The Airplace Indoor Positioning Platform for Android Smartphones''}, \\
Christos Laoudias, George Constantinou, Marios Constantinides, Silouanos Nicolaou, {\bf Demetrios Zeinalipour-Yazti}, Christos G. Panayiotou,
{\em Proceedings of the 13th IEEE International Conference on Mobile Data Management} {\bf (MDM 2012)},  IEEE Computer Society, Pages: 312--315, Bangalore, India, ISBN: 978-0-7695-4713-8, {\bf 2012}. ({\bf Best Demo Award})

\item[{\bf C41.}]
\label{C41}
{\bf ``SmartP2P: A Multiobjective Framework for Finding Social Content in P2P Smartphone Networks''}, \\
Andreas Konstantinidis, Christos Aplitsiotis, {\bf Demetrios Zeinalipour-Yazti},
{\em Proceedings of the 13th IEEE International Conference on Mobile Data Management} {\bf (MDM 2012)}, 
IEEE Computer Society, Pages: 324--327, Bangalore, India, ISBN: 978-0-7695-4713-8, {\bf 2012} 

\item[{\bf C40.}]
\label{C40}
{\bf ``Towards In-Situ Localization on Smartphones with a Partial Radiomap''}, \\
Andreas Konstantinidis, Georgios Chatzimilioudis, Christos Laoudias, Silouanos Nicolaou and {\bf Demetrios Zeinalipour-Yazti}, 
{\em Proceedings of the 4th ACM international workshop on Hot topics in planet-scale measurement} 
{\bf (HotPlanet'12)}, in conjunction with ACM MobiSys'12, ACM, Pages: 9--14, New York, NY, USA, ISBN: 978-1-4503-1318-6, Low Wood Bay, Lake District, UK, June 25, {\bf 2012}.

\item[{\bf C39.}]
\label{C39}
{\bf ``Demo: The Airplace Indoor Positioning Platform''}, \\
Christos Laoudias, George Constantinou, Marios Constantinides, Silouanos Nicolaou, {\bf Demetrios Zeinalipour-Yazti} and Christos G. Panayiotou,
{\em The 10th International Conference on Mobile Systems, Applications and Services} 
{\bf (MobiSys 2012)}, Low Wood Bay, Lake District UK, June 25 - 29,  Pages: 467-468,
 ISBN: 978-1-4503-1301-8, {\bf 2012}.

\item[{\bf C38.}]
\label{C38}
{\bf ``Demo: A Programming Cloud of Smartphones''}, \\
Andreas Konstantinidis, Constantinos Costa, George Larkou and {\bf Demetrios Zeinalipour-Yazti},
{\em The 10th International Conference on Mobile Systems, Applications and Services} 
{\bf (MobiSys 2012)}, Low Wood Bay, Lake District UK, June 25 - 29, Pages: 465-466,
 ISBN: 978-1-4503-1301-8, {\bf 2012}.
 
\item[{\bf C37.}]
\label{C37}
{\bf ``Towards a Network-aware Middleware for Wireless Sensor Networks''}, \\
Panayiotis Andreou, {\bf Demetrios Zeinalipour-Yazti}, George Samaras, Panos K. Chrysanthis,
8th Intl. Workshop on Data Management for Sensor Networks {\bf (DMSN 2011)}, in conjunction with VLDB 2011,
Seattle, WA, USA, August 29, {\bf 2011}.

\item[{\bf C36.}] 
\label{C36}
{\bf ``Data Management Techniques for Smartphone Networks''}, \\
{\bf Demetrios Zeinalipour-Yazti}
10th International ACM Workshop on Data Engineering for Wireless and Mobile Access {\bf (MobiDE 2011)}, in conjunction with SIGMOD/PODS 2011, Athens, Greece, June 12, {\bf 2011}.

\item[{\bf C35.}] 
\label{C35}
{\bf ``Energy Efficient Data Management in Smartphone Networks''}, \\
{\bf Demetrios Zeinalipour-Yazti}
NSF-sponsored Workshop on Sustainable Energy-Efficient Data Management {\bf (SEEDM 2011)},
Arlington, Virginia, May 2-3, {\bf 2011}.

\item[{\bf C34.}] 
\label{C34}
{\bf An Indoor Trajectory Comparison Framework for Android Smartphones}, Christos Laoudias, Constantinos Costa, {\bf Demetrios Zeinalipour-Yazti}, Christos G. Panayiotou, Demo at the International Conference on Indoor Positioning and Indoor Navigation {\bf (IPIN 2011)}, Guimarães, Portugal, 21-23 Sept. {\bf 2011}.

\item[{\bf C33.}] 
\label{C33}
{\bf ``A Platform for the Evaluation of Fingerprint Positioning Algorithms on Android Smartphones''}, Christos Laoudias, George Constantinou, Marios Constantinides, Silouanos Nicolaou, {\bf D. Zeinalipour-Yazti}, Christos G. Panayiotou, Demo at the International Conference on Indoor Positioning and Indoor Navigation {\bf (IPIN 2011)}, Guimarães, Portugal, 21-23 Sept. {\bf 2011}.

\item[{\bf C32.}] 
\label{C32}
{\bf ``Multi-Objective Query Optimization in Smartphone Social Networks''}, \\
Andreas Konstantinidis, {\bf Demetrios Zeinalipour-Yazti}, Panayiotis Andreou, George Samaras 
{\em 12th IEEE International Conference on Mobile Data Management} {\bf (MDM 2011)}, Pages: 27-32, IEEE Computer Society, Volume 1. IEEE 2011, ISBN 978-1-4577-0581-6, Lule\aa, Sweden, June 6-9, {\bf 2011}.

\item[{\bf C31.}] 
\label{C31}
{\bf ``Disclosure-free GPS Trace Search in Smartphone Networks''}, \\
{\bf Demetrios Zeinalipour-Yazti}, Christos Laoudias, Maria I. Andreou, Dimitrios Gunopulos 
{\em 12th IEEE International Conference on Mobile Data Management} {\bf (MDM 2011)}, Pages: 78-87, IEEE Computer Society, Volume 1, IEEE 2011, ISBN 978-1-4577-0581-6, Lule\aa, Sweden, June 6-9, {\bf 2011}.

\item[{\bf C30.}] 
\label{C30}
{\bf ``SmartTrace: Finding Similar Trajectories in Smartphone Networks without Disclosing the Traces''}, 
Constandinos Costa, Christos Laoudias, {\bf Demetrios Zeinalipour-Yazti}, Dimitrios Gunopulos  
Demo at 27th International Conference on Data Engineering March {\bf (ICDE 2011)},  
ISBN 978-1-4244-8958-9, Pages: 1288-1291, IEEE Press, April 11-16, Hannover, Germany, {\bf 2011}.

\item[{\bf C29.}]
\label{C29}
{\bf ``Minimum-Hot-Spot Query Trees for Wireless Sensor Networks''}, \\
Georgios Chatzimilioudis, {\bf Demetrios Zeinalipour-Yazti}, Dimitrios Gunopulos,
Ninth International ACM Workshop on Data Engineering for Wireless and Mobile Access {\bf (MobiDE 2010)},
June 6, 2010, Indianapolis, Indiana, USA, Pages: 33-40, ACM Press, ISBN: 978-1-4503-0151-0, 
DOI:10.1145/1850822.1850829, {\bf 2010}.

\item[{\bf C28.}]
\label{C28}
{\bf ``Improving the Dependability of Computational Grids via Short-Term Failure Predictions''}, 
Artur Andrzejak, {\bf Demetrios Zeinalipour-Yazti}, Marios D. Dikaiakos,
CoreGRID ERCIM Working Group Workshop on Grids, P2P and Service computing
{\bf (EuroPAR 2009 Workshops)}, Springer Press Series, Delft, Netherlands, August 24, {\bf 2009}.  

\item[{\bf C27.}]
\label{C27}
{\bf ``FSort: External Sorting on Flash-based Sensor Devices''}, \\ 
Panayiotis Andreou, Orestis Spanos, {\bf Demetrios Zeinalipour-Yazti}, Panos K. Chrysanthis, George Samaras,  
{\em 6th Intl. Workshop on Data Management for Sensor Networks (DMSN 2009)}
{\bf (VLDB 2009 Workshops)}, Lyon, Paris, ACM International Conference Proceeding Series, ISBN: 978-1-60558-777-6, DOI: 10.1145 / 1594187.1594201, article 10, {\bf 2009}.  

\item[{\bf C26.}]
\label{C26}
{\bf ``Perimeter-Based Data Replication and Aggregation in Mobile Sensor Networks''}, \\
Panayiotis Andreou, {\bf Demetrios Zeinalipour-Yazti}, Maria I. Andreou, Panos K. Chrysanthis, George Samaras,  
{\em 10th International Conference on Mobile Data Management} {\bf (MDM 2009)},
Taipei, Taiwan, May 18-21, Pages: 244-251, IEEE Computer Society, ISBN: 978-0-7695-3650-7, {\bf 2009}.

\item[{\bf C25.}] 
\label{C25}
{\bf ``KSpot: Effectively Monitoring the K Most Important Events in a Wireless Sensor Network''}, 
Panayiotis Andreou, {\bf Demetrios Zeinalipour-Yazti}, Martha Vasiliadou, Panos K. Chrysanthis, George Samaras,  
Demo at the 25th International Conference on Data Engineering March {\bf (ICDE 2009)}, Shanghai, China, May 29 - April 4, 2009, Pages: 1503-1506, ISBN: 978-1-4244-3422-0., IEEE Computer Society, {\bf 2009}.

\item[{\bf C24.}]
\label{C24}
{\bf ``ETC: Energy-driven Tree Construction in Wireless Sensor Networks''}, \\
Panayiotis Andreou, Andreas Pamboris, {\bf Demetrios Zeinalipour-Yazti}, Panos K. Chrysanthis, George Samaras,  
{\em 2nd International Workshop on Sensor Network Technologies for Information Explosion Era (SeNTIE'09)}, 
{\bf (MDM 2009 Workshops)}, Taipei, Taiwan, 2009, Pages: 513-518., ISBN: 978-1-4244-4153-2, 
IEEE Computer Society, {\bf 2009}.  

\item[{\bf C23.}]
\label{C23}
{\bf ``Identifying Failures in Grids through Monitoring and Ranking''}, \\
{\bf Demetrios Zeinalipour-Yazti}, Kyriacos Neocleous, Chryssis Georgiou, Marios D. Dikaiakos, 
The 7th IEEE International Symposium on Network Computing and Applications {\bf (NCA 2008)},
Cambridge, MA USA, Pages: 291-298, IEEE Computer Society, July  10-12, {\bf 2008}.

\item[{\bf C22.}]
\label{C22}
{\bf ``Workload-aware Optimization of Query Routing Trees in Wireless Sensor Networks''}, \\
Panayiotis Andreou, {\bf Demetrios Zeinalipour-Yazti}, Panos K. Chrysanthis and George Samaras,
{\em IEEE/ACM 9th International Conference on Mobile Data Management} {\bf (MDM 2008)},
Beijing, China, Pages: 189-196, IEEE Computer Society, April 27-30, {\bf 2008}.

\item[{\bf C21.}]
\label{C21}
{\bf ``Seminar: Distributed Top-K Query Processing in Wireless Sensor Networks''}, \\
{\bf Demetrios Zeinalipour-Yazti} and Zografoula Vagena,
{\em IEEE/ACM 9th International Conference on Mobile Data Management} {\bf (MDM 2008)},
Beijing, China, Pages: 227, IEEE Computer Society, April 27-30, {\bf 2008}.

\item[{\bf C20.}]
\label{C20}
{\bf ``SenseSwarm: A Perimeter-based Data Acquisition Framework for Mobile Sensor Networks''}, \\
{\bf Demetrios Zeinalipour-Yazti}, Panayiotis Andreou, Panos K. Chrysanthis, George Samaras,
{\em 4th Intl. Workshop on Data Management for Sensor Networks}
{\bf (DMSN 2007)}, ACM International Conference Proceeding Series; Volume 273,
Pages: 13-18, Vienna, Austria, {\bf 2007}.  

\item[{\bf C19.}]
\label{C19}
{\bf ``FailRank: Towards a Unified Grid Failure Monitoring and Ranking System''}, \\
{\bf Demetrios Zeinalipour-Yazti}, Kyriacos Neocleous, Chryssis Georgiou, Marios D. Dikaiakos, 
In CoreGrid Springer Volume of Selected Papers from the {\bf (Coregrid 2007 Workshop)}
on Grid Programming Models and P2P Systems Architecture, Heraklion, Greece, {\bf 2007}.

\item[{\bf C18.}]
\label{C18}
{\bf ``The MicroPulse Framework for Adaptive Waking Windows in Sensor Networks''}, \\
{\bf Demetrios Zeinalipour-Yazti}, Panayiotis Andreou, Panos K. Chrysanthis, George Samaras and Andreas Pitsillides, 
IEEE First International Workshop on Data Intensive Sensor Networks (DISN)
{\bf (MDM 2007 Workshops)}, Mannheim, Germany, Pages: 351-355, ISBN: 1-4244-1241-2, IEEE Computer Society, May 11, {\bf 2007}.
 

\item[{\bf C17.}]
\label{C17}
{\bf ``Intensive Care Window: A multi-modal monitoring tool for Intensive Care Research and Practice''},\\
Harald Gjermundrod, Marios Papa, {\bf Demetrios Zeinalipour-Yazti}, Marios D. Dikaiakos, George Panayi, Theodoros Kyprianou, {\em 20th IEEE International Symposium on Computer-Based Medical Systems {\bf (CBMS 2007)}},
IEEE Computer Society ISBN 0-7695-2905-4,  Pages: 471-476, June 20-22, Maribor, Slovenia, {\bf 2007}.

\item[{\bf C16.}]
\label{C16}
{\bf ``ICGrid: Enabling Intensive Care Medical Research on the EGEE Grid''}, \\
Harald Gjermundrod, Marios D. Dikaiakos, {\bf Demetrios Zeinalipour-Yazti}, George Panayi, Theodoros Kyprianou,
$5^{th}$ HealthGrid Conference  {\bf (HealthGrid 2007)}, April 24-27, Pages: 248-257, IOS Press, {\bf 2007}.  

\item[{\bf C15.}]
\label{C15}  
{\bf ``MINT Views: Materialized In Network Top-k Views in Sensor Networks''}, \\
{\bf Demetrios Zeinalipour-Yazti}, Panayiotis Andreou, Panos K. Chrysanthis, George Samaras, 
{\em IEEE/ACM 8th International Conference on Mobile Data Management} {\bf (MDM 2007)},
Mannheim, Germany, May 7 - 11, ISBN 14244-1240-4, Pages: 182-189, IEEE Press, {\bf 2007}. 

\item[{\bf C14.}]
\label{C14}  
{\bf ``Distributed Spatio-Temporal Trajectory Retrieval''}, \\
{\bf Demetrios Zeinalipour-Yazti}, Song Lin, Dimitrios Gunopulos, 
{\em ACM 15th Conference on Information and Knowledge Management} {\bf (CIKM 2006)}, 
November 6-11, Arlington, VA, USA, Pages: 14-23, ACM Press, ISBN 1-59593-433-2, {\bf 2006}. 

\item[{\bf C13.}]
 \label{C13}  
{\bf ``Efficient Online State Tracking Using Sensor Networks''}, \\
Maria Halkidi, Vana Kalogeraki, Dimitrios Gunopulos, Dimitris Papadopoulos, {\bf Demetrios Zeinalipour-Yazti} and Michail Vlachos
{\em IEEE/ACM 7th International Conference on Mobile Data Management} {\bf (MDM 2006)},
Nara, Japan, May 10-12, p. 24-32, {\bf 2006}. 

\item[{\bf C12.}]
 \label{C12} 
{\bf ``MicroHash: An Efficient Index for Sensor Nodes with External Flash Memories''}, \\
{\bf Demetrios Zeinalipour-Yazti}, Song Lin, Vana Kalogeraki, Dimitrios Gunopulos, Walid Najjar, 
{\em 4th USENIX Conference on File and Storage Technologies} {\bf (FAST 2005)},
San Francisco, CA, December 14-16, Pages: 31-44, {\bf 2005}.

\item[{\bf C11.}]
\label{C11} 
{\bf ``The Threshold Join Algorithm for Top-k Queries in Distributed Sensor Networks''},\\
{\bf Demetrios Zeinalipour-Yazti}, Zografoula Vagena, Dimitrios Gunopulos, Vana Kalogeraki, Vassilis Tsotras, Michail Vlachos, Nick Koudas, Divesh Srivastava, 
{\em 2nd Intl. Workshop on Data Management for Sensor Networks}
{\bf (DMSN 2005)}, Trondheim, Norway,
ACM Intl. Conference Proceeding Series; Volume 96, Pages: 61-66, {\bf 2005}.

\item[{\bf C10.}]
\label{C10}
{\bf RISE Co-S : High Performance Sensor Storage and Co-Processing Architecture}, \\
Anirban Banerjee, Abhishek Mitra, Walid Najjar, {\bf Demetrios Zeinalipour-Yazti}, Vana Kalogeraki and Dimitrios Gunopulos,  
Second Annual IEEE Communications Society Conference on Sensor and Ad Hoc Communications and Networks {\bf (SECON 2005)},
Santa Clara, California, USA, {\bf 2005}.

\item[{\bf C9.}]
\label{C9}
{\bf ``High-Performance Low Power Sensor Platforms Featuring Gigabyte Scale Storage''}, \\
Abhishek Mitra, Anirban Banerjee, Walid Najjar, {\bf Demetrios Zeinalipour-Yazti}, Vana Kalogeraki and Dimitrios Gunopulos,  
IEEE/ACM 3rd International Workshop on Measurement, Modeling, and Performance Analysis of Wireless Sensor Networks'', 
{\bf (SenMetrics 2005)}, San Diego, CA, {\bf 2005}.

\item[{\bf C8.}]
 \label{C8}
{\bf ``Data Acquisition in Sensor Networks with Large Memories''},\\
{\bf Demetrios Zeinalipour-Yazti}, Som Neema, Dimitrios Gunopulos, Vana Kalogeraki, Walid Najjar, 
{\em IEEE International Workshop on Networking Meets Databases},
{\bf (NetDB 2005)}, collocated with IEEE ICDE 2005, Pages: 1188-, Tokyo, Japan,  {\bf 2005}.

\item[{\bf C7.}]
\label{C7}
{\bf ``NODES: A Novel System Design for Embedded Sensor Networks''},\\
Som Neema, Abhishek Mitra, Anirban Banerjee, Walid Najjar, {\bf Demetrios Zeinalipour-Yazti}, Dimitrios Gunopulos, Vana Kalogeraki,
{\em IEEE Intl. Conference on Information Processing in Sensor Networks {\bf (IPSN 2005)}}, 
Los Angeles, CA, USA {\bf 2005}.

\item[{\bf C6.}]
\label{C6}
{\bf ``Towards Self-Managing QoS-Enabled Peer-to-Peer Systems''},\\
Vana Kalogeraki, Fang Chen, Thomas Repantis and {\bf Demetrios Zeinalipour-Yazti},
In Post-Proceedings of the workshop SELF-STAR: Self-* Properties in Complex Information Systems, 
Hot Topics in Computer Science, LNCS Volume 3460, Pages: 325-342, May {\bf 2005}.

\item[{\bf C5.}]
\label{C5} 
{\bf ``On Constructing Internet-Scale P2P Information Retrieval Systems''},\\
{\bf Demetrios Zeinalipour-Yazti}, Vana Kalogeraki and Dimitrios Gunopulos
{\em International Workshop On Databases, s and P2P Computing ``DBISP2P''}
{\bf (VLDB 2004 Workshops)}, LNCS Volume 3367, Pages: 136-150, Toronto, Canada, {\bf 2004}.

\item[{\bf C4.}] 
\label{C4} 
{\bf ``A Local Search Mechanism for Peer-to-Peer Networks''}, \\
Vana Kalogeraki, Dimitrios Gunopulos and {\bf Demetrios Zeinalipour-Yazti},
{\em ACM 11th International Conference on Information and Knowledge Management}
{\bf (CIKM 2002)}, Pages: 300-307, McLean, Virginia, USA, {\bf 2002}.

\item[{\bf C3.}]
\label{C3}
{\bf ``Design and Implementation of a Distributed Crawler and Filtering Processor''}, \\
{\bf Demetrios Zeinalipour-Yazti} and Marios D. Dikaiakos,
{\em 5th Intl. Workshop on Next Generation Information Technologies and Systems} {\bf (NGITS 2002)}, 
LNCS Volume 2382, Pages: 58-74, Eds. A. Halevy and A. Gal., Caesarea, Israel, {\bf 2002}.

\item[{\bf C2.}]
\label{C2}
{\bf ``WebRACE: A Distributed WWW Retrieval, Annotation, and Caching Engine''}, \\
{\bf Demetrios Zeinalipour-Yazti} and Marios D. Dikaiakos. {\em International Workshop on Performance-oriented} 
{\em Application Development for Distributed Architectures} {\bf (PADDA 2001)}, Munich, Germany, {\bf 2001}. 	

\item[{\bf C1.}] 
\label{C1}
{\bf ``Collaboration through Navigation: The Case of a Web-based Helpdesk System''},\\
Marios D. Dikaiakos, {\bf Demetrios Zeinalipour-Yazti}. Poster at the {\em  9th International World-Wide Web Conference} {\bf (WWW 2000)}, Pages: 96-97, Amsterdam, Netherlands, {\bf 2000}.   

\end{enumerate}


\subsection*{EDITORIALS}
\begin{enumerate}

\item[{\bf E9.}]
\label{E9}
{\bf ``Welcome message from MUSICAL 2016 chairs''}',  \\
Kazushige Ouchi, Takuya Yoshihiro, Yuka Kato, Tomoyuki Yashiro and {\bf Demetrios Zeinalipour-Yazti},
13th International Conference on Mobile and Ubiquitous Systems: Computing, Networking and Services, MobiQuitous 2016; Hiroshima; Japan; 28 Nov. 2016 - 1 Dec. 2016, ACM International Conference Proceeding Series, p. vi. {\bf 2016}.

\item[{\bf E8.}]
\label{E8}
{\bf ``Human Mobility Computing and Privacy: Fad or Reality?},  \\
Adam J. Lee, Konstantinos Pelechrinis and {\bf Demetrios Zeinalipour-Yazti},
16th IEEE International Conference on Mobile Data Management, Pittsburgh, PA, 2015, pp. 42-43.
doi: 10.1109/MDM.2015.86, {\bf 2015}.


\item[{\bf E7.}]
\label{E7}
{\bf ``Future directions in sensor data management: a panel discussion},  \\
{\bf Demetrios Zeinalipour-Yazti},
In Proceedings of the Seventh International Workshop on Data Management for Sensor Networks (DMSN '10). ACM, New York, NY, USA, 39-39. DOI=http://dx.doi.org/10.1145/1858158.1858170, {\bf 2010}.

\item[{\bf E6.}]
\label{E6}
{\bf ``Proceedings of the Tenth IEEE International Conference on Data Mining Contest (ICDM Contest 2010)},  \\
Editors: Marcin Wojnarski, Pawel Gora, Marcin Szczuka, Hung Son Nguyen, Joanna Swietlicka and {\bf Demetrios Zeinalipour-Yazti}, Sydney, Australia, 14-17 Dec. 2010. IEEE Computer Society, {\bf 2010}.

\item[{\bf E5.}]
\label{E5}
{\bf ``Proceedings of the 7th Intl. Workshop on Data Management for Sensor Networks (DMSN 2010)},
in conjunction with VLDB, \\
Editors: {\bf Demetrios Zeinalipour-Yazti} and Wang-Chien Lee, Singapore, September 13, 2010, ACM International Conference Proceeding Series, ACM Press, ISBN 978-1-4503-0416-0, {\bf 2010}.

\item[{\bf E4.}]
\label{E4}
{\bf ``Proceedings of the
16th Intl. Conference on Parallel Processing (Euro-Par 2010)}, \\
Editors: Rizos Sakellariou, Salvatore Orlando, Josep-Lluis Larriba-Pey, Srinivasan Parthasarathy, \\ {\bf Demetrios Zeinalipour-Yazti},  Ischia, Italy, August 31 - September 3, 2010, Proceedings, Part I. Lecture Notes in Computer Science 6271, Springer Press, ISBN 978-3-642-15276-4, {\bf 2010}.

\item[{\bf E3.}]
\label{E3}
{\bf ``Proceedings of the 9th ACM International Workshop on Data Engineering for Wireless and Mobile Access'' ({\bf MobiDE 2010})}, in conjunction with SIGMOD/PODS,\\
Editors: Phillip B. Gibbons, {\bf Demetrios Zeinalipour-Yazti}, Hui Lei, Suman Nath, June 29, 2010, Providence, Rhode Island, USA, ACM Press, ISBN 978-1-4503-0151-0, {\bf 2010}.

\item[{\bf E2.}]
\label{E2}
{\bf ``Proceedings of the 11th Intl. Conference on Mobile Data Management ({\bf MDM 2010})}'', \\
Editors: Takahiro Hara, Christian S. Jensen, Vijay Kumar, Sanjay Madria,  {\bf Demetrios Zeinalipour-Yazti}, Kansas City, Missouri, USA, 23-26 May 2010. IEEE CS, ISBN 978-0-7695-4048-1, {\bf 2010}.

\item[{\bf E1.}]
\label{E1}
{\bf ``Proceedings of the 8th ACM International Workshop on Data Engineering for Wireless and Mobile Access'' (MobiDE 2009)}, in conjunction with SIGMOD/PODS, \\
Editors: Yannis Kotidis, Pedro Jose Marron, Le Gruenwald, {\bf Demetrios Zeinalipour-Yazti}, June 29, 2009, Providence, Rhode Island, USA, ACM Press, ISBN 978-1-60558-712-7, {\bf 2009}.

\end{enumerate}


\subsection*{BOOK CHAPTERS AND NEWSLETTERS}
\begin{enumerate}

\item[{\bf B11.}]
\label{B11}
{\bf ``The Anatomy of the Anyplace Indoor Navigation Service''} \\
{\bf Demetrios Zeinalipour-Yazti} and Christos Laoudias, 
{\bf ACM SIGSPATIAL Special}, {\em Special Issue on Indoor Spatial Awareness II (invited)},
Editor: Chi-Yin Chow, 8 pages, {\bf 2017}. {\bf (in-press)}

\item[{\bf B10.}]
\label{B10}
{\bf ``Privacy-Preserving Indoor Localisation and Navigation''} \\
Andreas Konstantinidis, Georgios Chatzimilioudis and {\bf Demetrios Zeinalipour-Yazti}
{\em  News, No. 106, Special Issue on Cybersecurity}, ERCIM EEIG, ISSN: 0926-4981, July {\bf 2016}.

\item[{\bf B9.}]
\label{B9}
{\bf ``Nearest Neighbor Queries on Big Data''} \\
Georgios Chatzimilioudis, Andreas Konstantinidis and {\bf Demetrios Zeinalipour-Yazti}
Information Granularity, Big Data, and Computational Intelligence; Springer Verlag, Volume 8,
Editor(s): Witold Pedrycz and Shyi-Ming Chen, Pages: 3--22, ISBN: 978-3-319-08253-0, {\bf 2015}.

%
\item[{\bf B8.}] 
\label{B8}
{\bf ``A P2P Search Framework for Intelligent Crowdsourcing in Mobile Social Networks''} \\
Andreas Konstantinidis and {\bf Demetrios Zeinalipour-Yazti}
Opportunistic Mobile Social Networks, CRC Press, Taylor \& Francis Group, Published: August 14, 2014 by CRC Press, Editor(s): Jie Wu, Yunsheng Wang, Pages: 377--405, ISBN: 978-1-4665-9494-4, {\bf 2014}.

\item[{\bf B7.}]
\label{B7}
{\bf ``Airplace: Indoor Geolocation on Smartphones through WiFi Fingerprinting''}, \\
C. Laoudias, G. Larkou, {\bf D. Zeinalipour-Yazti} and C. G. Panayiotou
{\em  News, No. 93, Special Issue on Mobile Computing}, ERCIM EEIG, ISSN: 0926-4981, April {\bf 2013}.

\item[{\bf B6.}]
\label{B6}
{\bf ``SmartLab: Empowering Mobile Computing Research through an Open Smartphone Cloud''}, \\
G. Larkou, P. Andreou, A. Konstantinides and {\bf D. Zeinalipour-Yazti}
{\em ERCIM News, No. 93, Special Issue on Mobile Computing}, ERCIM EEIG, ISSN: 0926-4981, April {\bf 2013}.
 
\item[{\bf B5.}] 
\label{B5}
{\bf ``Online Social Networks: Status and Trends''} \\
George Pallis, {\bf Demetrios Zeinalipour-Yazti} and Marios D. Dikaiakos
New Directions in Web Data Management 1, Studies in Computational Intelligence, 
Volume 331, Vakali, Athena; Jain, Lakhmi C (Eds.), Springer Press, Volume 331, Pages: 213--234,
Berlin Heidelberg, ISBN: 978-3-642-17550-3 {\bf 2011}.

\item[{\bf B4.}] 
\label{B4}
{\bf ``Improving the Dependability of Computational Grids via Short-Term Failure Predictions''}, \\
Artur Andrzejak, {\bf Demetrios Zeinalipour-Yazti}, Marios D. Dikaiakos,
{\bf Grids, P2P and Services Computing}, Desprez, F.; Getov, V.; Priol, T.; Yahyapour, R. (Eds.)
1st Edition., 2010, XIV, 202 p., Hardcover, ISBN: 978-1-4419-6793-0, Springer Press, {\bf 2010}.

\item[{\bf B3.}] 
\label{B3}
{\bf ``Mobile Sensor Network Data Management''} \\
{\bf Demetrios Zeinalipour-Yazti}, Panos K. Chrysanthis, 
{\bf Encyclopedia of Database Systems (EBDS)},
Liu, Ling; \"Ozsu, M. Tamer (Eds.), 1st Edition.,  LXX, 3752 p. 60 illus.,
ISBN: 978-0-387-49616-0, {\bf 2009}.

\item[{\bf B2.}] 
\label{B2}
{\bf ``FailRank: Towards a Unified Grid Failure Monitoring and Ranking System''} \\
{\bf Demetrios Zeinalipour-Yazti}, Kyriacos Neocleous, Chryssis Georgiou, Marios D. Dikaiakos, 
{\bf Making Grids Work}, Pages: 247-259, Edited by Marco Danelutto, P. Fragopoulou and V. Getov, 
Springer Press, ISBN-13 :978-0-387-78447-2, {\bf 2008}.

\item[{\bf B1.}] 
\label{B1}
{\bf ``Top-K Retrieval Techniques in Distributed Sensor Networks''},\\
Song Lin, {\bf Demetrios Zeinalipour-Yazti}, Dimitrios Gunopulos, 
{\bf Encyclopedia of Geographic Information Systems (EGIS)},
Shekhar, Shashi; Xiong, Hui (Eds.), Hardcover book, Springer Press, ISBN: 978-0-387-30858-6, {\bf 2008}.
\end{enumerate}


\subsection*{\bf THESES}
\begin{itemize}
\item [{\bf T3.}]
\label{T3}
{\bf ``Search and Retrieval Algorithms for Distributed Data Management Systems''}, \\
{\bf Demetrios Zeinalipour-Yazti}, PhD Dissertation,  
{\em Dept. of Computer Science \& Engineering, University of California - Riverside}, 
August {\bf 2005}.    

\item [{\bf T2.}]
\label{T2}
{\bf ``Information Retrieval in Peer-to-Peer Systems''}, \\
{\bf Demetrios Zeinalipour-Yazti}, M.Sc. Thesis,  
{\em Dept. of Computer Science \& Engineering, University of California - Riverside}, 
June {\bf 2003}.    

\item [{\bf T1.}]
\label{T1}
{\bf ``eRACE: eXtensible Retrieval Annotation and Caching Engine''}, \\
{\bf Demetrios Zeinalipour-Yazti}, B.Sc. Thesis,  
{\em Dept. of Computer Science, University of Cyprus}, 
July {\bf 2000}.

\end{itemize}


\subsection*{\bf  GREEK CONFERENCES}
\begin{enumerate}

\item[{\bf G30.}]
\label{G30} % HDMS18-DP
{\bf ``Decaying Telco Big Data with Data Postdiction''}, \\
Constantinos Costa, Andreas Charalampous, Andreas Konstantinidis, {\bf Demetrios Zeinalipour-Yazti}, and Mohamed F. Mokbel,
{\em The 16th Hellenic Data Management Symposium} {\bf (HDMS 2018)}, 10 pages
Larnaca, Cyprus, July 2-4, {\bf 2018}. (unofficial proceedings)

\item[{\bf G29.}]
\label{G29} % MDM'18-FMS-DEMO
{\bf ``FMS: Managing Crowdsourced Indoor Signals with the Fingerprint Management Studio''}, \\
Marileni Angelidou, Constantinos Costa, Artyom Nikitin and {\bf Demetrios Zeinalipour-Yazti},
{\em The 16th Hellenic Data Management Symposium} {\bf (HDMS 2018)}, 2 pages
Larnaca, Cyprus, July 2-4, {\bf 2018}. (unofficial proceedings)

\item[{\bf G28.}]
\label{G28} % HDMS18-MDM18-DP-DEMO
{\bf ``TBD-DP: Telco Big Data Visual Analytics with Data Postdiction''}, \\
Constantinos Costa, Andreas Charalampous, Andreas Konstantinidis, {\bf Demetrios Zeinalipour-Yazti}, and Mohamed F. Mokbel
{\em The 16th Hellenic Data Management Symposium} {\bf (HDMS 2018)}, 2 pages
Larnaca, Cyprus, July 2-4, {\bf 2018}. (unofficial proceedings)

\item[{\bf G27.}]
\label{G27} % HDMS18-SIGMOD18-EPUI
{\bf ``EPUI: Experimental Platform for Urban Informatics''}, \\
Xiaoyi Ge, Panos K. Chrysanthis, Konstantinos Pelechrinis, and {\bf Demetrios Zeinalipour-Yazti}
{\em The 16th Hellenic Data Management Symposium} {\bf (HDMS 2018)}, 4 pages
Larnaca, Cyprus, July 2-4, {\bf 2018}. (unofficial proceedings)

\item[{\bf G26.}]
\label{G26}
{\bf ``Indoor Localization Accuracy Estimation from Fingerprint Data''}, \\
Artyom Nikitin, Christos Laoudias,  Georgios Chatzimilioudis, Panagiotis Karras and {\bf Demetrios Zeinalipour-Yazti},
{\em The 15th Hellenic Data Management Symposium} {\bf (HDMS 2017)}, 10 pages
Athens, Greece, August 24-25, {\bf 2017}. (unofficial proceedings)

\item[{\bf G25.}]
\label{G25}
{\bf ``ACCES: Offline Accuracy Estimation for Fingerprint-based Localization''}, \\
Artyom Nikitin, Christos Laoudias,  Georgios Chatzimilioudis, Panagiotis Karras and {\bf Demetrios Zeinalipour-Yazti},
{\em The 15th Hellenic Data Management Symposium} {\bf (HDMS 2017)}, 2 pages,
Athens, Greece, August 24-25, {\bf 2017}. (unofficial proceedings)

\item[{\bf G24.}]
\label{G24}
{\bf ``Efficient Exploration of Telco Big Data with Compression and Decaying''}, \\
Constantinos Costa, Georgios Chatzimilioudis, {\bf Demetrios Zeinalipour-Yazti} and Mohamed F. Mokbel,
{\em The 15th Hellenic Data Management Symposium} {\bf (HDMS 2017)}, 2 pages,
Athens, Greece, August 24-25, {\bf 2017}. (unofficial proceedings)

\item[{\bf G23.}]
\label{G23}
{\bf ``SPATE: Compacting and Exploring Telco Big Data''}, \\
Constantinos Costa, Georgios Chatzimilioudis, {\bf Demetrios Zeinalipour-Yazti}, and Mohamed F. Mokbel,
{\em The 15th Hellenic Data Management Symposium} {\bf (HDMS 2017)}, 12 pages,
Athens, Greece, August 24-25, {\bf 2017}. (unofficial proceedings)

\item[{\bf G22.}]
\label{G22}
{\bf ``Distributed In-Memory Processing of All k Nearest Neighbor Queries''}, \\
Georgios Chatzimilioudis, Constantinos Costa, {\bf Demetrios Zeinalipour-Yazti} and
Wang-Chien Lee and Evaggelia Pitoura,
{\em The 14th Hellenic Data Management Symposium} {\bf (HDMS 2016)},
Athens, Greece, July 28-29, {\bf 2016}. (unofficial proceedings)

\item[{\bf G21.}]
\label{G21}
{\bf ``Privacy-Preserving Indoor Localization on Smartphones''}, \\
Andreas Konstantinidis, Georgios Chatzimilioudis, {\bf Demetrios Zeinalipour-Yazti}, Paschalis Mpeis, Nikos Pelekis, and Yannis Theodoridis,
{\em The 14th Hellenic Data Management Symposium} {\bf (HDMS 2016)},
Athens, Greece, July 28-29, {\bf 2016}. (unofficial proceedings)

\item[{\bf G20.}]
\label{G20}
{\bf ``RadioMap Prefetching for Indoor Navigation in Intermittently Connected Wi-Fi Networks''}, \\
Andreas Konstantinidis, George Nikolaides, Georgios Chatzimilioudis, Giannis Evagorou,  {\bf Demetrios Zeinalipour-Yazti} and Panos K. Chrysanthis,
{\em The 13th Hellenic Data Management Symposium} {\bf (HDMS 2015)},
Athens, Greece, July 30-31, {\bf 2015}. (unofficial proceedings)

\item[{\bf G19.}]
\label{G19}
{\bf ``Anyplace: A Crowdsourced Indoor Information Service''}, \\
Kyriakos Georgiou, Timotheos Constambeys, Christos Laoudias, Lambros Petrou, Georgios Chatzimilioudis and  {\bf Demetrios Zeinalipour-Yazti}
{\em The 13th Hellenic Data Management Symposium} {\bf (HDMS 2015)},
Athens, Greece, July 30-31, {\bf 2015}. (unofficial proceedings)

\item [{\bf G18.}]
\label{G18}
{\bf ``Continuous All k-Nearest Neighbor Querying in Smartphone Networks''}, \\
Georgios Chatzimilioudis, {\bf Demetrios Zeinalipour-Yazti}, Wang-Chien Lee, Marios D. Dikaiakos,
{\em The 11th Hellenic Data Management Symposium} {\bf (HDMS 2012)}, 
Chania, Greece, June 28-29, {\bf 2012}. (unofficial proceedings)

\item [{\bf G17.}]
\label{G17}
{\bf ``Proximity Interactions with Crowdcast''}, \\
Marios Constantinides, George Constantinou, Andreas Panteli, Theophilos Phokas, Georgios Chatzimilioudis, {\bf Demetrios Zeinalipour-Yazti}
{\em The 11th Hellenic Data Management Symposium} {\bf (HDMS 2012)}, 
Chania, Greece, June 28-29, {\bf 2012}. (unofficial proceedings)

\item [{\bf G16.}]
\label{G16}
{\bf ``Continuous All k-Nearest Neighbor Querying in Smartphone Networks''}, \\
Georgios Chatzimilioudis, {\bf Demetrios Zeinalipour-Yazti}, Wang-Chien Lee, Marios D. Dikaiakos,
{\em The 11th Hellenic Data Management Symposium} {\bf (HDMS 2012)}, 
Chania, Greece, June 28-29, {\bf 2012}. (unofficial proceedings)

\item [{\bf G15.}]
\label{G15}
{\bf ``Multi-Objective Query Optimization in Smartphone Social Networks''}, \\
Andreas Konstantinidis, {\bf Demetrios Zeinalipour-Yazti}, Panayiotis Andreou, George Samaras 
{\em The 10th Hellenic Data Management Symposium} {\bf (HDMS 2011)}, 
Athens, Greece, June 17-18, {\bf 2011}. (unofficial proceedings)

\item [{\bf G14.}]
\label{G14}
{\bf ``Disclosure-free GPS Trace Search in Smartphone Networks''}, \\
{\bf Demetrios Zeinalipour-Yazti}, Christos Laoudias, Maria I. Andreou, Dimitrios Gunopulos 
{\em The 10th Hellenic Data Management Symposium} {\bf (HDMS 2011)}, 
Athens, Greece, June 17-18, {\bf 2011}. (unofficial proceedings)

\item [{\bf G13.}]
\label{G13}
{\bf ``SmartTrace: Finding Similar Trajectories in Smartphone Networks without Disclosing the Traces''}, \\
Constandinos Costa, Christos Laoudias, {\bf Demetrios Zeinalipour-Yazti}, Dimitrios Gunopulos  
Demo at {\em The 10th Hellenic Data Management Symposium} {\bf (HDMS 2011)}, 
Athens, Greece, June 17-18, {\bf 2011}.  (unofficial proceedings)

\item [{\bf G12.}]
\label{G12}
{\bf ``Socially-aware Query Routing in Mobile Networks''}, \\
Andreas Konstantinidis, {\bf Demetrios Zeinalipour-Yazti}, Kun Yang,
{\em The 9th Hellenic Data Management Symposium} {\bf (HDMS 2010)}, 
Ayia Napa, Cyprus, June 30 - July 3, {\bf 2010}. (unofficial proceedings)

\item [{\bf G11.}]
\label{G11}
{\bf ``Minimum-Hot-Spot Query Trees for Wireless Sensor Networks''}, \\
Georgios Chatzimilioudis, {\bf Demetrios Zeinalipour-Yazti}, Dimitrios Gunopulos,
{\em The 9th Hellenic Data Management Symposium} {\bf (HDMS 2010)}, 
Ayia Napa, Cyprus, June 30 - July 3, {\bf 2010}.  (unofficial proceedings)

\item [{\bf G10.}]
\label{G10}
{\bf ``A Distributed Spatio-Temporal Similarity Search Framework using Android-based Smartphones (demo)''}, \\
Constandinos Costa, Constandinos Christoforou, George Nicolaides, Diomidis Papadiomidous, Christos Laoudias, {\bf Demetrios Zeinalipour-Yazti}
{\em The 9th Hellenic Data Management Symposium} {\bf (HDMS 2010)}, 
Ayia Napa, Cyprus, June 30 - July 3, {\bf 2010}. (unofficial proceedings)

\item [{\bf G9.}]
\label{G9}
{\bf ``Perimeter-Based Data Replication and Aggregation in Mobile Sensor Networks''}, \\
Panayiotis Andreou, {\bf Demetrios Zeinalipour-Yazti}, Maria I. Andreou, Panos K. Chrysanthis, George Samaras,  
{\em The 8th Hellenic Data Management Symposium} {\bf (HDMS 2009)}, 
Athens, Greece, 28-29 August {\bf 2009}.  (unofficial proceedings)

\item [{\bf G8.}]
\label{G8}
{\bf ``KSpot: Effectively Monitoring the K Most Important Events in a Wireless Sensor Network (demo)''}, \\
Panayiotis Andreou, {\bf Demetrios Zeinalipour-Yazti}, Martha Vasiliadou, Panos K. Chrysanthis, George Samaras,  
{\em The 8th Hellenic Data Management Symposium} {\bf (HDMS 2009)}, 
Athens, Greece, 28-29 August {\bf 2009}. (unofficial proceedings)

\item [{\bf G7.}]
\label{G7}
{\bf ``Workload-aware Optimization of Query Routing Trees in Wireless Sensor Networks''}, \\
Panayiotis Andreou, {\bf Demetrios Zeinalipour-Yazti}, Panos K. Chrysanthis and George Samaras,
{\em The 7th Hellenic Data Management Symposium} {\bf (HDMS 2008)}, 
Heraklion, Greece, 28-29 July {\bf 2008}. (unofficial proceedings)

\item [{\bf G6.}]
\label{G6}  
{\bf ``MINT Views: Materialized In Network Top-k Views in Sensor Networks''}, \\
{\bf Demetrios Zeinalipour-Yazti}, Panayiotis Andreou, Panos K. Chrysanthis, George Samaras, 
{\em The 6th Hellenic Data Management Symposium} {\bf (HDMS 2007)}, 
Athens, Greece, 5-6 July, {\bf 2007}. (unofficial proceedings)

\item [{\bf G5.}]
\label{G5}  
{\bf ``Distributed Spatio-Temporal Trajectory Retrieval''}, \\
{\bf Demetrios Zeinalipour-Yazti}, Song Lin, Dimitrios Gunopulos, 
{\em The 6th Hellenic Data Management Symposium} {\bf (HDMS 2007)}, 
Athens, Greece, 5-6 July, {\bf 2007}. (unofficial proceedings)

\item [{\bf G4.}]
\label{G4}
{\bf ``Automatically Annotating the ODP Web Taxonomy''},\\
Christiana Christophi, {\bf Demetrios Zeinalipour-Yazti}, Marios D. Dikaiakos, George Paliouras,
{\em 10th Panhellenic Conference on Informatics {\bf (PCI 2007)}}, Web Search and Mining,
Patras, Greece, Springer Press, {\bf 2007}. 

\item [{\bf G3.}]
\label{G3}
{\bf ``Efficient Online State Tracking Using Sensor Networks''}, \\
Maria Halkidi, Vana Kalogeraki, Dimitrios Gunopulos, Dimitris Papadopoulos, {\bf Demetrios Zeinalipour-Yazti} and Michail Vlachos,
{\em Hellenic Data Management Symposium} {\bf (HDMS 2006)},
Thessaloniki, Greece, September 7-8,  {\bf 2006}.  (unofficial proceedings)

\item [{\bf G2.}]
\label{G2}  
{\bf ``Towards In-Situ Data Storage in Sensor Databases''}, \\
{\bf Demetrios Zeinalipour-Yazti}, Vana Kalogeraki, Dimitrios Gunopulos, Abhishek Mitra, Arnirban Banerjee, and Walid Najjar
{\em 10th Panhellenic Conference on Informatics {\bf (PCI 2005)}},
Volos, Greece, LNCS Volume 3746, Pages 36-46, {\bf 2005}.

\item [{\bf G1.}]
\label{G1}
{\bf ``High-Performance Crawling and Filtering in Java''},\\
{\bf Demetrios Zeinalipour-Yazti} and Marios D. Dikaiakos, 
{\em Proceedings of the 8th Panhellenic Conference on Informatics} {\bf (PCI 2001)},
Volume 2, Pages: 377-386, Nicosia, Cyprus, {\bf 2001}.

\end{enumerate}



\subsection*{\bf NON-REFEREED WORK}
\begin{enumerate}

\item [{\bf N7.}]
\label{N7}
{\bf ``D.SA.04 - Report on the four years of joint activities, open topics and future research in Architectural issues: scalability, dependability, adaptability''},\\
A. Andrjezak, C. Mastroianni, P. Fragopoulou, D. Kondo, P. Malecot, A. Reinefeld, F. Schintke, T. Schutt, G.-C. Silaghi, L.M. Silva, P. Trunfio, {\bf D. Zeinalipour-Yazti}, E. Zimeo 
CoreGRID, August 31, 2008, CoreGRID - Network of Excellence, {\bf 2008}. 

\item [{\bf N6.}]
\label{N6}
{\bf ``Grid Architectural Issues: State-of-the-art and Future Trends''},\\
A. Andrjezak, C. Mastroianni, P. Fragopoulou, D. Kondo, P. Malecot, A. Reinefeld, F. Schintke, T. Schutt, G.-C. Silaghi, L.M. Silva, P. Trunfio, {\bf D. Zeinalipour-Yazti}, E. Zimeo 
CoreGRID White Paper, Number WHP-00XX, May 30, 2008, Institute on Architectural Issues: Scalability, Dependability, Adaptability, CoreGRID - Network of Excellence, {\bf 2008}.

\item [{\bf N5.}]
\label{N5}
{\bf ``Intensive Care Window: A multi-modal, grid infrastructure related monitoring tool for Intensive Care Clinical Practice''}, \\
Theodoros Kyprianou, George Panayi, {\bf Demetrios Zeinalipour-Yazti}, Marios D. Dikaiakos, 
Intensive Care Medicine Journal, Abstracts of the 20th ESICM Annual Congress Berlin, Germany, Abstract 0173,
Volume 33, Supplement 2, Springer {\bf 2007}.

\item [{\bf N4.}]
\label{N4}
{\bf ``ICGrid: Intensive Care Grid''}, \\
{\bf Demetrios Zeinalipour-Yazti}, Marios D. Dikaiakos, Harald Gjermundrod, Marios Papas, Theodoros Kyprianou, George Panayi, 
{\em  Demonstration at the Europe's Information Society Technologies Conference} {\bf (IST 2006)},  
Helsinki, Finland, 21-23 November {\bf 2006}.  

\item [{\bf N3.}]
\label{N3}
{\bf ``ICGrid: Intensive Care Grid''}, \\
{\bf Demetrios Zeinalipour-Yazti}, Marios D. Dikaiakos, Harald Gjermundrod, Marios Papas, Theodoros Kyprianou, George Panayi, 
{\em  Demo at the CoreGRID Industrial Conference} {\bf (CIC 2006)},
Sophia Antipolis, France, Nov 30-Dec 1, {\bf 2006}. {\bf (Best Demo Award)}

\item [{\bf N2.}]
\label{N2}
{\bf ``ICGrid: Intensive Care Grid''}, \\
Marios Papas, {\bf Demetrios Zeinalipour-Yazti}, Marios D. Dikaiakos, George Panayi. Theodoros Kyprianou,
{\em  Poster at the European Enabling Grids for E-sciencE Conference} {\bf (EGEE 2006)}, 
Geneva, Switzerland, 25-29 September, {\bf 2006}.

\item [{\bf N1.}]
\label{N1}
\label{failrank-egee06}
{\bf ``Monitoring and Ranking Failures using FailRank''}, \\
{\bf Demetrios Zeinalipour-Yazti}, Kyriakos Neocleous, Chryssis Georgiou, Marios D. Dikaiakos, 
{\em  Poster at the European Enabling Grids for E-sciencE Conference} {\bf (EGEE 2006)}, 
Geneva, Switzerland, 25-29 September, {\bf 2006}.   

\end{enumerate}

\subsection*{\bf TECHNICAL REPORTS}
\begin{enumerate}


\item [{\bf R12.}]
\label{R12}
\label{mpi2017}
{\bf ``Systematic Objective Evaluation of RF-based Indoor Localization Algorithms''},\\
Dhruv Gupta, Klaus Berberich, Jannik Strötgen, and {\bf Demetrios Zeinalipour-Yazti},
“Generating Semantic Aspects for Queries,” Max-Planck-Institut für Informatik, Saarbrücken, MPI–I–2017–5-001, {\bf 2017}.

\item [{\bf R11.}]
\label{R11}
\label{evarilos2014}
{\bf ``Systematic Objective Evaluation of RF-based Indoor Localization Algorithms''},\\
Filip Lemic, Vlado Handziski, Adam Wolisz, Timotheos Constambeys, Christos Laoudias, {\bf Demetrios Zeinalipour-Yazti}, Christos Panayiotou, Stephan Adler, Simon Schmitt, Heiko Will, Thomas Hillebrandt, Marcel Kyas, Yuan Yang, Yubin Zhao
EVARILOS Open Challenge: Track 3, {\bf TKN Technical Reports Series} no. TKN-14-005, Techical University of Berlin, Germany, Editor: Prof. Dr.-Ing. Adam Wolisz, October {\bf 2014}.

\item [{\bf R10.}]
\label{R10}
\label{coregridTR180}
{\bf ``Improving the Dependability of Grids via Short-Term Failure Predictions''},\\
Artur Andrzejak, {\bf Demetrios Zeinalipour-Yazti}, Marios D. Dikaiakos, 
{\bf CoreGRID Technical Report}, TR-0180, July 24, {\bf 2009}.  

\item [{\bf R9.}]
\label{R9}
\label{coregridTR164}
{\bf ``Metadata Ranking and Pruning for Failure Detection in Grids''},\\
{\bf Demetrios Zeinalipour-Yazti}, Haris Papadakis, Chryssis Georgiou, Marios D. Dikaiakos, 
{\bf CoreGRID Technical Report}, TR-0164, July 10, {\bf 2008}.  

\item [{\bf R8.}]
\label{R8}
{\bf ``Workload-aware Optimization of Query Routing Trees in Wireless Sensor Networks''}, \\
Panayiotis Andreou, {\bf Demetrios Zeinalipour-Yazti}, Panos K. Chrysanthis and George Samaras,
TR-2008-003, Dept. of Comp. Sc., University of Pittsburgh, April {\bf 2008}.  

\item [{\bf R7.}]
\label{R7}
{\bf ``MINT Views: Materialized In Network Top-k Views in Sensor Networks''}, \\
{\bf Demetrios Zeinalipour-Yazti}, Panayiotis Andreou, Panos K. Chrysanthis, George Samaras, 
TR-2007-016, Dept. of Comp. Sc., University of Pittsburgh, May {\bf 2007}.  

\item [{\bf R6.}]
\label{R6}
{\bf ``The MicroPulse Framework for Adaptive Waking Windows in Sensor Networks''}, \\
{\bf Demetrios Zeinalipour-Yazti}, Panayiotis Andreou, Panos K. Chrysanthis, George Samaras and Andreas Pitsillides, 
TR-2007-015, Dept. of Comp. Sc., University of Pittsburgh, May {\bf 2007}.  

\item [{\bf R5.}]
\label{R5}
{\bf ``Managing Failures in a Grid System using FailRank''}, \\
{\bf Demetrios Zeinalipour-Yazti}, Kyriacos Neocleous, Chryssis Georgiou, Marios D. Dikaiakos, 
TR-2006-1, Dept. of Comp. Sc., University of Cyprus, September {\bf 2006}. 

\item [{\bf R4.}]
\label{R4}
{\bf ``Structuring Topologically-Aware Overlay Networks using Domain Names''},
{\bf Demetrios Zeinalipour-Yazti} and Vana Kalogeraki, 
TR-CS-92, Dept. of Comp. Sc. \& Eng., UC - Riverside, October {\bf 2004}.  

\item [{\bf R3.}]
\label{R3}
{\bf ``Quantitative Analysis of the Gnutella Network Traffic''},
{\bf Demetrios Zeinalipour-Yazti} and Theodore Folias,
TR-CS-89, Dept. of Comp. Sc. \& Eng., UC - Riverside, June {\bf 2002}.  

\item [{\bf R2.}]
\label{R2}
{\bf ``A Distributed Middleware Infrastructure for Personalized Services''},
Marios D. Dikaiakos and {\bf Demetrios Zeinalipour-Yazti},
TR-2001-4, Dept. of Comp. Sc., University of Cyprus, December {\bf 2001}. 

\item [{\bf R1.}]
\label{R1}
{\bf ``High-Performance Crawling and Filtering in Java''},
{\bf Demetrios Zeinalipour-Yazti} and Marios D. Dikaiakos,
TR-2001-3, Dept. of Comp. Sc., University of Cyprus, June {\bf 2001}. 

\end{enumerate}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%			TALKS \& PRESENTATIONS  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\renewcommand{\labelitemi}{$\bullet$}

\section{\bf TALKS }

\subsection*{\bf DISTINCTIONS}
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item {\bf ACM Distinguished Speaker}.  {\em ``a highly visible way that ACM, through the appointment of leading researchers, engages with emerging professionals, students and, in some cases, the public on a range of topics in computing.''}, Association for Computing Machinery, New York, NY, USA, as of February 17, 2017 until February 17, 2020.
\end{itemize}

\subsection*{\bf KEYNOTE TALKS}
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item  {\bf Keynote Speaker}, 21st European Conference on Advances in Databases and Information Systems {\bf (ADBIS 2017)}, Hilton Cyprus Hotel, Nicosia, Cyprus, 24 - 27 September, {\bf 2017}.
\end{itemize}

\subsection*{\bf PANEL TALKS}
\begin{itemize}
\setlength{\itemsep}{0.10ex}
%
\item  {\bf Panelist}, {\em ``The Beckman Database Research Self-Assessment Meeting''},
{\em 13th Hellenic Data Management Symposium} {\bf (HDMS 2015)}, Athens University of Economics and Business, Athens, Greece, July 31, 2015, with Alexandros Labrinidis, Peter Triantafillou and Herodotos Herodotou. Panel Moderators: Yannis Ioannidis, Panagiotis Karras.
%
\item  {\bf Panel Co-Chair}, {\em ``Human Mobility Computing and Privacy: Fad or Reality?''},
{\em 16th IEEE International Conference on Mobile Data Management} {\bf (MDM 2015)},
{\em The 3rd International Workshop On Human Mobility Computing And Privacy (HuMoComP 2015)},
held in conjunction with IEEE MDM'15, June 15, 2015 - Pittsburgh, Pennsylvania, USA.
%
\item  {\bf Panel Co-Chair}, {\em ``Mobile Big Data Analytics: Research, Practice and Opportunities''},
{\em 15th IEEE International Conference on Mobile Data Management} {\bf (MDM 2014)}, Mobile Data Management
15-18 July, 2014, Brisbane, Australia.
%
\item  {\bf Panelist}, {\em ``Large-Scale Participatory Urban Sensing: A Fad or Reality?''},  
{\em 14th IEEE International Conference on Mobile Data Management}  {\bf (MDM 2013)}, June 5, 2013, Milan, Italy. Panel Moderators:
Archan Misra (SMU, Singapore), Juha Laurila (Nokia Research, Switzerland).
%
\item  {\bf Panel Co-Chair}, {\em ``Future Directions in Sensor Data Management: A Panel Discussion''}, {\bf (DMSN 2010)}, collocated with {\bf (VLDB 2010)}, Singapore, Sept. 13, 2010, Panelists: Yanlei Diao (Univ. of Massachussets - Amherst, USA), Le Gruenwald (National Science Foundation, USA), Christian S. Jensen (University of Aarhus, Denmark), Kian-Lee Tan (National University of Singapore, Singapore), Proceedings of the 7th Workshop on Data Management for Sensor Networks, DMSN 2010, Singapore, September 13, 2010. ACM International Conference Proceeding Series ACM 2010, ISBN 978-1-4503-0416-0.
%
\item  {\bf Panelist}, {\em ``What does the Cloud mean for Data Management: Challenges and Opportunities''},  
{\em 9th Hellenic Data Management Symposium} {\bf (HDMS 2010)}, Ayia Napa, Cyprus, July 2nd, 2010, with Marios Dikaiakos, Evangelia Pitoura, Peter Triantafillou and Akrivi Vlachou, Panel Moderator: Anastasia Ailamaki.
\end{itemize}


\subsection*{\bf INVITED TUTORIALS and SUMMER SCHOOLS TALKS}
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item  {\bf Invited Tutorial}, {\em ``IoT-enabled Localization and Navigation''}, 2016 PERCCOM Summer School, Erasmus Mundus Master on Pervasive Computing \& COMmunications for sustainable development, Nancy, France, June 16, {\bf 2016}.
\item  {\bf Invited Tutorial}, {\em ``Mobile Data Management in Indoor Spaces''}, 16th IEEE International Conference on Mobile Data Management, Pittsburgh, PA, USA, June 17, {\bf 2015}. (1.5 hours).
\item {\bf Invited Tutorial}, {\em Crowdsourcing for Mobile Data Management''}, Georgios Chatzimilioudis and {\bf Demetrios Zeinalipour-Yazti}, The 14th IEEE International Conference on Mobile Data Management (MDM'13), Milan, Italy, June 5, {\bf 2013}. (1.5 hours).
\item {\bf Invited Tutorial}, {\em Distributed Top-K Query Processing''}, Demetrios Zeinalipour-Yazti and Zografoula Vagena, IEEE/ACM 9th International Conference on Mobile Data Management (MDM 2008), Beijing, China, April 27-30, {\bf 2008}. (3 hours).
\item  {\bf Invited Tutorial}, {\em ``Distributed Spatio-Temporal Similarity Search''}, 
 Thematic Network for Doctoral Education in Computing, Summer School on Intelligent Systems, Nicosia, Cyprus, July 4, {\bf 2007}. (3 hours).
\end{itemize}


\subsection*{\bf INVITED TALKS}
\begin{itemize}
\setlength{\itemsep}{0.10ex}
% 2018
\item  {\bf Invited Talk}, {\em ``Telco Big Data: Current State and Future Directions''}, 19th IEEE International Conference on Mobile Data Management June 25 - June 28, 2018, AAU, Aalborg, Denmark, June 26,  {\bf 2018}.

\item  {\bf Invited Talk}, {\em ``Query Operators and Systems for the Mobile Big Data Era''}, Department of Computer Science, University of Cyprus, January 15, {\bf 2018}.

% 2017
\item  {\bf Invited Talk}, {\em ``Indoor Data Management in Anyplace''}, Max-Planck Institute for Informatics, Saarbr\"ucken, Germany, July 11, {\bf 2017}.
\item  {\bf Invited Talk}, {\em ``Indoor Data Management in Anyplace''}, Heidelberg University, Heidelberg, Germany, June 6, {\bf 2017}.
\item  {\bf Invited Talk}, {\em ``Indoor Data Management in Anyplace''}, University of Mannheim, Mannheim, Germany, May 4, {\bf 2017}.
\item  {\bf Invited Talk}, {\em ``Building All k Nearest Neighbor Social Communities''},  Paris Descartes University Seminar Series on Data Analytics, Paris, France, April 12, {\bf 2017}.

% 2016
\item  {\bf Invited Talk}, {\em ``Spatial Big Data Research and Applications at the University of Cyprus''}, The First Europe-China Workshop on Big Data Management, Helsinki, Finland, May 16, {\bf 2016}.
\item  {\bf Invited Talk}, {\em ``Anyplace Indoor Information Service ''}, Symposium on Challenges of Fingerprinting in Indoor Positioning and Navigation, Open University of Catalonia, Barcelona, Spain, May 3, {\bf 2016}.
\item  {\bf Invited Talk}, {\em ``Prefetching Indoor Navigation Structures in Anyplace''}, University of Nicosia, Nicosia, Cyprus, March 23, {\bf 2016}.
\item  {\bf Invited Talk}, {\em ``Internet-based Indoor Navigation Services''}, ACROSS Meeting, Centrum Wiskunde \& Informatica (CWI), Amsterdam, Netherlands, February 25, {\bf 2016}.

% 2015
\item  {\bf Invited Talk}, {\em ``Prefetching Indoor Navigation Structures in Anyplace''}, 2nd Cyprus Workshop on Computing: Scientific Applications of Computing, European University Cyprus, Nicosia, Cyprus., October 27, {\bf 2015}.
\item  {\bf Invited Talk}, {\em ``Big Data Processing Architectures: Status and Challenges''}, European University of Cyprus, Nicosia, Cyprus, October 27, {\bf 2015}.
\item  {\bf Invited Talk}, ``Multifaceted Engagement of BSc Students in Computer Science Research'', Research-led Teaching Workshop, Centre for Teaching \& Learning, University Cyprus, Nicosia, Cyprus, December 15, {\bf 2015}.
\item  {\bf Invited Talk}, {\em ``Indoor Data Management in Anyplace''}, University of Pittsburgh, PA, USA, June 24, {\bf 2015}.
\item  {\bf Invited Talk}, {\em ``Indoor Data Management: Status and Challenges''}, University of Cyprus, Nicosia, Cyprus, February 17,  {\bf 2015}.

% 2014
\item  {\bf Invited Talk}, {\em ``Smartphone Cloud Testbeds and Applications''}, European Institute of Innovation \& Technology (EIT), ICT Labs, Budapest, Hungary, December 5, {\bf 2014}.
\item  {\bf Invited Talk}, {\em ``Indoor Data Management: Status and Challenges''}, Skolkovo Institute of Science and Technology (Skoltech), Moscow, Russia, October 2, {\bf 2014}.
\item  {\bf Invited Talk}, {\em ``Managing Smartphone Cloud Testbeds''}, Distributed Systems Group, Technical University of Vienna, Vienna, Austria, September 30, {\bf 2014}.
\item  {\bf Invited Talk}, {\em ``Mobile Crowdsourcing: Challenges and Applications''}, 7th Webdatanet (COST Action IS1004) Conference on Mobile Research, Larnaca, Cyprus, March 31, {\bf 2014}.
\item  {\bf Invited Talk}, {\em ``Crowdsourcing Urban Data with Smartphones''}, 1st International Workshop on Mining Urban Data, collocated with EDBT/ICDT, March 24-28, 2014 - Athens, Greece, March 28, {\bf 2014}.
\item  {\bf Invited Talk}, {\em ``Mobile Crowdsourcing: Challenges and Applications''},  7th Webdatanet (COST Action IS1004) Conference on Mobile Research, Larnaca Cyprus, March 31, 2014 {\bf 2014}.

% 2013
\item  {\bf Invited Talk}, {\em ``Big-Data - What is it?''}, 4th Cyprus IT Architect Club Meeting, Nicosia, March 12, {\bf 2013}.
\item  {\bf Invited Talk}, {\em ``Smartphone Sensing: Testbeds and Applications''}, Workshop on Social Platforms for Urban Sensing, Department of Computer Science, University of Cyprus, February 11, {\bf 2013}.

% 2012
\item  {\bf Invited Talk}, {\em ``Querying Sensor Data in Smartphone Networks''}, Department of Computer Science, University of Cyprus, Thursday, October 11, {\bf 2012}.

% 2011
\item  {\bf Invited Talk}, {\em ``Data Management Techniques for Smartphone Networks''}, 10th International ACM Workshop on Data Engineering for Wireless and Mobile Access (MobiDE'11), in conjunction with SIGMOD/PODS 2011, Athens, Greece, June 12, {\bf 2011}.
\item  {\bf Invited Talk}, {\em ``Energy Efficient Data Management in Smartphone Networks''},  NSF-sponsored Workshop on Sustainable Energy-Efficient Data Management (SEEDM), in Arlington, Virginia, May 2-3, {\bf 2011}. 
\item  {\bf Invited Talk}, {\em ``Querying Smartphone Networks with SmartTrace''}, Department of Computer Science, University of Pittsburgh, USA, March 29, {\bf 2011}.
\item  {\bf Invited Talk}, {\em ``Optimized Communication Structures for Wireless Sensor Networks''}, Master in Information Systems, Open University of Cyprus, Nicosia, Cyprus, March 9, {\bf 2011}.

% 2010
\item  {\bf Invited Talk}, {\em ``Ranking Query Results in a Networked World''}, Department of Informatics and Telecommunications, University of Athens, Greece,  July 23, {\bf 2010}.
\item  {\bf Invited Talk}, {\em ``Ranking Query Results in a Networked World''},  IBM T.J. Watson Research Center, Hawthorne, NY, USA, May 27, {\bf 2010}.
\item  {\bf Invited Talk}, {\em ``Spatio-Temporal Query Processing in Smartphone Networks''},  SSPC-WAN Workshop, 11th International Conference on Mobile Data Management (MDM 2010), Kansas City, USA, May 23, {\bf 2010}.
\item  {\bf Invited Talk}, {\em ``Semantic Challenges in (Mobile) Sensor Networks''},  Dagstuhl Seminar 10042: Semantic Challenges in Sensor Networks, Dagstuhl, Germany, January 26, {\bf 2010}.

% 2009

% 2008
\item  {\bf Invited Talk}, {\em ``Distributed Top-K Ranking Algorithms''}, Polytechnic University of Catalunya (UPC), Barcelona, Spain, December 15, {\bf 2008}.
\item  {\bf Invited Talk}, {\em ``Distributed Top-K Ranking Algorithms''}, Communication Systems Group (CSG), ETH Zurich, Switzerland, December 12, {\bf 2008}.
\item  {\bf Invited Talk}, {\em ``MicroHash - An External Memory Indexing Structure for Wireless Sensor Devices''}, IBM Research, Zurich, Switzerland, December 12, {\bf 2008}.
\item  {\bf Invited Talk}, {\em ``MicroHash - An External Memory Indexing Structure for Wireless Sensor Devices''}, Microsoft Research Cambridge, January 12, {\bf 2008}.

% 2007

% 2006
\item  {\bf Invited Talk}, {\em ``Content-Based Search in Internet-Scale Peer-to-Peer Systems''}, KTH - Royal Institute of Technology, Stockholm, Sweden, December 28, {\bf 2006}.
\item  {\bf Invited TV Presentation},  {\em ``ICGrid: Intensive Care Grid''}, 
The Best Practice Award Video produced by the Academic Internet Television Network (ATVN)
for the EMISPHER project, Oct 4, {\bf 2006}. \\
({\tt http://www.atvn.pl/atvn-eu-gp/euarchive/})
\item  {\bf Invited Talk}, {\em ``Top-K Query Processing Techniques for Distributed Environments''}, Institute of Computer Science, FORTH, Herakleion, Greece, June 7, {\bf 2006}. 
\end{itemize}

\subsection*{\bf OTHER LECTURES \& PRESENTATIONS}
\begin{itemize}
\item {\bf Presentation}, {\em ``Unraveling the link between Mobile Location and Microblog Data''}, Max-Planck Institute for Informatics, Saarbr\"ucken, Germany, May 2, {\bf 2017}.
\item  {\bf Demo Presentation}, {\em ``Data-driven Serendipity Navigation in Urban Places''}, 37th IEEE International Conference on Distributed Computing Systems (ICDCS 2017), Atlanta, GA, USA, June 7, {\bf 2017}.
\item  {\bf Presentation}, {\em ``Indoor Localization Accuracy Estimation from Fingerprint Data''}, 18th IEEE International Conference on Mobile Data Management (MDM 2017), KAIST, Daejeon, South Korea, May 31, {\bf 2017}.
\item  {\bf Demo Presentation}, {\em `` ACCES: Offline Accuracy Estimation for Fingerprint-Based Localization''}, 18th IEEE International Conference on Mobile Data Management (MDM 2017), KAIST, Daejeon, South Korea, May 30, {\bf 2017}.
\item  {\bf Demo Presentation}, {\em ``SPATE: Compacting and Exploring Telco Big Data''}, The 33rd IEEE International Conference on Data Engineering (ICDE 2017), San Diego, CA, USA, April 20, {\bf 2017}.
\item  {\bf Presentation}, {\em ``Efficient Exploration of Telco Big Data with Compression and Decaying''}, The 33rd IEEE International Conference on Data Engineering (ICDE 2017), San Diego, CA, USA, April 19, {\bf 2017}.
\item  {\bf Poster Presentation}, {\em ``Semantic Exploration of Anonymous Social Networks''}, Network Meeting of the Alexander von Humboldt Foundation, Dresden, April 05-07, {\bf 2017}.
\item  {\bf Presentation}, {\em ``Distributed In-Memory Processing of All k Nearest Neighbor Queries''}, The 14th Hellenic Data Management Symposium (HDMS 2016), Athens University of Economics and Business, Athens, Greece, July 28, {\bf 2016}.
\item  {\bf Presentation}, {\em ``Privacy-Preserving Indoor Localization on Smartphones''}, The 14th Hellenic Data Management Symposium (HDMS 2016), Athens University of Economics and Business, Athens, Greece, July 28, {\bf 2016}.
\item {\bf Presentation}, {\em ``Radiomap Prefetching for Indoor Navigation in Intermittently Connected Wi-Fi Networks''}', The 13th Hellenic Data Management Symposium (HDMS 2015), Athens University of Economics and Business, Athens, Greece, July 30, {\bf 2015}.
\item {\bf Presentation}, {\em ``Radiomap Prefetching for Indoor Navigation in Intermittently Connected Wi-Fi Networks''}, 16th IEEE International Conference on Mobile Data Management (MDM 2015), Pittsburgh, PA, USA, April 16, {\bf 2015}.
\item {\bf Demo Presentation}, {\em ``Scalable Mockup Experiments on Smartphones using SmartLab''}, 16th IEEE International Conference on Mobile Data Management (MDM 2015), Pittsburgh, PA, USA, April 16, {\bf 2015}.
\item {\bf Demo Presentation}, {\em ``Anyplace: A Crowdsourced Indoor Information Service''}, 16th IEEE International Conference on Mobile Data Management (MDM 2015), Pittsburgh, PA, USA, April 16, {\bf 2015}.
\item {\bf Presentation}, {\em ``Rayzit: An Anonymous and Dynamic Crowd Messaging Architecture''}, 3rd IEEE International Workshop on Mobile Data Management, Mining, and Computing on Social Networks, collocated with IEEE MDM'15 (Mobisocial '15), Pittsburgh, PA, USA, April 15, {\bf 2015}.
\item  {\bf Presentation}, {\em ``Hour of Code in Elementary Schools''}, December 7, 2015, 5th Elementary School of Aglantzia, Nicosia, Cyprus, {\bf 2015}.
\item  {\bf Presentation}, {\em ``Hour of Code in Elementary Schools''}, December 9, 2014, 4th Elementary School of Latsia, Nicosia, Cyprus, {\bf 2014}.
\item  {\bf Poster Presentation}, {\em ``Crowdsourced Indoor Localization and Navigation with Anyplace''}, 13th international conference on Information processing in sensor networks (IPSN '14), April 16, {\bf 2014}.
\item  {\bf Poster Presentation}, {\em ``Sensor Mockup Experiments with SmartLab''}, 13th international conference on Information processing in sensor networks (IPSN '14), April 16, {\bf 2014}.
\item  {\bf Presentation}, {\em ``Managing Smartphone Testbeds with SmartLab''}, 27th USENIX Large Installation System Administration Conference ' (LISA '13), Washington D.C., USA, November 7, {\bf 2013}.
\item  {\bf Presentation}, {\em ``Spatio-Temporal WiFi Localization''}, Final Conference of MOVE COST Action IC903, Vienna, Austria, Sept 30 - Oct 1, 2013, October 1, {\bf 2013}.
\item  {\bf Presentation}, {\em ``Smartphone Data Management: Frameworks and Applications''}, ERCIM Spring Meeting 2013, June 6, 2013, Nicosia Cyprus, June 6, {\bf 2013}.
\item  {\bf Presentation}, {\em ``CLODA: A Crowdsourced Linked Open Data Architecture''}, 1st IEEE Intl. Workshop on Mobile Data Management, Mining, and Computing on Social Networks (MobiSocial) with IEEE MDM '13, June 3, 2013, Milan Italy, June 3, {\bf 2013}.
\item  {\bf Lecture}, {\em ``Cloud Computing and Data Management''}, New Technologies and their utilization in Cyprus Information Centers, November 8, University of Cyprus Library and ΚΕΒΕΠ, {\bf 2012}.
\item  {\bf Lecture}, {\em ``Systems and Networks Direction in Computer Science''}, course: ``EPL202 - Exploration in Computer Science'', Undergraduate Course, Department of Computer Science, University of Cyprus,  Nicosia, Cyprus, November 8, {\bf 2012}.
\item  {\bf Lecture}, {\em ``Data Management in Smartphone Networks''}, course: ``EPL202 - Exploration in Computer Science'', Undergraduate Course, Department of Computer Science, University of Cyprus,  Nicosia, Cyprus, September 15, {\bf 2011}.
\item  {\bf Presentation}, {\em ``Data Management in Smartphone Networks (for High School Students)''}, 2nd Computer Science Day for High School Students, University of Cyprus,  Nicosia, Cyprus, March 19, {\bf 2011}.
\item  {\bf Lecture}, {\em ``Query Routing Trees in Wireless Sensor Networks''}, course: ``EPL 671 -  Computer Science: Research and Technology'', Graduate Course, Department of Computer Science, University of Cyprus,  Nicosia, Cyprus, Feb 15, {\bf 2011}.
\item  {\bf Presentation}, {\em ``MHS: Minimum-Hot-Spot Query Trees for Wireless Sensor Networks''}, the 9th Hellenic Data Management Symposium (HDMS 2010), Ayia Napa, Cyprus, June 30th - July 3, {\bf 2010}. 
\item  {\bf Presentation}, {\em ``MHS: Minimum-Hot-Spot Query Trees for Wireless Sensor Networks''}, 9th International ACM Workshop on Data Engineering for Wireless and Mobile Access (MobiDE'10), Indianapolis, Indiana, USA, in conjunction with SIGMOD/PODS, June 6, {\bf 2010}.
\item  {\bf Presentation}, {\em ``MDM'10: Program Report''}, 11th International Conference on Mobile Data Management (MDM 2010), Kansas City, Missouri, May 25, {\bf 2010}.
\item  {\bf Presentation}, {\em ``Introduction to Databases (for High School Students)''}, Computer Science Day for High School Students, University of Cyprus,  Nicosia, Cyprus, March 8, {\bf 2010}.
\item  {\bf Lecture}, {\em ``Introduction to Databases''}, course: ``EPL202 - Exploration in Computer Science'', Undergraduate Course, Department of Computer Science, University of Cyprus,  Nicosia, Cyprus, September 30, {\bf 2009}.
\item  {\bf Presentation}, {\em ``FSort: External Sorting on Flash-based Sensor Devices''}, DMSN'09 workshop, collocated with VLDB'09, Lyon, France, August 24, {\bf 2009}.
\item  {\bf Presentation}, {\em ``Perimeter-based Data Acquisition and Replication in Mobile Sensor Networks''},The 10th International Conference on Mobile Data Management (MDM'09), Tapei, Taiwan, May 20, {\bf 2009}. 
\item  {\bf Presentation}, {\em ``ETC: Energy-driven Tree Construction in Wireless Sensor Networks''}, SenTIE'09 workshop, collocated with MDM'09, Tapei, Taiwan, May 20, {\bf 2009}. 
\item  {\bf Lecture}, {\em ``Peer-to-Peer Systems''}, course: ``EPL601 - Distributed Systems'', Graduate Course, Department of Computer Science, University of Cyprus,  Nicosia, Cyprus, November 18, {\bf 2008}.
\item  {\bf Presentation}, {\em ``Indexing and Searching in Wireless Sensor Networks''}, SEARCHiN, Marie Curie TOK, University of Cyprus, Nicosia, Cyprus, February 14th {\bf 2008}.
\item  {\bf Presentation}, {\em ``Grid Failure Monitoring and Ranking using FailRank''}, CoreGRID Network of Excellence Workshop, Paris, France, January 15th {\bf 2007}.
\item  {\bf Presentation}, {\em ``ICGrid: Towards a Grid Infrastructure for Intensive Care Units''}, Cyprus Grid Day, January 10, {\bf 2008}.
\item  {\bf Lecture}, {\em ``Peer-to-Peer Systems''}, course: ``EPL601 - Distributed Systems'', Graduate Course, Department of Computer Science, University of Cyprus,  Nicosia, Cyprus, November 16, {\bf 2007}.
\item  {\bf Presentation}, {\em ``SenseSwarm: A Perimeter-based Data Acquisition Framework for Mobile Sensor Networks''}, The 4th Intl. Workshop on Data Management for Sensor Networks (with VLDB'2007), Vienna, Austria, Sep. 24, {\bf 2007}. 
\item {\bf  Presentation}, {\em ``MINT Views: Materialized In-Network Top-k Views in Sensor Networks''}, The 6th Hellenic Data Management Symposium (HDMS'07), Athens, Greece, July 5th {\bf 2007}. 
\item  {\bf Presentation}, {\em ``Distributed Spatio-Temporal Similarity Search''}, The 6th Hellenic Data Management Symposium (HDMS'07), Athens, Greece, July 5th {\bf 2007}. 
\item  {\bf Presentation}, {\em ``FailRank: Towards a Unified Grid Failure Monitoring and Ranking System''}, CoreGRID Workshop on Grid Programming Model Grid and P2P Systems Architecture Grid Systems, Tools and Environments , Crete, Greece, June 12th {\bf 2007}.
\item  {\bf Presentation}, {\em ``MINT Views: Materialized In-Network Top-k Views in Sensor Networks''}, IEEE 8th International Conference on Mobile Data Management, Mannheim, Germany, May 10th {\bf 2007}.
\item  {\bf Presentation}, {\em ``The MicroPulse Framework for Adaptive Waking Windows in Sensor Networks''}, IEEE First International Workshop on Data Intensive Sensor Networks 2007 (with MDM'2007), Mannheim, Germany, May 11th {\bf 2007}. 
\item  {\bf Lecture}, {\em ``Efficient Indexing Structures for Flash-Based Sensor Devices''}, course: ``EPL 651 -  Data Management for Mobile Computing'', Graduate Course, Department of Computer Science, University of Cyprus,  Nicosia, Cyprus, April 26, {\bf 2007}.
\item  {\bf Lecture}, {\em ``Top-K Algorithms: Concepts and Applications''}, course: ``EPL 671 -  Computer Science: Research and Technology'', Graduate Course, Department of Computer Science, University of Cyprus,  Nicosia, Cyprus, March 20, {\bf 2007}.
\item  {\bf Presentation}, {\em ``ICGrid: Intensive Care Grid''}, CoreGRID Industrial Conference, Sophia Antipolis, France, Nov 30, {\bf 2006}.
\item  {\bf Lecture}, {\em ``Peer-to-Peer Systems''}, course: ``EPL601 - Distributed Systems'', Graduate Course, Department of Computer Science, University of Cyprus,  Nicosia, Cyprus, October 13, {\bf 2006}.
\item  {\bf Presentation}, {\em ``Business Processes: Behavior Prediction and Capturing Reasons for Evolution''}, 8th International Conference on Enterprise Information Systems'', Paphos, Cyprus, May 24, {\bf 2006}.
\item  {\bf Lecture}, {\em ``MicroHash: An External Memory Indexing Structure for Wireless Sensor Devices''},  Computer Science Colloquium Series, University of Cyprus, Nicosia, Cyprus, March 31, {\bf 2006}.
\item  {\bf Lecture}, {\em ``Data Storage in Sensor Databases''}, eNEXT Workshop on Sensor and Ad-hoc Networks, Nicosia, Cyprus, March 14, {\bf 2006}.
\item  {\bf Lecture}, {\em ``Global Internet Content Delivery''}, course: ``EPL602 - Graduate Course in Programming of Internet Systems and Services'', Graduate Course, Department of Computer Science, University of Cyprus,  Nicosia, Cyprus, November 22nd, {\bf 2005}.
\item  {\bf Lecture}, {\em ``Distributed Top-K Query Processing''}, Computer Science Colloquium Series,  University of Cyprus, Nicosia, Cyprus, November 16, {\bf 2005}.
\item  {\bf Presentation}, {\em ``On Constructing Internet-Scale P2P Information Retrieval Systems''}, DBISP2P'04 (VLDB Conference), Toronto ON, Canada, September {\bf 2004}.
\item  {\bf Poster Presentations} at Industry Day, Riverside CA, USA, (2002-2005).
\item  {\bf Poster Presentations} at UCR Advisory Day, Riverside CA, USA, (2002-2005).
\item  {\bf Presentation}, {\em ``A Local Search Mechanism for Peer-to-Peer Networks''}, ACM CIKM'02, McLean VA, USA, November {\bf 2002}. 
\item  {\bf Lecture}, {\em ``A Quantitative Analysis of the Gnutella Network Traffic''}, UCY Lunch-Seminar, Nicosia, Cyprus, July {\bf 2002}. 
\item  {\bf TV Presentations} on Internet Technology at CyBC (Cyprus National TV), Nicosia, Cyprus, {\bf 2000}.  
\end{itemize}

\subsection*{\bf INTERVIEWS and PRESS COVERAGE}
\begin{itemize}
\setlength{\itemsep}{0.10ex}
%
\item  {\bf Kathimerini Newspaper},  daily morning newspaper published in Cyprus. Interview on {\em ``Data Management in Systems and Networks''}, Sunday, Nov. 20, {\bf 2016}.
%
\item  {\bf Postnauka.ru} Russian online portal focused on popularization of contemporary science, scientific ideas and scientists, who discover these ideas. Inteview on {\em ``Mobile Data Management''}, Online: {\tt http://postnauka.ru/author/zeinalipour}, October 15, {\bf 2014}.
%
\item  {\bf Euronews}, Europe-wide multilingual news media service headquartered in France.  Documentary {\em ``RIGHT-ON - Privacy versus new information technology''}, coverage of our research on mobile privacy by my PhD student Georgios Larkou, January 7,  {\bf 2013}. \\ Online: http://www.euronews.com/2013/01/07/privacy-versus-new-information-technology,. (also quoted: http://www.quotes.euronews.com/people/georgios-larkou-PA7VMZGJ).
%
\item  {\bf Alitheia Newspaper}, daily morning newspaper published in Cyprus. {\em ``The "Smart" phone at the University of Cyprus''} article, Sunday, Dec. 8, {\bf 2012}.
\end{itemize}

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%			GRANTS \& FUNDING
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\renewcommand{\labelitemi}{$\bullet$}

\section{\bf RESEARCH GRANTS AND FUNDING}
\begin{itemize}
\setlength{\itemsep}{0.10ex}


\item  {\bf 04/2019-03/2023 (PI):} {\em LASH FIRE: Legislative Assessment for Safety Hazards of Fire and Innovations in Ro-Ro ship Environment}, Topic identifier: MG-2-2-2018: Marine Accident Response, Subtopic C); Innovation Action (IA), 25 EU Partners (Industrial / Academic), H2020-MG-2018-TwoStages, Type of Action: IA, Acronym: LASH FIRE, Number: 814975, Duration: 48 months, Start Date: April 2019, Estimated Project Cost: 13,752,817.50 Euros.

\item  {\bf 03/2019-02/2022 (Co-PI):} {\em EnterCY: ENhancing Tourist ExpeRience in Cyprus}, Pillar:  Smart Growth, Programme: Integrated Projects, RPF Proposal Number: INTEGRATED/0609/0020,  Partners: Frederick Research Center (coordinator), University of Cyprus, CyRIC, Silversky3D, ???,  Department of Antiquities, Association of Cyprus Travel Agents (ACTA), Cyprus Tourism Organisation (CTO), Estimated Project Cost: 917,092.00 Euros.

\item {\bf 01/10/2018 - 01/10/2021 (participant):} {\em Marie Skłodowska-Curie Actions (MSCA) Research and Innovation Staff Exchange (RISE) - H2020-MSCA-RISE-2018}, ``ENDORSE: Safe, Efficient and Integrated Indoor Robotic Fleet for Logistic Applications in Healthcare and Commercial Spaces'', Project Number: 823887, Coordinator: Universite d'Orleans (France), 8 EU Partners, 9 Work Packages, Total Budget: 1,122,400.00 Euros, 01/10/2018 - 01/10/2021.

\item  {\bf 09/2017-07/2018 (supervisor):} {\em New Researcher Program}, University of Cyprus, Ph.D. Fellowship for C. Costa, Advisor: Demetrios Zeinalipour-Yazti.

\item {\bf 09/2016-08/2017 (experienced researcher):} {\em Semantic Exploration of Anonymous Social Networks}, Alexander von Humboldt Stiftung, Max Planck Institute for Informatics, Department 5: Databases and Information Systems (Group: Gerhard Weikum), Saarbr\"ucken, Germany.

\item  {\bf 2016 (supervisor):} {\em New Researcher Program}, University of Cyprus, Ph.D. Fellowship for C. Costa, Advisor: Demetrios Zeinalipour-Yazti.

\item {\bf 2013-2017 (Mangement Committee (MC) Member):}  {\em Autonomous Control for a Reliable Internet of Services (ACROSS)}, COST Action IC1304, European Cooperation in Science and Technology,  http://www.move-cost.info/.

\item {\bf 2013-2017 (participant):} {\em Erasmus Mundus Joint Master Degree: PERCCOM (Pervasive Computing \& COMmunications for sustainable development)}, Education, Audiovisual and Culture Executive Agency (EACEA), Coordinator: University of Lorraine (France). Other Partners: Lule\aa University of Technology (Sweden), Lappeenranta University of Technology (Finland), Saint Petersburg National Research University of Information Technologies, Mechanics and Optics (Russia)

\item {\bf 11/2015-05/2016 (PI):} {\em Development of Industrial Research and Innovation Activities (Programme Innovation)}, ``Data Storage Monitoring and Analysis'', Cyprus Research Promotion Foundation,  Partners: University of Cyprus, Drivenest Ltd., Cyprus.

\item {\bf 01/2015-12/2015 (PI):} {\em Big Data Research and Development (Development Services Agreement)}, ``Big Data Processing in Telcommunication Datacenters'', Partners: MTN Cyprus Ltd., Cyprus and University of Cyprus.

\item  {\bf 2014 (PI):} {\em New Researcher Program}, University of Cyprus, Ph.D. Fellowship for C. Costa, Advisor: Demetrios Zeinalipour-Yazti.  

\item {\bf 01/2014-12/2014 (PI):} {\em Smartphone Data Management (Development Services Agreement)}, ``Spatio-Temporal Mobile Data Management'', Geomatic Technologies Ltd., Cyprus.

\item {\bf 01/2014-12/2016 (PI):} {\em Research and Education in Mobile Systems (Industrial Sponsorship)}. Partners: MTN Cyprus Ltd., Cyprus and University of Cyprus.

\item {\bf 11/2012-12/2013 (PI):} {\em AppCampus Award}, ``Rayzit Crowd Messaging'', Industrial Grant by Aalto University, Microsoft, Nokia.

\item {\bf 07/2012-11/2012 (co-PI):} {\em Hybrid Indoor Positioning on Multi-Sensor Android Smartphones}, Industrial NRE by Cywee Entertainment Group Ltd., Taiwan (in collaboration with KIOS Research Center, University of Cyprus.

\item {\bf 2012-2013 (Mangement Committee (MC) Member):}  {\em Knowledge Discovery from Moving Objects (MOVE)},  COST Action IC0903, European Cooperation in Science and Technology,  http://www.move-cost.info/.

\item {\bf 2012-2013 (Associate Partner):}  {\em Planet-Data Network of Excellence on Large Scale Data Management} - http://www.planet-data.eu/.

\item {\bf 2009-2012 (Associate Partner):}  {\em MODAP (Mobility, Data Mining and Privacy)} Project, funded by EU FET-OPEN 2009-2012 - http://www.modap.org/.

\item  {\bf 2011-2013 (co-PI):} {\em eMammoth - Compute and Store on Grids and Clouds infrastructures}, funded by Cyprus Research Promotion Foundation, ΑΝΑΒΑΘΜΙΣΗ/0609/09, University of Cyprus.

\item  {\bf 2011-2013 (co-PI):} {\em VSense: Vehicular Sensor Networks}, funded by Cyprus Research Promotion Foundation, 2011, University of Cyprus, University of Nicosia Research Foundation, Rutgers University and University of Thessaly, who bring world-class expertise in research areas related to VSNs.

\item  {\bf 2010-2011 (PI):} {\em MobNet: A Mobile Programming Cloud for Data Management Research}, University of Cyprus, Startup Grant, Demetrios Zeinalipour-Yazti (PI).

\item {\bf 02/2006-02/2010 (Collaborator):} {\em AQSIOS: Algorithms and Metrics for New Generation Data Stream Management Systems},
IIS-0534531 (PI: Panos K. Chrysanthis; Co-PIs: Alexandros Labrinidis, Kirk Pruhs)

\item  {\bf 2008-2009 (PI):} {\em SenseView: An Energy Efficient Data Acquisition Framework for Wireless Sensor Networks}, Open University of Cyprus Research Projects, Demetrios Zeinalipour-Yazti (PI), Dimitrios Gunopulos (UCR), Vana Kalogeraki (UCR), Panos Chrysanthis (Uni. of Pittsburgh), George Samaras (Uni. of Cyprus).

\item  {\bf 2010-2014 (participant):} {\em EGI-InSPIRE project (Integrated Sustainable Pan-European Infrastructure for Researchers in Europe)}, co-funded by the European Commission FP7, contract number: RI-261323), as a collaborative effort involving more than 50 institutions in over 40 countries. Its mission is to establish a sustainable European Grid Infrastructure (EGI).  {\tt http://www.egi.eu/projects/egi-inspire/}.

\item  {\bf 2008-2012 (participant):} {\em Cooperating Objects Network Of Excellence}, EU-funded project under ICT FP7, Partners: UNIPI, ETHZ, SICS, UCY, ISEP-IPP, SAP, SCHNEIDER, AICIA, UPO, TI, AICIA, {\tt http://www.cooperating-objects.eu/}.


\item  {\bf 2006-2010 (experienced researcher):} {\em SEARCHiN: SEARCHing in a Networked world}, Marie Curie Host Fellowships for the Transfer of Knowledge (ToK),Marie Curie Actions, CORDIS, European Commission, M. D. Dikaiakos (UCY), Demetrios Zeinalipour-Yazti (UCY), Y. Dimopoulos (UCY), Yannis Ioannidis (University of Athens), Rizos Sakellariou (Univ. of Manchester), Norman Paton (Univ. of Manchester), Carole Goble (Univ. of Manchester), \\
 {\tt http://grid.ucy.ac.cy/SEARCHiN/}.


\item {\bf 2006 - 2010 (participant):} {\em EU Enabling Grids for E-sciencE (EGEE)}, \#IST-2003-508833, Information Society Technologies.

\item  {\bf 2008 (PI):} {\em An Experimental Evaluation of the FailRank Grid Monitoring and Ranking System},
{\em EU CoreGRID Network of Excellence Research Exchange Program (REP)}, \#IST-2002-004265, European Research Network on Foundations, Software Infrastructures and Applications for large scale distributed, GRID and Peer-to-Peer Technologies, Artur Andrzejak (Zuse Institute Berlin, Germany), Demetrios Zeinalipour-Yazti (OUC), Chryssis Georgiou (UCY), Marios D. Dikaiakos (UCY), Exchange Researcher: Dr. Artur Andrzejak (Zuse Institute Berlin, Germany).

\item  {\bf 2008 (PI):}  {\em Enhancing FailRank by Machine Learning Methods},
{\em EU CoreGRID Network of Excellence Research Exchange Program (REP)}, \#IST-2002-004265, European Research Network on Foundations, Software Infrastructures and Applications for large scale distributed, GRID and Peer-to-Peer Technologies, Demetrios Zeinalipour-Yazti (OUC), Chryssis Georgiou (UCY), Marios D. Dikaiakos (UCY), Vivi  Fragopoulou (ICS/FORTH), Evangelos Markatos (ICS/FORTH and Univ. of Crete),  Exchange Researcher: Harris Papadakis (ICS/FORTH and Univ. of Crete).

\item {\bf 2004 - 2008 (participant):} {\em EU CoreGRID Network of Excellence}, \#IST-2002-004265, European Research Network on Foundations, Software Infrastructures and Applications for large scale distributed, GRID and Peer-to-Peer Technologies.

\item  {\bf 2002 - 2005 (participant):} {\em ``Understanding Change in Spatiotemporal Data''}, {\em US National Science Foundation} \#0220148.

\item {\bf 2004 - 2005 (participant):} {\em ``An Adaptive and Scalable Architecture for Dynamic Sensor Networks''}, {\em US National Science Foundation} \#0330481.

\item {\bf 2000 - 2001 (young investigator):} {\em ``An extensible Retrieval, Annotation and Caching Engine''}, Cyprus Research Promotion Foundation (PENEK 23/2000).

\end{itemize}



\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%			PROFESSIONAL ACTIVITY \& MEMBERSHIPS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\renewcommand{\labelitemi}{$\bullet$}

\section{\bf PROFESSIONAL ACTIVITY \& MEMBERSHIPS}
\begin{itemize}
\setlength{\itemsep}{0.80ex}
\item {\bf Editorial Boards:}
\begin{itemize}
\item[-] {\bf Associate Editor}, {\bf Distributed and Parallel Databases} journal, {\bf Springer Press}, Heidelberg, Germany, Editors-in-Chief: Mohamed Mokbel (University of Minnesota, MN, USA) and Divyakant Agrawal (University of California - Santa Barbara, CA, USA), {\bf (05/2017 - current)}.
\item[-] {\bf Associate Editor}, {\bf Big Data Research} journal, {\bf Elsevier Press}, Amsterdam, Netherlands, Z. Wu (Zhejiang University, Hangzhou, China), T. Palpanas (Paris Descartes Univerity, Paris, France) {\bf (04/2016 - current)}.
\item[-] {\bf Associate Editor}, {\bf International Journal of Cooperative Information Systems} journal, {\bf World Scientific},  Singapore, Editors-in-Chief: Heiko Ludwig (IBM Almaden Research Center, USA), Gunter Schlageter, (University of Hagen, Germany), Vassilis J Tsotras (University of California - Riverside, USA). {\bf (02/2018 - current)}.

\end{itemize}

\item {\bf Organizing Committee Member:}
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item[-] {\bf Program Committee Co-Chair} [with Jianliang Xu (Hong Kong Baptist University, Hong Kong), Mohamed F. Mokbel (University of Minnesota - Twin Cities, MN, USA)]: 20th IEEE International Conference on Mobile Data Management (MDM'19), Hong Kong, June 30 - July 5, {\bf 2019}.
\item[-] {\bf Local Advisory Committee}: 23rd Pan-Hellenic Conference on Informatics (PCI), Nicosia, Cyprus, November 28 - 30, {\bf 2019}.
\item[-] {\bf Program Committee Co-Chair} [with Herodotos Herodotou (Cyprus University of Technology, Cyprus)]: 16th Hellenic Data Management Symposium (HDMS'18), Larnaca, Cyprus, July 2 - July 4, {\bf 2018}.
\item[-] {\bf Panel Chair and Session Chair}: 19th IEEE International Conference on Mobile Data Management (MDM'18), Aalborg, Denmark, June 25 - June 28, {\bf 2018}.
\item[-] {\bf Area PC Vice-Chair} for {\em ``Temporal, Spatial, Mobile, and Multimedia Data.''}, The 34th IEEE International Conference on Data Engineering {\bf (IEEE ICDE'18)}, Paris, France, April, 16-20, 2018.
\item[-] {\bf Senior TPC Member}, The APWeb-WAIM Joint Conference on Web and Big Data {\bf APWeb-WAIM'18}, Macau, China, July 23-25, {\bf 2018}.
\item[-] {\bf Advisory Board Member}: Euro-Par Advisory Board, {\bf 2017}.
\item[-] {\bf Publicity Co-Chair}: 4th IEEE International Conference on Big Data and Smart Computing (BigComp'17), Jeju Islands, Korea, Feb. 13-16, {\bf 2017}.
\item[-] {\bf Program Committee Co-Chair} [with Yuka Kato (TWC University, Japan), Takuya Yoshihiro (Wakayama University, Japan)]:  1st Intl. Workshop On Mobile Ubiquitous Systems, Infrastructures, Communications, And AppLications (MUSICAL'16), with EAI's MobiQuitous, November 28, 2016, Hiroshima, Japan. {\bf 2016}.
\item[-] {\bf Advanced Seminar Co-Chair} [with Mario Nascimento (Univ. of Alberta, Canada)]: 17th IEEE International Conference on Mobile Data Management (MDM'16), Porto, Portugal, July 13-16, {\bf 2016}.
\item[-] {\bf Program Committee Co-Chair} [with Konstantinos Pelechrinis (Univ. of Pittsburgh, USA), Adam J. Lee (Univ. of Pittsburgh, USA) and Manolis Terrovitis (IMIS Athena, Greece)]:  3rd International Workshop On Human Mobility Computing and Privacy (HuMoComP 2015), held in conjunction with the 16th IEEE MDM 2015, June 18, 2015 - Pittsburgh, PA, USA, {\bf 2015}.
\item[-] {\bf Workshops Co-Chair} [with  Wang-Chien Lee (Univ. of Pennsylvania, USA)]: 16th IEEE International Conference on Mobile Data Management (MDM'15), June 18, 2015 - Pittsburgh, PA, USA, {\bf 2015}.
\item[-] {\bf Panel Co-Chair} [with  Shonali Krishnaswamy (I2R, Singapore)]: 15th IEEE International Conference on Mobile Data Management (MDM'14), Brisbane, Australia, July 14-18, {\bf 2014}.
\item[-] {\bf Demo Co-Chair} : 14th IEEE International Conference on Mobile Data Management (MDM'13). , Milan, Italy, June 3, {\bf 2013}.
\item[-] {\bf Publicity and Session Chair}: 13th International Conference on Web Information System Engineering (WISE'12), Paphos, Cyprus, November 28-30, {\bf 2012}.
\item[-] {\bf Steering Committee Member} : 10th International ACM Workshop on Data Engineering for Wireless and Mobile Access (MobiDE'11), collocated with ACM SIGMOD, Athens, Greece, June 12, {\bf 2011}.
\item[-] {\bf General Co-Chair} [with  Wang-Chien Lee (Univ. of Pennsylvania, USA)]: DMSN 2011 - The 8th International Workshop on Data Management for Sensor Systems (DMSN'11), collocated with VLDB'11, Westin, Seattle, WA, Aug. 29, {\bf 2011}.
\item[-] {\bf Poster Co-Chair} [with  Alexandros Labrinidis (Univ. of Pittsburgh, USA) and Vassilis Vassalos (AUEB, Greece)]: HDMS 2010 - 9th Hellenic Data Management Symposium, Ayia Napa, Cyprus, June 30th - July 3, {\bf 2010}.
\item[-] {\bf General Co-Chair} [with  Phillip B. Gibbons (Intel Labs Pittsburgh, USA)]: 9th International ACM Workshop on Data Engineering for Wireless and Mobile Access (MobiDE'10), collocated with ACM SIGMOD, Indianapolis, Indiana, USA, June 6-11, {\bf 2010}.
\item[-] {\bf Contest Organization Chair}: The 10th IEEE International Conference on Data Mining (ICDM'10), Sydney, Australia, December 13-17, {\bf 2010}.
\item[-] {\bf Program Committee Co-Chair} [with Wang-Chien Lee (Penn State Univ., USA)]: The 7th International Workshop on Data Management for Sensor Networks (DMSN'10), collocated with VLDB'10, Singapore, Sept. 13, {\bf 2010}.
\item[-] {\bf Organizing Chair and Session Chair}: 9th Helenic Data Management Symposium (HDMS'10), Ayia Napa, Cyprus, {\bf 2010}.
\item[-] {\bf Program Committee Co-Chair} [with Vijay Kumar (Univ. of Missouri - Kansas City, USA) and Takahiro Hara (Osaka Univ, Japan)]: 11th International Conference on Mobile Data Management (MDM'10), Kansas City, Missouri, USA, May 23rd to May 26, {\bf 2010}.
\item[-] {\bf Program Committee Co-Chair} [with Le Gruenwald (Univ. of Oklahoma , USA)]: 8th International ACM Workshop on Data Engineering for Wireless and Mobile Access (MobiDE'09), collocated with ACM SIGMOD, Providence, Rhode Island, USA, June 29, {\bf 2009}.
\item[-] {\bf Publicity Chair}: 7th International ACM Workshop on Data Engineering for Wireless and Mobile Access (MobiDE'08), collocated with ACM SIGMOD, Vancouver, Canada, June 13, {\bf 2008}.
\item[-] {\bf Session Chair}: Wireless Networks session, 12th IEEE International Conference on Mobile Data Management (MDM'11), 6-9 June,  Lule\aa, Sweden, {\bf 2011}.
\item[-] {\bf Session Chair}: Modeling and Programming Sensor Networks session, $4^{th}$ Intl. Workshop on Data Management for Sensor Networks (DMSN), in conjunction with the Very Large Data Base Conference, Vienna, Austria, September {\bf 2007}.
\item[-] {\bf Session Chair}: Fault tolerance and Dependability session, CoreGRID Workshop on Grid Programming Models and P2P Systems Architecture (Coregrid), Heraklion, Crete, Greece, June 12-13, {\bf 2007}.
\end{itemize}
\item {\bf Technical Program Committee Member:}
\begin{itemize}
\setlength{\itemsep}{0.10ex}
%
\vspace{0.1in}
\item[]{\bf 2019 TPC Activity\hrulefill }
%
\item[-] {\bf TPC Member}, The 25th Annual ACM SIGKDD International Conference on Knowledge Discovery and Data Mining {\bf (ACM SIGKDD'19)}, Anchorage, Alaska, USA, August 4-8, {\bf 2019}. 
\item[-] {\bf TPC Member}, The 1st International Workshop on Blockchain and Data Management (BlockDM 2019), In Conjunction with ICDE 2019, Macau SAR, China, 8-12 April {\bf 2019}.
\item[-] {\bf TPC Member}, The 45th International Conference on Very Large Data Bases {\bf (VLDB'19)}, Los Angeles, California, USA, August 26-30, {\bf 2019}.
\item[-] {\bf TPC Member}, The 22nd International Conference on Extending Database Technology {\bf (EDBT'19)}, Lisbon, Portugal, March 26-29, {\bf 2019}.
\item[-] {\bf TPC Member}, The 2nd workshop on ``Big Mobility Data Analytics'' {\bf (BMDA'19)}, collocated with 22nd International Conference on Extending Database Technology , Lisbon, Portugal, March 26-29, {\bf 2019}.

\vspace{0.1in}
\item[]{\bf 2018 TPC Activity\hrulefill }
%
\item[-] {\bf TPC Member}, 2nd IEEE workshop on Human-Machine Collaboration in BigData {\bf (IEEE HMData'18)}, collocated with IEEE Big Data, Seattle, WA, USA, December 10-13, {\bf 2018}.
\item[-] {\bf TPC Member}, The 9th ACM SIGSpatial International Workshop Indoor Spatial Awareness {\bf (ISA'18)}, in conjunction with ACM SIGSpatial Conference 2018,  November 06, 2018 - Seattle, Washington, USA, with ACM SIGSPATIAL {\bf 2018}.
\item[-] {\bf TPC Member}, 7th Intl. Workshop on Big Data, IoT Streams and Heterogeneous Source Mining: Algorithms, Systems, Programming Models and Applications ({\bf BigMine-18}) at ACM KDD 2018, London, UK, August 20, {\bf 2018}.
\item[-] {\bf TPC Member}, 26th ACM SIGSPATIAL International Conference on Advances in Geographic Information Systems ({\bf ACM SIGSPATIAL 2018}), Seattle, Washington, USA, Nov. 6 - Nov. 9, {\bf 2018}.
\item[-] {\bf Senior TPC Member}, The APWeb-WAIM Joint Conference on Web and Big Data {\bf APWeb-WAIM'18}, Macau, China, July 23-25, {\bf 2018}.
\item[-] {\bf TPC Member}, The 21st International Conference on Extending Database Technology {\bf (EDBT'18)}, Demo Track, Vienna, Austria, March 26-29, {\bf 2018}.
\item[-] {\bf TPC Member}, The 38th IEEE International Conference on Distributed Computing Systems,  {\bf (ICDCS'18)}, Demo Track, Vienna, Austria, July 2 – 5, 2018, {\bf 2018}.
\item[-] {\bf TPC Member}, The 27th ACM International Conference on Information and Knowledge Management   {\bf (CIKM'18)}, Demo Track, Lingotto, Turin, Italy, October 22-26, {\bf 2018}.
\item[-] {\bf TPC Member}, The 5th ACM International Workshop on Exploratory Search in Databases and the Web {\bf (ExploreDB 2018)}, co-located with ACM SIGMOD 2018, Houston, TX, USA, June 15, {\bf 2018}.
\item[-] {\bf TPC Member}, The 19th IEEE International Conference on Mobile Data Management {\bf (IEEE MDM'18)}, AAU, Aalborg, Denmark, June 25 - June 28, {\bf 2018}.
\item[-] {\bf TPC Member}, The 37th International Conference on Management of Data ACM SIGMOD {\bf (SIGMOD'18)}, Demo Track, Houston, TX, USA, June 10th - June 15th, {\bf 2018}.
\item[-] {\bf TPC Member} for {\em ``Lightning Talks''} track chaired by Stefan Manegold (CWI, Netherlands) and Timos Sellis (Swinburne Univ. of Technology, Australia), The 34th IEEE International Conference on Data Engineering {\bf (IEEE ICDE'18)}, Paris, France, April, 16-20, 2018.

\vspace{0.1in}
\item[]{\bf 2017 TPC Activity\hrulefill }
%

\item[-] {\bf TPC Member}, IEEE workshop on Human-Machine Collaboration in BigData {\bf (IEEE HMData'17)}, collocated with IEEE Big Data 2017, Boston, MA, USA, December 11-14, {\bf 2017}.
\item[-] {\bf TPC Member}, 6th International Workshop on Big Data, Streams and Heterogeneous Source Mining: Algorithms, Systems, Programming Models and Applications {\bf (BigMine'17)}, collocated with ACM KDD 2017, Halifax, Nova Scotia, Canada August 14, {\bf 2017}.
\item[-] {\bf TPC Member}, Indoor Positioning Technology and Location-based Mobile Applications {\bf (IEEE IPT'17)}, KAIST, Taejeon, South Korea, May 29, {\bf 2017}.
\item[-] {\bf TPC Member}, The APWeb-WAIM Joint Conference on Web and Big Data 2017 {\bf (APWeb-WAIM'17)}, Beijing, China, July 07-09, {\bf 2017}.
\item[-] {\bf TPC Member}, The 8th IEEE International Conference on Big Knowledge {\bf (IEEE ICKB'17)}, Hefei, China, August 9 -10, {\bf 2017}.
\item[-] {\bf TPC Member}, The 18th IEEE International Conference on Mobile Data Management {\bf (IEEE MDM'17)}, KAIST, Taejeon, South Korea, May 29 - June 1, {\bf 2017}.
\item[-] {\bf TPC Member}, The 4th ACM International Workshop on Exploratory Search in Databases and the Web {\bf (ExploreDB 2017)}, Raleigh, North Carolina, USA, on May 14-19, 2017, co-located with ACM SIGMOD 2017.
\item[-] {\bf TPC Member}, The 20th International Conference on Extending Database Technology {\bf (EDBT'17) Demo Track}, Venice, Italy, March 21-24, {\bf 2017}.
\item[-] {\bf TPC Member}, The 20th International Conference on Extending Database Technology {\bf (EDBT'17) Research Track},  Venice, Italy, March 21-24, {\bf 2017}.
\item[-] {\bf TPC Member}, IEEE Workshop on Scalable Internet of Things (S-IoT) {\bf (MoWNeT)}, Avignon, France, 17-19 May, {\bf 2017}.

\vspace{0.1in}
\item[]{\bf 2016 TPC Activity\hrulefill }
%
\item[-] {\bf TPC Member}, The 8th ACM SIGSpatial International Workshop Indoor Spatial Awareness {\bf (ISA'16)}, in conjunction with ACM SIGSpatial Conference 2016, October 31 - November 3, 2016, San Francisco Bay Area, CA, USA, {\bf 2016}.
\item[-] {\bf TPC Member}, 5th International Workshop on Big Data, Streams and Heterogeneous Source Mining: Algorithms, Systems, Programming Models and Applications {\bf (BigMine'16)}, collocated with ACM KDD 2016, San Francisco, CA, USA, August 14, {\bf 2016}.
\item[-] {\bf TPC Member}, The European Conference on Machine Learning and Principles and Practice of Knowledge Discovery in Databases {\bf (ECML/PKDD'16)}, Riva del Garda, Italy, September 19-23, {\bf 2016}.
\item[-] {\bf TPC Member}, The 36th IEEE International Conference on Distributed Computing Systems (ICDCS 2016) {\bf (IEEE ICDCS'16)}, Nara, Japan, June 27-30, {\bf 2016}.
\item[-] {\bf TPC Member}, The 17th IEEE International Conference on Mobile Data Management {\bf (IEEE MDM'16)}, Porto, Portugal, June 13-16, {\bf 2016}.
\item[-] {\bf TPC Member}, The 32nd IEEE International Conference on Data Engineering {\bf (IEEE ICDE'16)}, Helsinki, Finland, April 7-11, {\bf 2016}.
\item[-] {\bf TPC Member}, 19th International Conference on Extending Database Technology {\bf (EDBT'16)},  Bordeaux, France, March 15-18, {\bf 2016}.
\item[-] {\bf TPC Member}, The 3rd ACM International Workshop on Enriched Geo-Spatial Data {\bf (GeoRich 2016)}, San Francisco, CA, USA, June 26, 2016, co-located with ACM SIGMOD 2016.
\item[-] {\bf TPC Member}, The 3rd ACM International Workshop on Exploratory Search in Databases and the Web {\bf (ExploreDB 2016)}, San Francisco, CA, USA, June 26, 2016, co-located with ACM SIGMOD 2016.
\item[-] {\bf TPC Member}, The 2016 International Workshop on Scalable Internet of Things {\bf (S-IoT'16)}, Cairo, Egypt, April 11-13, {\bf 2016}.
\item[-] {\bf TPC Member}, The 2016 International Conference on Selected Topics in Mobile and Wireless Networking {\bf (MoWNeT)}, April 11-13, {\bf 2016}.
\item[-] {\bf TPC Member}, 14th Hellenic Data Management Symposium {\bf (HDMS'16)}, Athens, Greece, July 28-29, {\bf 2016}.
%
\vspace{0.1in}
\item[]{\bf 2015 TPC Activity\hrulefill }
%
\item[-] {\bf TPC Member}, The 7th ACM SIGSpatial International Workshop Indoor Spatial Awareness {\bf (ISA'15)}, in conjunction with ACM SIGSpatial Conference 2015, Seattle Washington, USA, November 3, {\bf 2015}.
\item[-] {\bf TPC Member}, The 34th International Conference on Management of Data ACM SIGMOD {\bf (SIGMOD'15)}, Research Track, Melbourne, Australia, May 31 - June 4, {\bf 2015}.
\item[-] {\bf TPC Member}, The 16th IEEE International Conference on Mobile Data Management {\bf (IEEE MDM'15)}, Pittsburgh, USA, June 14-18, {\bf 2015}.
\item[-] {\bf TPC Member}, The European Conference on Machine Learning and Principles and Practice of Knowledge Discovery in Databases {\bf (ECML/PKDD'15)}, Porto, Portugal, September 7-11, {\bf 2015}.
\item[-] {\bf TPC Member}, 2nd International Workshop on Exploratory Search in Databases and the Web {\bf (ExploreDB 2015)}, Melbourne, Australia, May 31, 2015, co-located with ACM SIGMOD 2015.
\item[-] {\bf TPC Member}, 3rd International Workshop on Mobile Data Management, Mining, and Computing on Social Networks {\bf (IEEE MobiSocial'15)}, co-located with IEEE MDM'15, Pittsburgh, PA, USA, June 15, {\bf 2015}.
\item[-] {\bf TPC Member}, 13th Hellenic Data Management Symposium {\bf (HDMS'15)}, Athens, Greece, July 30-31, {\bf 2015}.
\item[-] {\bf TPC Member}, IEEE 2nd IEEE International Symposium on Dependable Computing and Internet of Things {\bf (DCIT 2015)}, Wuhan, China, Nov 16-18, {\bf 2015}.
\item[-] {\bf TPC Member}, 5th International Conference on Model \& Data Engineering (MEDI 2015) Island of Rhodes, Greece, 26-28 September 2015.
\item[-] {\bf TPC Member}, 13th Hellenic Data Management Symposium {\bf (HDMS'15)}, Athens, Greece, July 30-31, {\bf 2015}.

%
\vspace{0.1in}
\item[]{\bf 2014 TPC Activity\hrulefill }
%
\item[-] {\bf TPC Member}, The European Conference on Machine Learning and Principles and Practice of Knowledge Discovery in Databases {\bf (ECML/PKDD'14)}, Nancy, France, September 15-19, {\bf 2014}.
\item[-] {\bf TPC Member}, 2nd International Workshop on Mobile Data Management, Mining, and Computing on Social Networks {\bf (MobiSocial 2014)}, co-located with PAKDD, Tainan, Taiwan, May 13, {\bf 2014}.
\item[-] {\bf TPC Member}, The 15th IEEE International Conference on Mobile Data Management {\bf (IEEE MDM'14)}, Brisbane, Australia, July 14-18, {\bf 2014}.
\item[-] {\bf TPC Member},
1st International Workshop on Mining Urban Data {\bf (MUD 2014)}, Athens, Greece, March 28, 2014, co-located with EDBT/ICDT 2014.
\item[-] {\bf TPC Member},
1st International Workshop on Exploratory Search in Databases and the Web {\bf (ExploreDB 2014)}, Athens, Greece, March 28, 2014, co-located with EDBT/ICDT 2014.
\item[-] {\bf TPC Member}, The 2014 ACM SIGMOD International Conference on Management of Data {\bf (SIGMOD'14)}, Demo Track, Snowbird, USA, June 22-27, {\bf 2014}.
\item[-] {\bf TPC Member}, IEEE 30th International Conference on Data Engineering {\bf (IEEE ICDE'14)}, Chicago, IL, USA, April 7-11, {\bf 2014}.

%
\vspace{0.1in}
\item[]{\bf 2013 TPC Activity\hrulefill }
%
\item[-] {\bf TPC Member},
1st International Workshop on Pervasive Urban Crowdsensing Architecture and Applications (PUCAA 2013) (https://sites.google.com/site/pucaaworkshop2013/), which wiill be held on September 9th, 2013 in Zurich, Switzerland in conjunction with Ubicomp 2013.
\item[-] {\bf TPC Member}, 2nd International Workshop on Big Data, Streams and Heterogeneous Source Mining: Algorithms, Systems, Programming Models and Applications {\bf (BigMine'13)}, collocated with ACM KDD 2013, Chicago, IL, USA, August 11-14, {\bf 2013}.
\item[-] {\bf TPC Member}, IEEE International Workshop on Mobile Data Management, Mining, and Computing on Social Networks (MobiSocial 2013), in conjunction with IEEE MDM'13, Milan, Italy, June 3-6, {\bf 2013}.
\item[-] {\bf TPC Member}, The 2013 ACM SIGMOD International Conference on Management of Data {\bf (SIGMOD'13)}, Demo Track, New York, USA, June 22-27, {\bf 2013}.
\item[-] {\bf TPC Member}, The 14th IEEE International Conference on Mobile Data Management {\bf (IEEE MDM'13)},
Milan, Italy, June 3-6, {\bf 2013}.
\item[-] {\bf TPC Member}, The 39th International Conference on Very Large Databases {\bf (VLDB'13)}, Demo Track, Riva del Garda, Trento, August 26th - 31st, {\bf 2013}.
\item[-] {\bf TPC Member}, IEEE 29th International Conference on Data Engineering {\bf (IEEE ICDE'13)}, Brisbane, Australia, April 8-11, {\bf 2013}.

%
\vspace{0.1in}
\item[]{\bf 2012 TPC Activity\hrulefill }
%
\item[-] {\bf TPC Member}, 1st International Workshop on Big Data, Streams and Heterogeneous Source Mining: Algorithms, Systems, Programming Models and Applications {\bf (BigMine'12)}, collocated with ACM KDD 2012, Beijing, China, August 12, {\bf 2012}.
\item[-] {\bf TPC Member}, The 1st International Workshop on Data Management in Participatory Sensing {\bf (DMPS'12)}, collocated with IEEE MDM, Bengaluru, India, July 23-26, {\bf 2012}.
\item[-] {\bf TPC Member}, The 11th International ACM Workshop on Data Engineering for Wireless and Mobile Access {\bf (ACM MobiDE'12)}, collocated with ACM SIGMOD, Scottsdale, Arizona, USA, May 20th, {\bf 2012}.
\item[-] {\bf TPC Member}, 11th Hellenic Data Management Symposium {\bf (HDMS'12)}, Chania, Greece, June, {\bf 2012}.
\item[-] {\bf TPC Member}, The 13th International Conference on Mobile Data Management {\bf (IEEE MDM'12)}, Bangalore, India, July 23-26, {\bf 2012}.
\item[-] {\bf TPC Member}, The 2012 ACM SIGMOD International Conference on Management of Data {\bf (SIGMOD'12)}, Demo Track, Scottsdale, Arizona, USA, May 20, 2012 - May 25, {\bf 2012}.'

%
\vspace{0.1in}
\item[]{\bf 2011 TPC Activity\hrulefill }
%
\item[-] {\bf TPC Member}, The European Conference on Machine Learning and Principles and Practice of Knowledge Discovery in Databases {\bf (ECML/PKDD'11)}, Athens, Greece, 5-9 September {\bf 2011}.
\item[-] {\bf TPC Member}, The 17th Annual ACM SIGKDD International Conference on Knowledge Discovery and Data Mining {\bf (ACM SIGKDD'11)}, San Diego, California, USA, August {\bf 2011}.
\item[-] {\bf TPC Member}, 6th International Workshop on Using P2P, Grid and Agents for the Development of Content Networks {\bf (UPGRADE-CN'11)}, collocated with CCGrid 2011, Newport Beach, CA, USA, May 23-26 {\bf 2011}.
\item[-] {\bf TPC Member}, 1st Workshop on New Trends in Similarity Search {\bf (NTSS'11)}, collocated with the EDBT 2011 Conference, Uppsala, Sweden, March 21-25, {\bf 2011}.
\item[-] {\bf TPC Member}, 10th Hellenic Data Management Symposium {\bf (HDMS'11)}, Athens, Greece, June 17-18, {\bf 2011}.
\item[-] {\bf TPC Member}, The 10th International ACM Workshop on Data Engineering for Wireless and Mobile Access {\bf (ACM MobiDE'11)}, collocated with ACM SIGMOD, Athens, Greece, June 12-16, {\bf 2011}.
\item[-] {\bf TPC Member}, The  2011 International Conference on Collaboration Technologies and
Systems {\bf (CTS'11)},  Philadelphia, Pennsylvania, USA, May 23-27, {\bf 2011}.
\item[-] {\bf TPC Member}, The 12th International Conference on Mobile Data Management {\bf (IEEE MDM'11)}, Lule\aa, Sweden, June 6th to June 9, proceedings by IEEE Computer Society, {\bf 2011}.
\item[-] {\bf TPC Member}, IEEE 27th International Conference on Data Engineering {\bf (IEEE ICDE'11)}, Hannover, Germany, April 11-15, {\bf 2011}.

%
\vspace{0.1in}
\item[]{\bf 2010 TPC Activity\hrulefill }
%
\item[-] {\bf TPC Member}, 9th Hellenic Data Management Symposium {\bf (HDMS'10)}, Ayia Napa, Cyprus, June 30th - July 3, {\bf 2010}.
\item[-] {\bf TPC Member}, IEEE 10th IEEE International Conference on Data Mining {\bf (IEEE ICDM'10)}, Sydney, Australia, December 13-17, {\bf 2010}.
\item[-] {\bf TPC Member}, IEEE 19th ACM International Conference on Information and Knowledge Management {\bf (ACM CIKM'10)}, Domain Specific Data Management Track, Toronto, Canada, Oct 27-29, {\bf 2010}.
\item[-] {\bf TPC Member}, The 9th International Conference on Ontologies, DataBases, and Applications of Semantics  \\
{\bf (ODBASE'10)}, Crete, Greece, Oct 26 - 28, {\bf 2010}.
\item[-] {\bf TPC Member}, IEEE 4th International Workshop on Sensor Network Technologies for the Information Explosion Era {\bf (SeNTIE'10)}, in conjunction with the Mobile Data Management Conference {\bf (IEEE MDM'10)}, Kansas City, Missouri, May 23-26, {\bf 2010}.
\item[-] {\bf TPC Member}, 16th International Euro-Par Conference {\bf (Europar 2010)}, proceedings by Springer, Aug. 31st - Sep. 3, 2010, Ischia - Naples, Italy, {\bf 2010}.
\item[-] {\bf TPC Member}, IEEE 5th International Workshop on Content Delivery Networks {\bf (CDN'10}) in conjunction with the 10th IEEE/ACM International Symposium on Cluster, Cloud and Grid Computing {\bf (CCGrid'10)}, Melbourne, Australia 17-20 May, {\bf 2010}.\

%
\vspace{0.1in}
\item[]{\bf 2009 TPC Activity\hrulefill }
%
\item[-] {\bf TPC Member}, IEEE's 9th International Conference on Information Technology and Applications in Biomedicine, November 5-7, Larnaca, Cyprus, {\bf 2009}.
\item[-] {\bf TPC Member}, ICPP's First International Workshop on Distributed XML Processing: Theory and Practice, in conjunction with the 38th International Conference on Parallel Processing {\bf (ICPP'09)}, September 22-25, 2009, Vienna, Austria, {\bf 2009}.
\item[-] {\bf TPC Member}, VLDB's 6th International Workshop on Data Management for Sensor Networks, in conjunction with the Very Large Data Base Conference {\bf (VLDB'09)}, Lyon, France, August {\bf 2009}.
\item[-] {\bf TPC Member}, IEEE 3rd International Workshop on Sensor Network Technologies for the Information Explosion Era {\bf (SeNTIE'09)}, in conjunction with the Mobile Data Management Conference {\bf (MDM'09)}, Taipei, Taiwan, May 18-21, {\bf 2009}.
\item[-] {\bf TPC Member}, The 13th Pacific-Asia Conference on Knowledge Discovery and Data Mining {\bf (PAKDD'09)}, Bankong, Thailand, April 27th - April 30th {\bf 2009}.
\item[-] {\bf TPC Member}, IEEE 25th International Conference on Data Engineering {\bf (IEEE ICDE'09)}, Demo Program, Shanghai, China, March 29 - April 4, {\bf 2009}.

%
\vspace{0.1in}
\item[]{\bf 2008 TPC Activity\hrulefill }
%
\item[-] {\bf TPC Member}, IEEE 8th International Conference on Data Mining {\bf (IEEE ICDM'08)}, Pisa, Italy, December 15-19, {\bf 2008}.
\item[-] {\bf TPC Member}, IEEE Future Generation Communication and Networking, International Workshop on Peer-to-Peer Computing for Information Search {\bf (P2PSearch'08)}, Hainan Island, China, {\bf 2008}.
\item[-] {\bf TPC Member}, VLDB's 5th International Workshop on Data Management for Sensor Networks, in conjunction with the Very Large Data Base Conference {\bf (VLDB'08)}, Auckland, New Zealand, August {\bf 2008}.
\item[-] {\bf TPC Member}, 2nd International Workshop on Peer-to-Peer Computing for Information Search {\bf (P2PSearch'08)}, in conjunction with FGCN 2008, Hainan Island, China, {\bf 2008}.
\item[-] {\bf TPC Member}, ACM 7th International Workshop on Data Engineering for Wireless and Mobile Access {\bf (ACM MobiDE'08)}, in conjunction with the International Conference on Management of Data {\bf (SIGMOD'08)}, Vancouver, Canada, {\bf 2008}.
\item[-] {\bf TPC Member}, IEEE International Workshop on Sensor Network Technologies for the Information Explosion Era {\bf (SeNTIE'08)}, in conjunction with the Mobile Data Management Conference {\bf (MDM'08)}, Beijing, China, April {\bf 2008}.
\item[-] {\bf TPC Member}, IEEE International Conference on Sensor Networks, Ubiquitous, and Trustworthy Computing {\bf (SUTC'08)}, Taichung, Taiwan, June {\bf 2008}.
\item[-] {\bf TPC Member}, IEEE 22st International Conference on Advanced Information Networking and Applications {\bf (IEEE AINA'08)}, Okinawa, Japan {\bf 2008}.

%
\vspace{0.1in}
\item[]{\bf 2007 TPC Activity\hrulefill }
%
\item[-] {\bf TPC Member}, VLDB's 4th International Workshop on Data Management for Sensor Networks, in conjunction with the Very Large Data Base Conference {\bf (VLDB'07)}, Vienna, Austria, September {\bf 2007}.
\item[-] {\bf TPC Member}, ACM 6th International Workshop on Data Engineering for Wireless and Mobile Access {\bf (ACM MobiDE'07)}, in conjunction with the International Conference on Management of Data {\bf (SIGMOD'07)}, Beijing, China, {\bf 2007}.
\item[-] {\bf TPC Member}, IEEE 21st International Conference on Advanced Information Networking and Applications {\bf (IEEE AINA'07)}, Internet Computing and Web Applications, Niagara Falls, Canada, {\bf 2007}.
\end{itemize}

\item {\bf Referee for Journals and Magazines:}
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item[-] ACM SIGMOD Record (since 2015) - {\bf 1 review}
\item[-] ACM Computing Surveys (since 2018) - {\bf 1 review}
\item[-] ACM Transactions on Autonomous and Adaptive Systems {\bf (ACM TAAS}) Journal (since 2014) - {\bf 1 review}
\item[-] ACM Transactions on Intelligent Systems and Technology {\bf (ACM TIST}) Journal (since 2011) - {\bf 2 reviews}
\item[-] ACM Transactions on Spatial Algorithms and Systems {\bf (ACM TSAS}) Journal (since 2016) - {\bf 1 review}
\item[-] ACM Transactions on Storage {\bf (ACM TOS}) Journal (since 2010) - {\bf 1 review}

\item[-] IEEE Transactions on Knowledge and Data Engineering {\bf (IEEE TKDE}) Journal (since 2005) - {\bf 14 reviews}
\item[-] IEEE Transactions on Mobile Computing {\bf (IEEE TMC}) Journal (since 2010) - {\bf 3 reviews}
\item[-] IEEE Transactions on Vehicular Technology {\bf (IEEE TVT}) Journal (since 2010) - {\bf 1 review}
\item[-] IEEE Transactions on Computers {\bf (IEEE TC}) Journal (since 2010) - {\bf 2 reviews}
\item[-] IEEE Transactions on Distributed and Parallel Systems {\bf (IEEE TPDS}) Journal (since 2008) - {\bf 2 reviews}

\item[-] IEEE Transactions on Evolutionary Computation {\bf (IEEE TEC}) Journal (since 2005) - {\bf 2 reviews}
\item[-] IEEE Transactions on Services Computing {\bf (IEEE TSC}) Journal (since 2014) - {\bf 1 review}

\item[-] IEEE Internet Computing Magazine {\bf (IEEE IC}) - Special Issue on Cloud Computing (since 2008) - {\bf 2 reviews}
\item[-] IEEE Internet of Things {\bf (IEEE IoT}) Journal (since 2016) - {\bf 1 review}
\item[-] IEEE Network Magazine (since 2004) - {\bf 1 review}
\item[-] IEEE Communications Letters (since 2011) - {\bf 1 review}
\item[-] Springer's Very Large Databases {\bf (VLDB}) Journal (since 2007) - {\bf 3 reviews}
\item[-] Springer's Distributed and Parallel Databases {\bf (DAPD}) Journal (since 2008) - {\bf 3 reviews}
\item[-] Springer's Data Mining and Knowledge Discovery {\bf (DAMI}) Journal (since 2005) - {\bf 3 reviews}
\item[-] Springer's Knowledge and Information Systems {\bf (KAIS}) Journal (since 2011) - {\bf 3 reviews}
\item[-] Elsevier's Information Systems {\bf (InfoSys}) Journal (since 2011) - {\bf 2 reviews}
\item[-] Elsevier's Ad hoc Networks {\bf (Adhoc}) Journal (since 2005) - {\bf 3 reviews}
\item[-] Elsevier's Information Sciences {\bf (InfoSciences}) Journal (since 2004) - {\bf 4 reviews}
\item[-] Elsevier's Computer Communications  {\bf (ComCom}) Journal (since 2006) - {\bf 5 reviews}
\item[-] Elsevier's Journal of Parallel and Distributed Computing {\bf (JPDC}) Journal (since 2007) - {\bf 2 reviews}
\item[-] Elsevier's Journal of Systems and Software {\bf (JSS}) Journal (since 2008) - {\bf 1 review}
\item[-] Elsevier's Journal of Knowledge \& Data Engineering {\bf (DKE}) Journal (since 2010) - {\bf 1 review}
\item[-] Elsevier's Pervasive and Mobile Computing {\bf (PMC}) Journal (since 2016) - {\bf 1 review}
\item[-] Oxford's Computer Journal (since 2011) - {\bf 1 review}

\item[-] Wiley's Wireless Communications and Mobile Computing {\bf (WCM) - {\bf 1 review}}
\end{itemize}

\item {\bf Referee for Conferences/Symposiums (in addition to PC appointments):}
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item[-] ACM SIGMOD - Intl. Management of Data Conference, 2009.
\item[-] ACM PAVLAD - First Intl. Workshop on Privacy and Anonymity for Very Large Datasets, with CIKM'2009, Hong Kong, China, 2009.
\item[-] ACM Intl. Conference on Computing Frontiers, Ischia, Italy, 2009.
\item[-] SAGT - 4th Intl. Symposium on Algorithmic Game Theory, Salerno - Amalfi Coast, Italy, 2011.
\item[-] IEEE MDM - Intl. Conference on Mobile Data Management, Tapei, Taiwan, 2009.
\item[-] ACM SIGMOD - Intl. Management of Data Conference, 2008.
\item[-] IEEE MDM - Intl. Conference on Mobile Data Management, Beijing, China, 2008.
\item[-] EuroPar - 14th International Euro-Par Conference, 2008.
\item[-] IEEE IPDPS -  Intl. Parallel and Distributed Processing Symposium 2008.
\item[-] ACM CIKM - Intl. Information and Knowledge Management Conference,  2007.
\item[-] IEEE AINA - Intl. Conference on Advanced Information Networking and Applications, 2007.
\item[-] HDMS - 6th Hellenic Data Management Symposium, 2007.
\item[-] ACM CIKM - Intl. Information and Knowledge Management Conference, 2006.
\item[-] OPODIS -  Intl. Principles of Distributed Systems Conference, 2006.
\item[-] ACM SIGMOD - Intl. Management of Data Conference, 2005.
\item[-] ACM PODS - Intl. Principles of Database Systems Symposium, 2005.
\item[-] IEEE ICPS - Intl. Pervasive Services Conference,  2005.
\item[-] ACM SIGKDD - Intl. Knowledge Discovery and Data Mining Conference, 2005.
\item[-] ACM GIS - Intl. Advances in Geographic Information Systems Symposium, 2005.
\item[-] PAKDD - Pacific-Asia Conference on Knowledge Discovery and Data Mining, 2005.
\item[-] ICESS - Intl. Embedded Software and Systems Conference, 2005.
\item[-] VLDB - Very Large Data Bases  Conference, 2004, 2009
\item[-] ACM SAC - Intl. Applied Computing Symposium, 2004.
\end{itemize}

\item {\bf External Referee for Workshops (in addition to PC appointments):}
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item[-] IEEE SME (MDM) - Intl. Workshop on Semantics in Mobile Environments, 2005.
\item[-] ACM WebKDD (SIGKDD) - Intl. Workshop on Knowledge Discovery in the Web, 2005.
\item[-] DBISP2P (VLDB) - Intl. Workshop on Databases, Information Systems, and Peer-to-Peer Computing, 2004.
\item[-] DMSN (VLDB) - Intl. Workshop on Data Management for Sensor Networks, 2005.
\end{itemize}

\item  {\bf Proposal Evaluator:}
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item[-] Proposal Evaluator, 2nd Ph.D. Fellowship Program 2019-2020, {\bf Hellenic Foundation for Research and Innovation (H.F.R.I.)}, 1/12/2018 - 31/01/2019. %0
\item[-] Proposal Evaluator, {\bf Marie Sklodowska-Curie Individual Fellowships (H2020-MSCA-IF-2017)} call, European Commission Research Executive Agency (REA), 09/10/2017 - 07/12/2017. %1.1
\item[-] Proposal Evaluator (4), Trans-Domain Proposals (TDP), European Cooperation in Science and Technology (COST), 6/6/2014-26/6/2014.
\item[-] Proposal Evaluator (1), Trans-Domain Proposals (TDP), European Cooperation in Science and Technology (COST), 1/7/2013-19/7/2013.
\item[-] Proposal Evaluator, Senate Committee for the Basic Reseach Funding Program (BRFP), Athens University of Economics and Business, 2010.
\item[-] Moderator/Reviewer for Milestone MJRA 1.3 (NA4), EU Enabling Grids for E-sciencE (EGEE), \#IST-2003-508833, {\em Information Society Technologies}.
\end{itemize}

\item  {\bf Paper Review System Developer:}
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item[-]  5th International Conference Parallel Computing Technologies (PACT 1999), St. Petersburg, Russia, Springer Press, September 6-10, 1999.
\end{itemize}

\item  {\bf Professional Memberships:}
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item[-] {\bf Senior Member of ACM} (Association for Computing Machinery)
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item[-] Member of ACM SIGMOD (ACM Special Interest Group on Management of Data) - since 2008.
\end{itemize}
\item[-] {\bf Senior Member of IEEE} (Institute of Electrical and Electronics Engineers)
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item[-] Member of IEEE CS (Computer Society) 
\item[-] Member of IEEE TCDE (Technical Committee on Data Engineering)
\item[-] Member of IEEE TCI (Technical Committee on Internet)
\item[-] Member of IEEE Big Data Initiative
\end{itemize}
\item[-] Member of USENIX (Advanced Computing Systems Association)
\end{itemize}


\item  {\bf Research Center Affiliation:}
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item[-] {\bf Member} (Cyprus Science and Research Centre) - http://cysrc.eu/index.php/en/
\end{itemize}

\end{itemize}


\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%			PROFESSIONAL ACTIVITY \& MEMBERSHIPS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\renewcommand{\labelitemi}{$\bullet$}

\section{\bf UNIVERSITY AND PUBLIC SERVICE}
\begin{itemize}
\setlength{\itemsep}{0.10ex}
   \item {\bf Board Member}, Department of Computer Science appointed representative at the ``University Security Committee'', University of Cyprus, 01/2019-.

   \item {\bf Board Member}, Faculty of Pure and Applied Sciences Board Member / Department of Computer Science elected representative, University of Cyprus, 09/2018-.
   \item {\bf Expert}, e-University ad-hoc strategy committee consulting the Vice-Rector for International Affairs, Finance and Administration, University of Cyprus, 04/2018-06/2018.
   \item {\bf Board Member}, Postdoctoral Researcher Program, Graduate School, Representative for the School of Pure and Applied Sciences, University of Cyprus, 2017-2018.
   \item {\bf Independent Expert} (Computer Science), Cyprus Council for the Recognition of Higher Education Qualifications (KY.S.A.T.S), 01/2017-12/2017.
   \item {\bf Independent Expert} (Computer Science), Cyprus Council for the Recognition of Higher Education Qualifications (KY.S.A.T.S), 01/2016-12/2016.
   \item {\bf Independent Expert} (Computer Science), Cyprus Council for the Recognition of Higher Education Qualifications (KY.S.A.T.S), 07/2015-12/2015.
   \item {\bf Judge}, MTN Innovation Challenge 2, MTN Cyprus, http://www.mtn-ic.com.cy/, 5/2015 - 10/2015.
   \item {\bf Judge}, MTN Innovation Challenge, MTN Cyprus, http://www.mtn-ic.com.cy/, 5/2014 - 10/2014.
   \item {\bf Member}, Special Technical Committee, Higher Education Academic Program registration process, Ministry of Education, 3/2014-7/2014.
   \item {\bf Coordinator}, Requirement Specification Committee: ``Upgrading and Extending the Network Infrastructure" action, e-University Project,  University of Cyprus, 09/2013-12/2015.
   \item {\bf Trainer}, ``National Olympiad 2013 Camp - University of Cyprus'', Programming and Algorithms,  2013.
   \item {\bf Coordinator}, Computer Engineering Committee, Cyprus Council for the Recognition of Higher Education Qualifications (KY.S.A.T.S), 01/2013-05/2015.
   \item {\bf Trainer}, ``National Olympiad 2012 Camp - University of Cyprus'', Programming and Algorithms  2012.
   \item {\bf Exam Preparator}, ``IT Officer in Web Application Development'' position, Open University of Cyprus , 2011.
   \item {\bf Scientific Team Member}, ``1974 Turkish Invasion Missing Persons Registry'', with M. Dikaiakos and P. Tsimpoglou, 2011.
   \item {\bf Exam Preparator}, ``National Entrance Exam for Public Universities (Computer Science)'', Ministry of Education, 2011.
   \item {\bf Exam Preparator}, ``Cyprus Goverment IT Officer'' position, Ministry of Education, 2010.
   \item {\bf Board Member}, Center for Teaching and Learning (KEDIMA) Committee, Representative for the School of Pure and Applied Sciences, 2009-2012
   \item {\bf Exam Preparator}, ``University Officer'' position, Open University of Cyprus, 2008, 2009.
   \item {\bf Member}, Hiring Committee for one ``Assistant Information Technology Officer'' position, Open University of Cyprus, February 2008.
   \item {\bf Member}, Hiring Committee for five ``Part Time Educational Personnel'' positions, Open University of Cyprus, July 2007.
   \item {\bf Member}, Hiring Committee for two ``Information Technology Officer'' positions, Open University of Cyprus, August 2007.
   \item {\bf Member}, Hiring Committee for one ``Assistant Information Technology Officer'' position, Open University of Cyprus, August 2007.
   \item {\bf Founder}, The eClass Learning Management System at the Open University of Cyprus (http://eclass.ouc.ac.cy/), 2007.
\end{itemize}

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%			DEPARTMENTAL SERVICE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5

\section{\bf DEPARTMENTAL SERVICE}
\begin{itemize}
\setlength{\itemsep}{0.10ex}
   \item {\bf Chair}, Faculty Search Committee, Department of Computer Science appointed chair for a Lecturer/Assistant Professor position on ``Data Management'', University of Cyprus, 01/2019-.
   \item {\bf Chair}, Departmental Committee for IT Systems, 2017-.
   \item {\bf Steering Committee}, 10th National Logipaignion Contest for Students, http://logipaignion.cs.ucy.ac.cy/2017, 2017.
    \item {\bf Evaluator}, Renewal Committee for EEP, University of Cyprus, 2016. % Pavlos Antoniou
   \item {\bf Coordinator}, 2nd National Hour-of-Code (code.org) Initiative with Microsoft Cyprus and the Education Departments of UCY and Frederick (http://code.org/), December 2015.
   \item {\bf Coordinator}, 1st National Hour-of-Code (code.org) Initiative with Microsoft Cyprus and the Education Departments of UCY and Frederick (http://code.org/), December 2014.
   \item {\bf Steering Committee}, 7th National Logipaignion Contest for Elementary and High School Students, http://logipaignion.cs.ucy.ac.cy/2015, 2015.
   \item {\bf Chair}, 6th National Logipaignion Contest for Elementary and High School Students, \\
   http://logipaignion.cs.ucy.ac.cy/2014, 2014.
    \item {\bf Judge}, hack Cyprus contest, University of Cyprus, 2013.
    \item {\bf Board Member} (systems), ``Department of Computer Science Board for Logipaignion Contest'', with V. Vassiliou, G. Pallis, 2013.
   \item {\bf Board Member}, ``Department of Computer Science Board for Field Olympics'', with Y. Sazeides and G. Papadopoulos, 2011.
    \item {\bf Board Member} (systems), ``Department of Computer Science Board for Logipaignion Contest'', with V. Vassiliou, G. Pallis, 2010-2011.
   \item {\bf Member}, Requirement Specification Board for a 50TB Storage Server, University if Cyprus, PLH109/10, 2010.
   \item {\bf Curriculumn Developer}, Restructing sequence/material of undegraduate courses EPL131, EPL132, EPL231, EPL233, 2010.
   \item {\bf Co-Chair}, Logipaignion Organizing Committee, http://www.logipaignion.cs.ucy.ac.cy/, 2010.
   \item {\bf Chair}, Requirement Specification Board 30 Smartphone Devices, University if Cyprus, PLH086/10, 2010.
   \item {\bf Coordinator}, Computer Science Colloquium Series  at the University of Cyprus \\ (http://www.cs.ucy.ac.cy/colloquium/), 2009-current.
   \item {\bf Member}, Graduate Program Committee, Master in Information Systems, Open University of Cyprus September 2008.   
   \item {\bf Founder and Webmaster} of the Master in Information Systems CMS (http://is.ouc.ac.cy/), 2008.
   \item {\bf Member}, Search Committee for ``PhD candidates'', Open University of Cyprus, September 2008.
   \item {\bf Member}, Search Committee for three ``Graduate Research Assistant'' positions, Open University of Cyprus, August 2008.
   \item {\bf Member}, Committee for establishing the ``Graduate Admission Criteria in Information Systems'', Master in Information Systems, Open University of Cyprus 2007.
   

\end{itemize}		


\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%			TEACHING EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5


\section{\bf TEACHING WORK EXPERIENCE}

\subsection*{TEACHING AWARDS}
\begin{center}  % put inside center environment
\begin{tabular*}{1.0\textwidth}%
	{@{\extracolsep{\fill}}lr}
{\bf  Outstanding Teaching Assistant Honorable Mention} 	&  	 2002-2003	\\
\end{tabular*}
\end{center}

\begin{tabular*}{1.0\textwidth} {@{\extracolsep{\fill}}lr}
\parbox[t]{13.2cm}{
Awarded to teaching assistants for their commitment to excellence in teaching,
at the Computer Science Department \& Engr., University of California - Riverside.
}
\end{tabular*}

\begin{center} 
\begin{tabular*}{1.0\textwidth}%
	{@{\extracolsep{\fill}}lr}
{\bf  Outstanding Teaching Assistant Award} 	&  	 2001-2002	
\end{tabular*}
\end{center}

\begin{tabular*}{1.0\textwidth} {@{\extracolsep{\fill}}lr}
\parbox[t]{13.2cm}{
Awarded each year to teaching assistants for their outstanding contribution 
in teaching at the Computer Science Department \& Engr., University of California - Riverside.
}
\end{tabular*}


\subsection*{TEACHING APPOINTMENTS}

\begin{center}  
\begin{tabular*}{1.0\textwidth}%
   {@{\extracolsep{\fill}}lr}
{\bf Lecturer and Assistant Prof., Dept. of Computer Science, Univ. of Cyprus} 	&  	 01/2009-present
\end{tabular*}
\end{center}

\begin{tabular*}{1.0\textwidth} {@{\extracolsep{\fill}}ll}
\parbox[t]{12.2cm}{
\setlength{\itemsep}{0.05ex}
\begin{itemize}
    \item
        {\bf EPL646 - Advanced Topics in Databases} (Winter 2012--2017):
        Graduate (15 students/year), Elective for All Directions.
        ({\tt http://www.cs.ucy.ac.cy/\~{}dzeina/courses/epl646/})
    \item 
        {\bf EPL446 - Advanced Database Systems} (Spring 2008--2011):
        Undergraduate (15 students/year), Upper-division Elective for General Direction in CS.
        ({\tt http://www.cs.ucy.ac.cy/\~{}dzeina/courses/epl446/})        
    \item {\bf EPL371 - Systems Programming} (Spring 2008--2017, new curriculum):
        Undergraduate (25 students/year), Upper-division Elective Course for CS students.
        ({\tt http://www.cs.ucy.ac.cy/\~{}dzeina/courses/epl371/})
    \item 
        {\bf EPL342 - Databases} (Winter 2009--2011):
        Undergraduate (85 students/year), Lower-Division Compulsory for all CS students.
        ({\tt http://www.cs.ucy.ac.cy/\~{}dzeina/courses/epl342/})
    \item
        {\bf EPL232 - Programming Techniques and Tools} {\bf (Winter 2017, new course)}:
        Undergraduate (85 students/year), Lower-Division Compulsory for all CS students.
        ({\tt http://www.cs.ucy.ac.cy/\~{}dzeina/courses/epl232/})
    \item
        {\bf EPL132 - Programming Principles II} (Spring 2011--2016):
        Undergraduate (\~{}85 students): Lower-Division Compulsory for all Directions in CS.
        ({\tt http://www.cs.ucy.ac.cy/\~{}dzeina/courses/epl132/})        
    \item 
        {\bf EPL035 - Data Structures and Algorithms for ECE} (Spring 2011--2012):
        Undergraduate (\~{}70 students): Lower-Division Compulsory for all Directions in ECE.
        ({\tt http://www.cs.ucy.ac.cy/\~{}dzeina/courses/epl035/})
\end{itemize}}
\end{tabular*}

\newpage
\begin{center} 
\begin{tabular*}{1.0\textwidth}%
   {@{\extracolsep{\fill}}lr}
{\bf Lecturer, School of Pure and Applied Sc., Open Univ. of Cyprus, Cyprus} 	&  	 07/2007-12/2008
\end{tabular*}
\end{center}

\begin{tabular*}{1.0\textwidth} {@{\extracolsep{\fill}}lr}
\parbox[t]{13.2cm}{
{\bf PLS50 - Fundamental Specialization in Theory and Software (Thematic Unit Coordinator)}
\begin{itemize}
\item 
	{\em Programming languages.} 
\item 
	{\em Data Structures and Algorithms.} 
\item
	{\em Software engineering.} 
\end{itemize}}
\end{tabular*}



\begin{center}  
\begin{tabular*}{1.0\textwidth}%
	{@{\extracolsep{\fill}}lr}
{\bf  Visiting Lecturer}, Department of  Computer Science, University of Cyprus 	&	 2005-2007	\\
\end{tabular*}
\end{center}

\setlength{\itemsep}{0.01ex}
\begin{itemize}
\item 
	{\bf EPL428 - Systems Programming} (Spring 2007) \\
	({\tt http://www.cs.ucy.ac.cy/\~{}dzeina/courses/epl428/})
\item 
	{\bf EPL231 - Data Structures and Algorithms} (Fall 2005) \\
	({\tt http://www.cs.ucy.ac.cy/\~{}dzeina/courses/epl231/})
\item
	{\bf EPL111 - Discrete Structures in Computer Science and Computation} (Spring 2006, 2007) \\
	({\tt http://www.cs.ucy.ac.cy/\~{}dzeina/courses/epl111/})
\item 
	{\bf EPL035 - Data Structures and Algorithms for Elec. and Comp. Engineers} (Fall 2006) \\
	({\tt http://www.cs.ucy.ac.cy/\~{}dzeina/courses/epl035/})
\item 
	{\bf EPL032 - Introduction to Programming and Problem Solving} (Spring 2006) \\
	({\tt http://www.cs.ucy.ac.cy/\~{}dzeina/courses/epl032/})
\item
	{\bf EPL003 - Computer Science and Information Systems}  (Fall 2005, Fall 2006) \\
	({\tt http://www.cs.ucy.ac.cy/courses/EPL003/})
\item
	{\bf EPL001 - Introduction to Computer Science}  (Fall 2005, Spring 2007)	 \\
	({\tt http://www.cs.ucy.ac.cy/courses/EPL001/})
	
\end{itemize}

\begin{center}  
\begin{tabular*}{1.0\textwidth}%
	{@{\extracolsep{\fill}}lr}
{\bf  Invited Tele-Education Lecturer}, EMISPHER (Euro-Mediterranean Internet-Satellite   	&	 2006-2007\\
\indent Platform for Health, Education and Research) \\
\end{tabular*}
\end{center}


\begin{center}  
\begin{tabular*}{1.0\textwidth}%
	{@{\extracolsep{\fill}}lr}
{\bf  Head Teaching Assistant}, Dept. of Comp. Sc. \& Engr., Univ. of California - Riverside 	&	 2002-2003	\\
\end{tabular*}
\end{center}

\begin{tabular*}{1.0\textwidth} {@{\extracolsep{\fill}}lr}
\parbox[t]{13.2cm}{
Coordinated a group of 50+ Teaching Assistants including the preparation of their teaching schedule.
}
\end{tabular*}


\begin{center} 
\begin{tabular*}{1.0\textwidth}%
	{@{\extracolsep{\fill}}lr}
{\bf Teaching Assistant}, Dept. of Computer Sc. \& Engr., University of California - Riverside 	&  	 2001-2003	
\end{tabular*}
\end{center}

\renewcommand{\labelitemi}{$\bullet$}

\begin{itemize}
\item
{\bf Advanced Database Systems Project}, taught by Prof. V.J. Tsotras   \\
{\tt http://www.cs.ucr.edu/\~{}csyiazti/ta/cs179s03/index.html}

\item
{\bf Database Systems}, taught by Prof. V.J. Tsotras   \\
{\tt http://www.cs.ucr.edu/\~{}csyiazti/ta/cs166w03/index.html}

\item
{\bf Multicast Networking Project}, taught by Prof. S.V. Krishnamurthy   \\
{\tt http://www.cs.ucr.edu/\~{}csyiazti/ta/cs179f02/index.html}

\item
{\bf Introduction to Programming in C++}, taught by Dr. K. Lick   \\
{\tt http://www.cs.ucr.edu/\~{}csyiazti/ta/cs10s02/index.html}
\end{itemize}

\begin{center}  
\begin{tabular*}{1.0\textwidth}%
	{@{\extracolsep{\fill}}lr}
{\bf  Technology Show}, Cyprus Broadcasting Corporation (CyBC), Nicosia, Cyprus &  1999-2000 \\
\end{tabular*}
\end{center}

\begin{tabular*}{1.0\textwidth} {@{\extracolsep{\fill}}lr}
\parbox[t]{13.2cm}{}
\end{tabular*}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%			STUDENT ADVISING
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\renewcommand{\labelitemi}{$\bullet$}

\section{\bf ADVISING}
\begin{itemize}
   \setlength{\itemsep}{0.80ex}

    \item {\bf Post Doctoral Collaborators:} 
	\begin{itemize}
		\setlength{\itemsep}{0.10ex}
            \item[-] 01/2012 - current: {\bf Georgios Chatzimilioudis}, Topics: Big Data, Query Processing and Smartphones. Current Appointment: Instructor at University of Cyprus and Open University of Cyprus, Cyprus.
            \item[-] 06/2014 - current: {\bf Christos Laoudias}, Topics: Indoor Localization and Navigation. Current Appointment: KIOS Research Center, Cyprus.
			\item[-] 03/2010 - current: {\bf Andreas Konstantinidis}, Topics: Intelligent Computing, Privacy and Indoor Information Management, Smartphone Testbeds. Current Appointment: Lecturer at Frederick Univ. Cyprus.
            \item[-] 07/2011 - 12/2013: {\bf Panayiotis Andreou}, Topics: Smartphone Testbeds, Smartphone Sensing, Wireless Sensor Networks and Data Management. Next Appointment: Lecturer at Univ. of of Central Lancashire Cyprus.
	\end{itemize}
        
    \item {\bf Ph.D. Advisor:}
	\begin{itemize}
		\setlength{\itemsep}{0.10ex}
			\item[-] 09/2013-current: {\bf Constantinos Costa}, Ph.D. candidate, Topic: ``A Performance-driven Architecture for Spatial Big Data Management".
			\item[-] 09/2012-12/2014: {\bf Georgios Larkou}, Ph.D. student, Topic: ``Management of Smartphone Testbeds". Next Appointment: Co-Founder \& CEO @ Lifey.
            \item[-] 09/2013-12/2014: {\bf Georgios Nicolaides}, Ph.D. student, Topic: ``Crowdsourcing and Mobile Data Management". Next Appointment: Co-Founder \& CTO @ Lifey.
            \item[-] 09/2006-06/2011: {\bf Panayiotis Andreou}, Ph.D. completed (co-advised with George Samaras), ``KSpot+: A Network-aware Framework for Energy-Efficient Data Acquisition in Wireless Sensor Networks'', Graduation Date: June 2011. {\bf Recipient of the CONET European Wireless Sensor Networks (EWSN) PhD Award, 2012.} Next Appointment: Lecturer at UCLAN Cyprus.
	\end{itemize}

    \item {\bf Ph.D. Mentor / Collaborating Students:}
    \begin{itemize}
    \setlength{\itemsep}{0.10ex}
        \item[-] 09/2016-current: {\bf Xiaoyu Ge}, Ph.D. student at Univ. of Pittsburgh, USA, Topic: ``Semantic Location-based  Recommendations'', Advisor: Panos. K. Chrysanthis.
        \item[-] 10/2016-current: {\bf Yusra Ibrahim}, Ph.D. student at Max Planck Institute for Informatics, Saarbruecken, Germany, Topic: ``Semantic Understanding of Quantities and Tables'', Advisor: Gerhard Weikum.
        \item[-] 08/2016-current: {\bf Dhruv Gupta}, Ph.D. student at Max Planck Institute for Informatics, Saarbruecken, Germany, Topic: ``Semantic Aspect Generation'', Advisor: Klaus Berberich.
        \item[-] 06/2016-current: {\bf Artyom Nikitin}, Ph.D. student at Skoltech, Moscow, Russia, Topic: ``Indoor Localization Accuracy Estimation'', Advisor: Panagiotis Karras, 1 open-source tool, 1 honorable-mention award, 1 best demo award.
\item[-] 2011-2014: {\bf Christos Laoudias}, {\bf Ph.D. completed} at Univ. of Cyprus (Advisor: Christos Panayiotou). {\bf Recipent of the Alpha Bank Cyprus Ph.D. Award for ``Creative Research and Innovation''}, three joint international awards (IEEE MDM'12, ACM IPSN'14 and EU-FP7 EVARILOS), 22 joint publications, 2 open source systems/services: Airplace/Anyplace, 2014. Next Appointment: Localization Expert at Huawei Research, Ireland.
        \item[-] 09/2004-12/2005: {\bf Song Lin}, {\bf Ph.D. completed} at Univ. of California - Riverside, CA, USA  (Advisor: Dimitrios Gunopulos). Topics: ``Tiny Index Structures and Top-K Query Processing''. Next Appointment: Google, USA
    \end{itemize}

    \newpage

    \item {\bf PhD. Defense Committee Member:}
    \begin{itemize}
    \setlength{\itemsep}{0.10ex}
        \item[-] {\bf Sepideh Nazemi Gelyan}, ``Distributed Optimization Framework for In-Network Data Processing'', Advisor: Kin K. Leung, Imperial College, London, UK. Other Members: William Knottenbelt (Imperial, UK). {\bf Defense: July 5, 2016.}
        \item[-] {\bf Orestis Gkorgkas}, ``Database content exploration and exploratory analysis of user queries'', Advisor: Kjetil N{\o}rv{\aa}g, Norwegian University of Science and Technology (NTNU), Trondheim, Norway. Other Members: Katja Hose (Aalborg University, Denmark), {\bf Defense: 12 August, 2015}.
        \item[-] {\bf Marios Kleanthous}, ``Cache Content Duplication'', Advisor: Yanos Sazeides, Department of Computer Science, University of Cyprus, Cyprus. Other Members: Chrysostomos Nicopoulos (ECE, UCY), {\bf Defense: April 6, 2012}.
        \item[-] {\bf Panayiotis Andreou}, ``KSpot+: A Network-aware Framework for Energy-Efficient Data Acquisition in Wireless Sensor Networks'', Co-Advisor with George Samaras, Other Members: P.K. Chrysanthis (Univ. of Pittsburgh, USA), E. Pitoura (Univ. of Ioannina, Greece),  {\bf Defense: May 23, 2011}.
    \end{itemize}

    \item {\bf PhD. Proposal Committee Member:}
    \begin{itemize}
    \setlength{\itemsep}{0.10ex}
        \item[-] {\bf Constantinos Costa} (Spatial Big Data: Indexing and Query Processing), PhD Student advised by myself, University of Cyprus, Cyprus. 12/2015.
        \item[-] {\bf Andreas Papadopoulos} (Data Mining, Graph Clustering), PhD Student advised by George Pallis and Marios Dikaiakos, University of Cyprus, Cyprus. 12/2012, 10/2015.
        \item[-] {\bf Hariton Efstathiades} (Social Analytics: Twitter), PhD Student advised by Marios Dikaiakos and George Pallis, University of Cyprus, Cyprus. 12/2014.
        \item[-] {\bf Panayiotis Charalambous} (Graphics: Crowd Steering), PhD Student advised by Yiorgos Chrysanthou, University of Cyprus, Cyprus. 11/2011.
        \item[-] {\bf Marios Kleanthous} (Architecture: Cache Content Duplication), PhD Student advised by Yanos Sazeides, University of Cyprus, Cyprus. 07/2011.
        \item[-] {\bf Panayiotis Andreou} (Database Systems: Sensor Data Management), PhD Student co-advised with George Samaras, University of Cyprus, Cyprus. 05/2008.
        \end{itemize}

    \item {\bf M.Sc. Advisor:}
	\begin{itemize}
		\setlength{\itemsep}{0.10ex}
            \item[-] {\bf Martin Teufner}, M.Sc.,``Life’s a Game – Applying Game Mechanics to real-world Activities through MR Apps in the Field of Travelling'', Erasmus visiting student from University of Applied Sciences Technikum, Vienna, Austria, September 2016.
            \item[-]  {\bf Adamos Adamou}, M.Sc.,``Scalable Trajectory Grouping with K-Anonymity Guarantees'', December 2014.
            \item[-] {\bf Yannis Kitromilidis}, M.Sc.,``Experimental Evaluation and Characterization of SQLite on Android Smartphones'', December 2014.
			\item[-] {\bf Vasileios Mitrousis}, M.Sc.,``Design and Implementation of a JSON Database for Mobile Devices'', August 2013.
			\item[-] {\bf Constantinos Costa}, M.Sc.,``Scalable Continuous All k Nearest Neighbor Queries over Big Data Stores'', August 2013.
	\end{itemize}    
	
    \item {\bf B.Sc. Advisor:} 
	\begin{itemize}
		\setlength{\itemsep}{0.10ex}
         \item[-] Joanna Charalampous, BSc Student, ``Experimental Evaluation of Telco Big Data Amnesia Framework'',  06/2018 (next appointment: TBA)
         \item[-] Andreas Charalampous, BSc Student, ``Experimental Evaluation of Telco Big Data Amnesia Framework'',  06/2018 (next appointment: TBA)
         \item[-] Marileni Angelidou, BSc Student, ``Efficient Exploratory Analysis and Data Management of Wi-Fi Fingerprints'',  06/2018 (next appointment: TBA)
         \item[-] Dimitrios Valeris, BSc Student, ``Implementation of Data Management and Data Search in Indoor Spaces'',  08/2016.
         \item[-] Dimosthenis Stefanidis, BSc Student, ``Foodscanner: Measuring and Identification of Nutritional Facts'', Allergens and Chemical Substances'',  06/2016. (next appointment: University of Cyprus, Cyprus)
         \item[-] Stelios Nicolaou, BSc Student, ``Beacon-based Indoor Data Management'',  06/2016. (next appointment: University of Cyprus, Cyprus)
         \item[-] Chrysovalantis Anastasiou, BSc Student, ``TelcoWare: A Scalable Architecture for Processing Big Telecommunications Data'',  06/2015. (next appointment: USC, USA - MSc/PhD)
         \item[-] Kyriakos Georgiou, BSc Student, ``Implementation and Evaluation of Advanced Indoor Mapping Tools'',  06/2015. (next appointment: U. of Toronto, Canada - MSc)
        \item[-] Timotheos Constambeys, BSc Student, ``Implementation and Evaluation of Indoor Navigation Subsystems'',  12/2014 (next appointment: Edinburgh, UK - MSc)
.
         \item[-] Rafael Constantinou, BSc Student, ``Multi-dimensional K Nearest Neighbor Queries'',  06/2014
         \item[-] Giannis Evagorou, BSc Student, ``Indoor Radiomap Retrieval Techniques and Algorithms'',  06/2014 (next appointment: UCL, UK - MSc/PhD)
         \item[-] Marios Mintzis, BSc Student, ``Big-Data Mockup Studies on Smartphones'',  06/2014 (next appointment: UCL, UK - MSc)
         \item[-] Lambros Petrou, BSc Student, ``Crowdsourcing Indoor Data in Anyplace'',  06/2014 (next appointment: Oxford, UK - MSc \& Amazon UK)
         \item[-] Stefano Taranto, BSc Student, ``Management Tools for Smartphone Testbeds'',  06/2014 (next appointment: Betologic, Cyprus)
         %
			\item[-] Tzoulia Metochi, BSc Student, ``Indoor Inventory Management System with Smartphones'',  06/2013  % 9/10
			\item[-] Paschalis Mpeis, BSc Student, ``Continuous Localization on Smartphones with Privacy Guarantees'',  06/2013 (next appointment: Univ. of Edinburgh, UK - MSc/PhD)  % 10/10
			\item[-] Silouanos Nicolaou, BSc Student, ``Localization on Smartphones with a Partial Radiomap'', 06/2012 (next appointment: Univ. of Kent, UK)  % 9/10
			\item[-] Christos Aplitsiotis, BSc Student, ``The SmartP2P Framework for Finding Social Content in P2P Smartphone Networks'', 06/2012 (next appointment: Univ. of Cyprus, Cyprus)  % 9/10
			\item[-] Gavriella Koupepidou, BSc Student, ``A Crowdsourced Virtual Library with Smartphone Scanners'', 06/2012  % 7.5/10
			\item[-] Costandinos Costa, BSc Student, ``Finding Similar Trajectories in Smartphone Networks without Disclosing the Traces'', 06/2011 (next appointment: Univ. of Cyprus, Cyprus)  % 10/10
 			\item[-] Theodoros Ioannou, BSc Student (co-advised with G. Samaras), ``A Proximity-based Social Network for Smartphone Users'', 06/2011 (next appointment: Univ. of California - Riverside, USA)     % 9/10
            \item[-] Antonis Mavris, BSc Student, ``MobNet: A Mobile Programming Cloud Testbed'', 06/2011 (next appointment: UCL, UK) % 9/10
			\item[-] Pavlos Touloupos, BSc Student, ``External Sorting Algorithms for Flash Storage'', 05/2010. (next appointment: Univ. of Manchester, UK)% 10/10
			\item[-] Panagiota Gianni, BSc Student, ``An Experimental Evaluation of the MINT Algorithm'', 05/2010.	% 7.5/10
	\end{itemize}

   \item {\bf M.Sc. Committee Member: }
	\begin{itemize}
		\setlength{\itemsep}{0.10ex}
            \item[-] 12/2017: Andreas Demetriou, {\em `` ''}, Advisor: Georgia Kapitsaki, University of Cyprus, Cyprus.
            \item[-] 06/2016: Nikita Klyuchnikov, {\em ``Development and commercialization of hybrid visual, inertial and satellite navigation module for unmanned aerial vehicles''}, Advisor: Panagiotis Karras, Skolkovo Institute of Science and Technology (Skoltech), Moscow, Russia.
            \item[-] 06/2015: Athanasios Foudoulis, {\em ``Topology Aware Analytics For Elastic Cloud Services''}, Advisor: George Pallis and Marios Dikaiakos, University of Cyprus, Cyprus.
            \item[-] 06/2015: Ehsan Ul Haq, {\em ``Interactive Customer Experience Based on Social Networks Using Smart Devices''}, Advisor: Panagiotis Karras, Skolkovo Institute of Science and Technology (Skoltech), Moscow, Russia.
            \item[-] 12/2012: Alexander G. Connor, {\em ``Ariadne: A Novel High Availability Cloud Data Store with Transactional Guarantees.}, Advisor: Alex Labrinidis and Panos K. Chrysanthis, Dept. of CS, Univ. of Pittsburgh, PA, USA.
            \item[-] 08/2012: Apostolos Apostolidis, {\em ``Cloud Storage''}, Advisor: Stratis D. Viglas,  School of Informatics at the University of Edinburgh, UK.
            \item[-] 05/2012: Nearchos Panayiotou, Advisor: Yiorgos Chrysanthou, Dept. of CS, Univ. of Cyprus.
            \item[-] 05/2012: Andreas Andreou, Advisor: Chryssis Georgiou, Dept. of CS, Univ. of Cyprus.
            \item[-] 09/2011: Neophytos Theodorou, Advisor: Marios D. Dikaiakos, Dept. of CS, Univ. of Cyprus, Cyprus.
            \item[-] 11/2010: Michael Georgiou, Advisor: Marios Dikaiakos, Dept. of CS, Univ. of Cyprus.
			\item[-] 05/2010: Andreas Savva, Advisor: Chryssis Georgiou, Dept. of CS, Univ. of Cyprus.
			\item[-] 05/2010: Constantinos Savvides, Advisor: Marios Dikaiakos, Dept. of CS, Univ. of Cyprus.
			\item[-] 09/2009: Asterios Katsifodimos, Advisor: Marios Dikaiakos, Dept. of CS, Univ. of Cyprus.
			\item[-] 05/2009: George Athienitis, Advisor: George Chrysanthou, Dept. of CS, Univ. of Cyprus.
			\item[-] 05/2007: Styliani Nisioti, Advisor: Chryssis Georgiou, Dept. of CS, Univ. of Cyprus.
			\item[-] 05/2007: Antoniou Antonis, Advisor: Andreas Pitsillides, Dept. of CS, Univ. of Cyprus.
			\item[-] 05/2007: Kyriacos Neocleous, Advisor: Marios Dikaiakos, Dept. of CS, Univ. of Cyprus.
			\item[-] 05/2007: Andreas Leykaritis, Advisor: George Chrysanthou,  Dept. of CS, Univ. of Cyprus.
	\end{itemize}
  
        
   \item {\bf B.Sc. Committee Member (Dept. of Comp. Sc., Univ. of Cyprus): }
	\begin{itemize}
		\setlength{\itemsep}{0.10ex}	
            \item[-]05/2012: Phedon Roussou, Advisor: George Pallis
            \item[-]05/2012: Antoniadou Marina, Advisor: Pedro Trancoso
            \item[-]05/2012: Tsekouras Nikolas, Advisor: Vasos Vassiliou                                    
            \item[-]05/2011: Andreou Panayiotis, Advisor: George Pallis
            \item[-]05/2011: Sophocleous Constantinos, Advisor: Marios Dikaiakos							
			\item[-]05/2010: Evangelia Vanezi, Advisor: Yannis Dimopoulos
			\item[-]12/2009: Andreas Manoli, Advisor: Marios Dikaiakos
			\item[-]12/2009: Irene Eleftheriou, Advisor: Marios Dikaiakos
			\item[-]05/2009: Constandinos Constantinides, Advisor: Vasos Vassiliou
			\item[-]05/2009: Chatzidimitriou Antigoni, Advisor: Chryssis Georgiou
			\item[-]05/2009: Agathokleous Orestis, Advisor: Yannakis Sazeides
			\item[-]05/2009: Dionysiou Eliana, Advisor: Yannakis Sazeides
			\item[-]05/2009: Siakas Andreas, Advisor: George Samaras
			\item[-]05/2009: Spanos Orestis, Advisor: George Samaras
			\item[-]05/2009: Hapoupi Panayiota, Advisor: George Samaras	
			\item[-]05/2007: Marios Papa, Advisor: Pedro Trancoso
	\end{itemize}
    
   \item {\bf Other Advising: }
	\begin{itemize}
		\setlength{\itemsep}{0.10ex}
			\item[-] Giorgos Constantinou, Marios Constantinides, Andreas Panteli, Theophilos Phoca, Participation in National Imaginecup contest (Ze Gathem Team) ranking 3rd, Department of CS, University of Cyprus, Cyprus.
			\item[-] Wei Xing, PhD Student, Advisor: Marios Dikaiakos, University of Manchester, UK.
			\item[-] Harris Papadakis, PhD Student, Advisor: Evangelos Markatos \& Vivi Fragopoulou, University of Crete and ICS/FORTH, Greece.
			\item[-] Martha Vasiliadou, BSc Student, Advisor: George Samaras, University of Cyprus, Cyprus.
	\end{itemize}   		
\end{itemize}



\section*{\bf ADVISEES AWARDS \& HONORS}
\setlength{\itemsep}{0.10ex}
\begin{itemize}
\item {\bf PhD Fellowship}, Constantinos Costa (PhD candidate): got one of the 55 University of  Cyprus PhD fellowships for 2017/2018.
\item {\bf Travel Scholarship}, Constantinos Costa (PhD student): Eleventh International Workshop on Real-Time Business Intelligence and Analytics (BIRTE'17), with 43rd International Conference on Very Large Databases (VLDB'17), Munich, Germany, August 28, 2017.
\item {\bf Travel Grant}, Constantinos Costa (PhD candidate): among limited number of invitees globally with a travel grant to attend the {\em ``2017 Lectures in Computer Science: Big Data and Applications''}, The Onassis Foundation Science Lecture Series, Heraklion, Crete, Greece, July 10-14, 2017.
\item {\bf Travel Grant}, Constantinos Costa (PhD candidate): among 200 invitees globally with a travel grant to attend the 4th Heidelberg Laureate Forum (HLF), Heidelberg, Germany, Sept 18 23, 2016.
\item {\bf PhD Fellowship}, Constantinos Costa (PhD student): got one of the 33 University of  Cyprus PhD fellowships for 2016/2017.
\item {\bf Travel Grant}, Lambros Petros (MSc collaborator) got a travel grant to attend the ACM Sigmod 2015 Programming Contest, after ranking in the top-5 of the competition organized by MIT, USA and TUM, Germany,  Melbourne, Australia, May 31 - Jun 4, 2015.
\item {\bf Travel Grant}, George Chatzimilioudes (Postdoc collaborator) got a fellowship to attend the Herrenhausen Conference titled ``Big Data in a Transdisciplinary Perspective'', Hannover, Germany, March 25 – 27, 2015.
\item {\bf PhD Fellowship}, Constantinos Costa (PhD student): selected for a competitive University of  Cyprus PhD fellowship for 2015/2016.
\item  {\bf Best PhD Academic Award}, Christos Laoudias (PhD collaborator) was the recipient of the Recipent of the Alpha Bank Cyprus Ph.D. Award for ``Creative Research and Innovation'' for his PhD thesis titled ``Localization and tracking in wireless networks for fault tolerance and device diversity'', University of Cyprus, Cyprus, March 2014.
\item {\bf Travel Grant}, George Larkou (PhD student): got a travel grant to attend the 27th Large Installation System Administration Conference (LISA), Washington, D.C., USA, Nov. 3 - Nov. 8, 2013.
\item  {\bf Best PhD Academic Award}, Panayiotis Andreou (PhD student) was the recipient of the CONET European Wireless Sensor Networks (EWSN) PhD Academic Award for his PhD thesis titled ``KSpot+: A Network-aware Framework for Energy-efficient Data Acquisition in Wireless Sensor Networks'', 9th European Conference on Wireless Sensor Networks, EWSN 2012, University of Trento, Italy, February 15 - 17, 2012.
\item {\bf Sigmod Programming Contest} Various teams coached by me consistenly ranked in 5th-10th position at the ACM Sigmod Programming contest, 2010, 2011, 2013, 2014 and 2015.
\end{itemize}

\newpage

	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%		        SOFTWARE SYSTEMS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5

\section{\bf OPEN-SOURCE SOFTWARE (Selected, 2009-2016)}
\noindent
\begin{itemize}

\item
{\bf Anyplace - Indoor Localization and Navigation (2011-current):}
I supervised the development of Anyplace, an open, modular, extensible and scalable navigation architecture that exploits crowdsourced Wi-Fi data to develop a novel navigation service that won several international research awards for its utility and accuracy (i.e., less than 2 meters). Paricularly, it won the 1st place at the Evaluation of RF-based Indoor Localization Solutions for the Future Internet (EVARILOS Open Challenge), European Union, the 2nd place at the Microsoft Research Indoor Localization Competition at IEEE/ACM IPSN 2014, Berlin, Germany and the Best Demo Award at 2012 IEEE Mobile Data Management Conference, Bangalore, India. Our MIT-licenced open-source software stack has to this date been used by hundreds of researchers and practitioners around the globe, with the public Anyplace service reaching over 100,000 real user interactions and over 20,000 real users. ({\tt http://anyplace.cs.ucy.ac.cy/})

\item
{\bf Rayzit - Proximity-based Social Network (2012-current):}
I supervised the development of Rayzit, an anonymous dynamic crowd messaging architecture, which is based on
generating a kNN network among users by connecting each user to their k geographically closest peers at each moment.
The given service has won the Appcampus award by a Finnish Alliance comprising of Microsoft, Nokia and Aalto University.
Our MIT-licenced open-source software stack has to this date been used by many researchers and practitioners around the globe, with the public Rayzit service reaching over 45,000 real user interactions and over 10,000 real users. ({\tt http://rayzit.com/})

\item
{\bf SmartLab - A Smartphone Programming Cloud (2011-2015):}
I supervised the development of the SmartLab, an experimental testbed of Android Smartphones deployed at the Department of Computer Science building at the University of Cyprus. SmartLab provides a public testbed for development and testing of smartphone network applications via an intuitive web-based interface. In many respects, it is one of the first Smartphone Computer Clusters globally. Registered users can upload and install APK files on a number of Android smartphones, capture their output (screenshot or files), reboot the devices, create concurrent interactive jobs using MonkeyRunner scripts and many other exciting features. SmartLab has been used to facilitate research in smartphone network programming environments, communication protocols, system design, and applications. ({\tt http://smartlab.cs.ucy.ac.cy/})

\item
{\bf SmartTrace - A Crowdsourced Trajectory Similarity Framework (2009-2013):}
I supervised the development of SmartTrace+, a prototype crowdsourced trajectory similarity search framework that enables the execution of queries in the form: ``Report the users that move more similar to Q, where Q is some query trace. The notion of similarity captures the trajectories that differ only slightly, in the whole sequence, from the query Q. SmartTrace+ enables the execution of such queries in both outdoor environments (using GPS) and indoor environments (using WiFi RSS), without disclosing the traces of participating users to the querying node. Our framework can be utilized in large-scale urban and transit planning applications, which would otherwise be limited by data disclosure constraints, social networking applications for smartphones, habitant monitoring systems, etc.  ({\tt http://smarttrace.cs.ucy.ac.cy/})

\item
{\bf KSpot - Spotting the K Highest-ranked answers in Wireless Sensor Networks (2011):}
    I supervised the development of the KSpot software system, a graphical user interface and ranking system
    for effectively monitoring the K highest-ranked answers
    to a query in a  Wireless Sensor Network. KSpot deploys state-of-the-art distributed Top-k query processing
    algorithms in order to realize both {\em snapshot queries} and {\em historic queries}
    minimizing the consumption of system resources and prolonging the lifetime of the deployed sensor network.
    Additionally, KSpot is {\em user-friendly and customizable} featuring an intuitive user interface that enables the user to
    express declarative SQL-like queries over any ad-hoc scenario and to
    display the results graphically ({\tt http://kspot.cs.ucy.ac.cy/})


\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%			LANGUAGES        
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\section{\bf LANGUAGES}
\begin{itemize}
\setlength{\itemsep}{0.10ex}

\item Greek   (native)
\item English (fluent) 
\item German  (fluent) 
\end{itemize} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%			PERSONAL
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\renewcommand{\labelitemi}{$\bullet$}

\section{\bf PERSONAL INFORMATION}
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item  Gender:  Male
\item  Date of Birth: June 20, 1978
\item  Place of Birth:  Yazd/Iran
\item  Nationality:  Cypriot
\item  Marital Status:  Married with 2 children 
\end{itemize}


\end{document}

	
	
		
		
		
		
		
		
		
		
		
	
	
	
	
	
	
