% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% CV.tex
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Dr. Zhuo-Song Zhang}
\newcommand{\CVTitle}{Zhuo-Song Zhang's CV}
\newcommand{\CVNote}{CV compiled on {\today}}
\newcommand{\CVWebpage}{https://zhuosongz.github.io}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\newcounter{numa}

\Title{\CVAuthor}


\begin{Body}

%%%%%%%%%%
%% Basic information
%%%%%%%%%%


\Section{Basic information}
{Basic information}
{PDF:Basic information}

%\BulletItem Research Fellow
\BulletItem Department of Statistics and Applied Probability
\BulletItem National University of Singapore
%\BulletItem Phone: 
\BulletItem Email: \href{mailto:zszhang.stat@gmail.com}
{zszhangstat@gmail.com}
\BulletItem Homepage: \href{\CVWebpage}\CVWebpage

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
\href{http://www.cuhk.edu.hk}
{\textbf{The Chinese University of Hong Kong}}, Hong Kong

\Gap
\BulletItem
Ph.D. in
\href{http://www.sta.cuhk.edu.hk}
{Statistics}
\SubBulletItem
Supervisor:
Prof.~Qi-Man~Shao.
\hfill
\DatestampYMD{2013}{08}{01} -- \DatestampYMD{2017}{07}{30}
%\DatestampYMD{2014}{07}{15}
\begin{Detail}
%\SubBulletItem
%Focus:
%Stein's method, Asymptotic theory in probability and statistics, Statistical physics.
\end{Detail}

\Entry
\href{http://www.whu.edu.cn}
{\textbf{Wuhan University}}, China
\Gap
\BulletItem
B.S. in Statistics.
\hfill
\DatestampYMD{2009}{09}{01} -- \DatestampYMD{2013}{06}{30}



%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Research Experience}
{Research Experience}
{PDF:ResearchExperience}

\Entry
\href{http://www.stanford.edu}
{\textbf{Stanford University,  Statistics Department}}
%Science College

\Gap
\BulletItem
Visiting Student Researcher
\SubBulletItem
Adviser:
Prof.~Sourav~Chatterjee.
\hfill
\DatestampYMD{2016}{07}{01} --
\DatestampYMD{2016}{08}{31}
\begin{Detail}
%\SubBullet

\end{Detail}
\Entry
\href{http://www.unimelb.edu.au}
{\textbf{Melbourne University,  School of Mathematics and Statistics}}
%Science College

\Gap
\BulletItem
Research Fellow in statistics
\SubBulletItem
Adviser:
Prof.~Aurore~Delaigle.
\hfill
\DatestampYMD{2017}{08}{01} --
\DatestampYMD{2019}{06}{27}
\Gap 
\Entry
\href{http://www.nus.edu.sg}
{\textbf{National University of Singapore,  Department of Statistics and Applied Probability}}
%Science College

\BulletItem
Research Fellow
\SubBulletItem
Adviser:
Prof.~Adrian~Roellin.
\hfill
\DatestampYMD{2019}{07}{01} --
present
\begin{Detail}
%\SubBulletItem

\end{Detail}


%%%%%%%%%%%%%%%%%%
%% Research interest
%%%%%%%%%%%%%%%%%%

\Section
{Research interests}
{Research interests}
{PDF:Research interests}
Asymptotic theory in probability and statistics;  Stein's method;  Functional data analysis;
Nonparametric statistics; Random Graph theory.

%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%

\Section
{Publications}
{Publications}
{PDF:Publications}


% Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
\begingroup
\renewcommand{\MaxNumberedItem}{[88]}

\BigGap
\NumberedItem{[1]}
\href{http://link.springer.com/article/10.1007/s11425-016-0322-3}
{Q.-M.~Shao and \underline{Z.-S.~Zhang}.  (2016).
``Identifying the limiting distribution by a general approach of Stein’s method'',
\textit{Sci. China Math.},
vol.~59,
~2379--2392. } 

\BigGap
\NumberedItem{[2]}
{Q.-M.~Shao and \underline{Z.-S.~Zhang}. (2019).
``Berry--Esseen bounds of normal and non-normal approximation for unbounded exchangeable pairs'',
\textit{Ann. Probab.}, 
vol. 47, 
~61--108. }

\BigGap
\NumberedItem{[3]}
{Q.-M.~Shao, M.-C.~Zhang and {\underline{Z.-S.~Zhang}}. (2021),
``Cram\'er-type moderate deviations for non-normal
approximation''. \textit{Ann. Appl. Probab.}
Vol. 31,~247–283.}
 

\NumberedItem{[4]}
Q.-M. Shao and \underline{Z.-S.~Zhang} (2020),
``Berry–Esseen bounds for multivariate nonlinear statistics with applications to M-estimators and stochastic gradient descent algorithms''.
To appear in Bernoulli. 
\endgroup


\BigGap 

\Section
{Submitted papers}
{Submitted papers}
{PDF:submittedpapers}


\begingroup
\renewcommand{\MaxNumberedItem}{[88]}
\setcounter{numa}{1}
\def\numathe{\thenuma\stepcounter{numa}}


\BigGap

\NumberedItem{[\numathe]}
\underline{Z.-S.~Zhang},
``Cram\'er-type moderate deviations of normal approximation for exchangeable pairs''. 
Available at arXiv: 1901.09526. Submitted to \emph{Bernoulli}, Major revision.
\BigGap 

\NumberedItem{[\numathe]}
\underline{Z.-S.~Zhang},
``Berry--Esseen bounds for generalized $U$-statistics''. 
Available at arXiv: 2104.03479. Submitted to \emph{Electronic Journal of Probability}.
\BigGap

\NumberedItem{[\numathe]}
\underline{Z.-S.~Zhang},
``Berry--Esseen bounds for self-normalized sums of local dependent random variables''. 
Available at arXiv: 2104.03683. Submitted to \emph{Journal of Applied Probability}.

\BigGap
\NumberedItem{[\numathe]}
S. Liu and \underline{Z.-S.~Zhang},
``Cram\'er-type moderate deviation under Stein's identities with applications to local dependence and combinatorial central limit theorems''. Submitted to \emph{Annals of Applied Probability}.

\BigGap

\NumberedItem{[\numathe]}
A. Roellin and \underline{Z.-S.~Zhang},
``Dense multigraphon-valued stochastic processes and edge-changing dynamics in the configuration model''. Submitted to \emph{Annals of Applied Probability}.

\Gap

\endgroup 


\Section{Working\\
papers}
{Working papers}
{PDF:Working papers}


\begingroup
\renewcommand{\MaxNumberedItem}{[88]}
\setcounter{numa}{1}
\def\numathe{\thenuma\stepcounter{numa}}

\NumberedItem{[\numathe]}
%\href{http://www.example.com/my-paper-doi-5}
A.~Delaigle, D.~Dutta and {\underline{Z.-S.~Zhang}},
``Reconstructing fragmented functional data by Markov chains''. 

\Gap  

\NumberedItem{[\numathe]}
%\href{http://www.example.com/my-paper-doi-5}
A.~Delaigle and {\underline{Z.-S.~Zhang}},
``Reconstructing functional data by nonparametric methods''. 

\Gap
\endgroup



\BigGap
\newpage
\Section
{Invited presentations}
{Invited presentations}
{PDF:Invited presentations}

% Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
\begingroup
\renewcommand{\MaxNumberedItem}{[8888]}
\setcounter{numa}{1}
\def\numathe{\thenuma\stepcounter{numa}}

\BigGap
\NumberedItem{[\numathe]}
%\href{http://ims-aprm2016.sta.cuhk.edu.hk}
\textit{62nd ISI World Statistics Congress 2019},
Kuala Lumpur, Malaysia.  
\DatestampYM{2019}{08}.


\BigGap
\NumberedItem{[\numathe]}
%\href{http://ims-aprm2016.sta.cuhk.edu.hk}
\textit{Stein's Method and Related Topics},
Macau, China, 
\DatestampYM{2018}{12}.

\BigGap
\NumberedItem{[\numathe]}
%\href{http://ims-aprm2016.sta.cuhk.edu.hk}
\textit{The 5th Institute of Mathematical Statistics
Asia Pacific Rim Meeting},
The National University of Singapore, Singapore, 
\DatestampYM{2018}{06}.
\Gap
\NumberedItem{[\numathe]}
\textit{2017 IMS-China International Conference on Statistics and Probability}, Guangxi University For Nationalities, Nanning, China, 
\DatestampYM{2017}{6}
\Gap

\NumberedItem{[\numathe]}
\textit{The 10th ICSA international conference}, Shanghai Jiao Tong University, 
Shanghai, China,
\DatestampYM{2016}{12}.


\Gap
\NumberedItem{[\numathe]}
\href{http://110.65.147.107/events/11/}
{
\textit{The International Symposium on Probability Theory and Related Fields}, Southern University of Science and Technology, 
Shenzhen, China,
\DatestampYM{2016}{11}.
}
\Gap
\NumberedItem{[\numathe]}
%\href{http://ims-aprm2016.sta.cuhk.edu.hk}
\textit{The 4th Institute of Mathematical Statistics
Asia Pacific Rim Meeting},
The Chinese University of Hong Kong, HK,
\DatestampYM{2016}{06}.



\endgroup

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AWARDS & SCHOLARSHIPS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage
\Section
{Awards \&\newline
Scholarships}
{Awards \& Scholarships}
{PDF:AwardsAndScholarships}

\BulletItem
Overseas Research Award, \DatestampY{2015--2016}\\
Department of Statistics, The Chinese University of Hong Kong
\BulletItem
Nominee of Global Young Scientists Summit 2015, \DatestampY{2014--2015}\\ 
Science Faculty, The Chinese University of Hong Kong
\BulletItem
Wuhan University Outstanding Graduate student, \DatestampY{2013}
%Wuhan University, Wuhan, China
\BulletItem
National motivational scholarships, \DatestampY{2011}
%Wuhan University, Wuhan, China
\BulletItem
Wuhan University Outstanding students scholarship, \DatestampY{2011}
%Wuhan University, Wuhan, China
\BulletItem
Wuhan University Excellent student, \DatestampY{2011}
%Wuhan University, Wuhan, China



%%%%%%%%%%%%%%%%%%%%%%%5
%%% Professional activities
%%%%%%%%%%%%%%%%%%%%%%%%



\Section{Professional services}
{Professional services}
{PDF:Professional services}


\SubSection{Reviewers}{Reviewers}
{PDF:Reviewers}

\begingroup

Journals: Bernoulli, Probability in the Engineering and Informational Sciences
\endgroup


\Section{Supervision Experience}{Co-supervision}
{PDF:Co-supervision}

\SubSection{PhD Students}{PhD Students}
{PDF:Students}


Mr. Debajit Dutta, PhD student \\
Co-supervisor of his thesis work on ``fragmented functional data''. % with Professor Aurore Delaigle. 



\Section
{Teaching}
{Teaching}
{PDF:Teaching }

\BulletItem
Fall 2018, MAST90123, Advanced Mathematical Statistics, University of Melbourne

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Teaching Assistant %%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\Section
{Teaching Assistant}
{Teaching Assistant}
{PDF:Teaching Assistant}

\BulletItem
Fall 2013, STAT 2001 A/B, Basic Concepts in Probability and Statistics I 
\BulletItem
Spring 2014, STAT 2006 A/B, Basic Concepts in Probability and Statistics II
\BulletItem
Fall 2014, STAT 5005, Advanced Probability Theory %, \\ Instructor: Prof. Qi-Man SHAO.

\BulletItem
Spring 2015, STAT 4003, Statistical Inference%, \\ Instructor: Prof. WU Ka Hok.

\BulletItem
Fall 2015, STAT 5005, Advanced Probability Theory%, \\ Instructor: Prof. Qi-Man SHAO.

\BulletItem
Fall 2015, RMSC 5001, Advanced Statistical  Theory in Risk Management%, \\ Instructor: Prof. LEUNG Pui Lam.

\BulletItem
Spring 2016, RMSC 4001, Simulation Methods for Risk Management Science and Finance %\\ Instructor: Prof. WONG Hoi Ying.

\BulletItem
Fall 2016, STAT 3210, Statistical Techniques in Life Sciences%, \\ Instructor: Prof. Xiao FANG.



\end{Body}

\end{document}
